### 2022-10-24 r-examples/emissions_2109.Rmd
examples

---
title: "Emissions 2109"
author: "Johann Salzmann"
output: pdf_document
---

```{r setup, include=FALSE}

rm(list = ls(envir = globalenv()),envir = globalenv())

if (!require("pacman")) install.packages("pacman")
library(pacman)

p_load(tidyr)
p_load(dplyr)
p_load(magrittr)
p_load(purrr)
p_load(stringr)
p_load(rlang)
p_load(tidyverse)
p_load(ggplot2)
p_load(readxl)

"%cin%" = function(x,y){str_detect(y,x)}
"%xin%" = function(x,y){x %cin% y | y %cin% x}
"%ni%" = Negate("%in%")
"%nci%" = Negate("%cin%")
"%nxi%" = Negate("%xin%")
"%.%" = function(x,y){paste(x,y,sep = "")}
cNA = as.character(NA)
as.numeric.factor = . %>% as.numeric(levels(.))[.]

## These files take relatively long to load, so it is best to load them just once
## We can then move to another chunk for the rest of the analysis
## But be careful not to overwrite these data frames, otherwise you have to come back here and load them again

```

```{r group_and_join}

load("Data/data_wdi.RData")
data_ghg = read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)

data_ghg %<>% group_by(ISO,country,year) %>%
  summarise(GHGa = sum(GHG))

data_wdi %<>% select(ISO,year,pop)

data_joined = data_ghg %>% inner_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHGpc = GHGa/pop)

data_joined %>% filter(GHGpc > 20) %>%
  ggplot(aes(x=year, y=GHGpc, group=ISO)) +
  geom_line(aes(color=factor(ISO)))+
  geom_point() +
  theme_light()

data_joined %>% filter(year == 2019) %>%
  ggplot(aes(x=GHGpc)) +
  geom_histogram(bins=50) +
  theme(legend.position="none") +
  theme_light()

data_joined %>% filter(year == 2019) %>%
  ggplot(aes(x=GHGpc)) +
  geom_histogram(bins=50) +
  theme(legend.position="none") +
  theme_light()

data_joined %>% filter(year == 2019) %>%
  ggplot(aes(x=GHGpc)) +
  geom_density() +
  theme(legend.position="none") +
  theme_light()

data_joined %>% ggplot(aes(x=year, y=GHGpc, fill=ISO)) + 
    geom_area() +
    theme(legend.position="none")

## To plot total GHG emissions, we need to merge the two datasets
## This is one of the most common things you have to do in data coding
## But first I would aggregate both datasets into global totals, then join them together
## We do this by "grouping" and "summarising" the data

plot_data_gases <- data_ghg %>%       # create a new variable called "data_gases", copied from "data_ghg"
  group_by(year) %>%                  # choose "years" as our grouping variable
  summarise(CO2=sum(CO2,na.rm=TRUE),  # sum up the CO2 column by years, ignoring any missing values
            CH4=sum(CH4,na.rm=TRUE),  # sum up the CH4 column by years, ...
            N2O=sum(N2O,na.rm=TRUE),  # etc.
            Fgas=sum(Fgas,na.rm=TRUE))

# Note that "summarise" drops any other columns in the dataframe that were not grouped or summarised

## Now we want to do the same for the LULUCF data
## In this dataset we only want the "mean" column

plot_data_lulucf <- data_lulucf %>% 
  group_by(year) %>% 
  summarise(CO2_LULUCF=sum(mean,na.rm=TRUE)) # sum up the mean column by years, but rename it to "CO2_LULUCF"

## Now we can join the two datasets together
## Here we use a "left_join"
## This function takes all rows from the data frame we specify as "left" (the first data frame)
## It then matches these rows to the data frame we specify as "right" (the second data frame)
## If there are no matches it returns NA in that row
## If there are additional rows in the "right" data frame, they are dropped
## We need to specify a matching column, to merge the data frames, here we use "year"

plot_data_gases <- left_join(plot_data_gases,plot_data_lulucf,by="year")

## Notice that only the years 1970-2019 are taken from "data_lulucf"? The rest are not copied over
## This is what we want, but one could also use a "full_join" to keep all available rows in both frames

```

```{r gather}

## All our data is now in a single data frame
## Now we need to "gather" it into a long format
## Many functions in R expect data to be in a long format, especially plot functions
## Long format is when all numerical values are in a single column

plot_data_gases <- gather(plot_data_gases,key="gas",value="total_GHG_emissions",CO2:CO2_LULUCF)

## "Key" defines the name of the column that will now take the gathered column titles as it's values
## In our case we call it "gas" because it will contain "CO2", "CH4", etc...
## "Value" defines the name of the column that will take all the number values
## And the last argument ("CO2:CO2_LULUCF") defines the range of columns that are to be gathered

```

```{r plot}

## Now we can plot!
## We will use the ggplot function from tidyverse, which is good for layering up components of a graphic

## To use it, we need to define the aesthetics. 
## Aesthetics map the variables in your dataset to the elements that you can see on a plot
## We define them using the "aes()" function
## You can use aes() to define position (x or y axis), fill color, size, and other types of plot elements
## Here we define the x axis as "year", the y axis as "total_GHG_emissions", and the fill color as "gas"

## These variables are then passed into a geometric object ("geom"), which are the marks on the plot
## We want to show an area plot, so we use "geom_area()"
## There are many other geom functions available to use: https://ggplot2.tidyverse.org/reference/

ggplot(plot_data_gases,aes(x=year,y=total_GHG_emissions,fill=gas)) +
  geom_area()

```

```{r nicer_plot}

## Now we might want to make this plot looks nicer
## Here are some examples of things that I would tweak
## As a general rule, simple and clean figures are usually best

plot_data_gases <- plot_data_gases %>% 
  filter(year!=2020) %>%                              ## filter the dataset to remove the year 2020
  mutate(total_GHG_emissions=total_GHG_emissions/1e9) ## convert tons into Gigatons (Gt)

ggplot(plot_data_gases,aes(x=year,y=total_GHG_emissions,fill=gas)) +
  geom_area(color="#636363") +              ## Define a colour (grey) to outline each area 
  ylab("Total GHG emissions (GtCO2eq)") +   ## replace the label on the y axis
  theme_bw() +                              ## Use my favourite "black/white" theme 
  scale_fill_brewer(palette="Set2") +       ## Use my favourite color scale from https://colorbrewer2.org
  theme(axis.title.x = element_blank()) +   ## Remove the x axis label (years is obvious)
  ggtitle("Total anthropogenic GHG emissions continue to grow")

```

### 2022-10-24 r-examples/emissions_by_country_and_sector.Rmd
examples

---
title: "emissions_by_country_and_sector"
author: "William F. Lamb"
date: "18 9 2022"
output: html_document
---

```{r setup, include=FALSE}

rm(list = ls())
library(tidyverse)
library(readxl)

data_ghg <- read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)

```

```{r country_trend, echo=FALSE,fig.width=4,fig.height=2}

## I divide by 1e6 because country emissions are often reported in Megatons (MtCO2eq)

data_countries <- data_ghg %>% 
  group_by(ISO,country,region_ar6_6,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE)/1e6)

data_countries %>% 
  filter(year!=2020) %>% 
  filter(country %in% c("United States")) %>% 
  ggplot(.,aes(x=year,y=GHG)) +
  geom_path() +
  theme_bw() +
  scale_y_continuous(limits=c(0,NA)) +
  ylab("GHG emissions (MtCO2eq)") +
  theme(axis.title.x=element_blank()) +
  ggtitle(paste0("United States GHG emissions"))

```

```{r country_sector_trend, echo=FALSE,fig.width=4,fig.height=2}

data_countries <- data_ghg %>% 
  group_by(ISO,country,region_ar6_6,year,sector_title) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE)/1e6)

data_countries %>% 
  filter(year!=2020) %>% 
  filter(country %in% c("United States")) %>% 
  ggplot(.,aes(x=year,y=GHG,fill=sector_title)) +
  geom_area(color="#636363") +
  theme_bw() +
  scale_fill_brewer(palette="Set2") +
  ylab("GHG emissions (MtCO2eq)") +
  theme(axis.title.x=element_blank()) +
  ggtitle(paste0("United States GHG emissions"))

```

### 2022-10-24 r-examples/emissions_by_gas.Rmd
examples

--- 2022-10-24 r-examples/emissions_2109.Rmd
@@
 ---
-title: "Emissions 2109"
-author: "Johann Salzmann"
+title: "emissions_by_gas"
+author: "William F. Lamb"
 output: pdf_document
@@
 
-rm(list = ls(envir = globalenv()),envir = globalenv())
+## At the start of a notebook you need to load all the packages needed for your analysis
 
-if (!require("pacman")) install.packages("pacman")
-library(pacman)
+library(tidyverse) ## In our case we need Tidyverse
+library(readxl) ## And a library to open xlsx files
 
-p_load(tidyr)
-p_load(dplyr)
-p_load(magrittr)
-p_load(purrr)
-p_load(stringr)
-p_load(rlang)
-p_load(tidyverse)
-p_load(ggplot2)
-p_load(readxl)
+## We also need to get the data.
+## There are two sheets already in the data folder
+## These are sourced from a file online (https://zenodo.org/record/6483002)
+## To load the data, we need to simply indicate where the file is ("xlsxFile =")
+## And which sheet should be read ("sheet = ")
 
-"%cin%" = function(x,y){str_detect(y,x)}
-"%xin%" = function(x,y){x %cin% y | y %cin% x}
-"%ni%" = Negate("%in%")
-"%nci%" = Negate("%cin%")
-"%nxi%" = Negate("%xin%")
-"%.%" = function(x,y){paste(x,y,sep = "")}
-cNA = as.character(NA)
-as.numeric.factor = . %>% as.numeric(levels(.))[.]
+data_ghg <- read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)
+data_lulucf <- read_excel(path = 'Data/essd_lulucf_data.xlsx', sheet = 2)
 
@@
 ```{r group_and_join}
-
-load("Data/data_wdi.RData")
-data_ghg = read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)
-
-data_ghg %<>% group_by(ISO,country,year) %>%
-  summarise(GHGa = sum(GHG))
-
-data_wdi %<>% select(ISO,year,pop)
-
-data_joined = data_ghg %>% inner_join(data_wdi,by=c("ISO","year")) %>%
-  mutate(GHGpc = GHGa/pop)
-
-data_joined %>% filter(GHGpc > 20) %>%
-  ggplot(aes(x=year, y=GHGpc, group=ISO)) +
-  geom_line(aes(color=factor(ISO)))+
-  geom_point() +
-  theme_light()
-
-data_joined %>% filter(year == 2019) %>%
-  ggplot(aes(x=GHGpc)) +
-  geom_histogram(bins=50) +
-  theme(legend.position="none") +
-  theme_light()
-
-data_joined %>% filter(year == 2019) %>%
-  ggplot(aes(x=GHGpc)) +
-  geom_histogram(bins=50) +
-  theme(legend.position="none") +
-  theme_light()
-
-data_joined %>% filter(year == 2019) %>%
-  ggplot(aes(x=GHGpc)) +
-  geom_density() +
-  theme(legend.position="none") +
-  theme_light()
-
-data_joined %>% ggplot(aes(x=year, y=GHGpc, fill=ISO)) + 
-    geom_area() +
-    theme(legend.position="none")
 

### 2022-10-24 r-examples/emissions_by_multiple_countries.Rmd
examples

---
title: "extra_code"
author: "William F. Lamb"
date: "21 9 2022"
output: html_document
---

```{r setup, include=FALSE}

rm(list = ls())
library(tidyverse)
library(readxl)

data_ghg <- read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)

```

```{r countries_by_sectors, echo=FALSE,fig.width=7,fig.height=6}

## In this example we can sum emissions to 3 dimensions: country, year and sector

data_countries <- data_ghg %>% 
  group_by(ISO,country,year,sector_title) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE)/1e6)

## Then instead of showing one plot for a single country, you can use a list to filter multiple countries
## And use "facet_wrap" to split your plot into multiple subplots based on a variable in your dataset (here using "country")

data_countries %>% 
  filter(year!=2020) %>% 
  filter(country %in% c("United States",
                        "China",
                        "India",
                        "Indonesia",
                        "Japan",
                        "Russia",
                        "Germany")) %>%
  ggplot(.,aes(x=year,y=GHG,fill=sector_title)) +
  geom_area(color="#636363") +
  facet_wrap(.~country,scales="free",ncol=2) + ## this splits your plot into multiple subplots, giving each its own scale
  theme_bw() +
  scale_fill_brewer(palette="Set2") +
  ylab("GHG emissions (MtCO2eq)") +
  theme(axis.title.x=element_blank())

```

```{r sectors_by_countries, echo=FALSE,fig.width=7,fig.height=6}

data_countries <- data_ghg %>% 
  group_by(ISO,country,year,sector_title) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE)/1e6)

## You can facet by any variable, e.g. here we split the plots by sector and color in the fill by country:

data_countries %>% 
  filter(year!=2020) %>% 
  filter(country %in% c("United States",
                        "China",
                        "India",
                        "Indonesia",
                        "Japan",
                        "Russia",
                        "Germany")) %>%
  ggplot(.,aes(x=year,y=GHG,fill=country)) +
  geom_area(color="#636363") +
  facet_wrap(.~sector_title,scales="free",ncol=2) + ## this splits your plot into multiple subplots, giving each its own scale
  theme_bw() +
  scale_fill_brewer(palette="Set2") +
  ylab("GHG emissions (MtCO2eq)") +
  theme(axis.title.x=element_blank())

```

```{r multi_country_trend, echo=FALSE,fig.width=5,fig.height=6}

data_countries <- data_ghg %>% 
  group_by(ISO,country,region_ar6_10,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE)/1e6)

## We can also identify countries computationally, e.g. by calculating the top 15 emitters in a new data frame

country_list <- data_countries %>% 
  filter(year==2019) %>% 
  arrange(desc(GHG)) %>% 
  head(15) %>% 
  ungroup() %>% 
  select(ISO) %>% 
  mutate(include=1)

## Then by re-joining this list and filtering by it

data_countries <- left_join(data_countries,country_list,by="ISO")

data_countries %>% 
  filter(year!=2020) %>% 
  filter(include==1) %>% 
  ggplot(.,aes(x=year,y=GHG)) +
  geom_path() +
  facet_wrap(.~country,scales="free",ncol=3) +
  theme_bw() +
  scale_fill_brewer(palette="Set2") +
  scale_y_continuous(limits=c(0,NA)) +
  scale_x_continuous(breaks=c(1980,2000,2019)) +
  ylab("GHG emissions (MtCO2eq)") +
  theme(axis.title.x=element_blank())

```

```{r region_by_sector, echo=FALSE,fig.width=10,fig.height=3}

## Bar plots are another option for showing evolution and comparing between facets. Here we sum emissions to regions, rather than countries.

data_countries <- data_ghg %>% 
  group_by(region_ar6_10_short,year,sector_title) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE)/1e6)

data_countries %>% 
  filter(region_ar6_10_short!="AIR") %>% 
  filter(region_ar6_10_short!="SEA") %>% 
  filter(year %in% c(1990,2000,2010,2019)) %>% ## filter to four seperate years
  mutate(year=as.factor(year)) %>% 
  ggplot(.,aes(x=year,y=GHG,fill=sector_title)) +
  geom_col(color="#636363") +
  facet_wrap(.~region_ar6_10_short,nrow=1) +
  theme_bw() +
  scale_fill_brewer(palette="Set2") +
  ylab("GHG emissions (MtCO2eq)") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_text(angle=45,hjust=1))

```

```{r cumulative_fraction, echo=FALSE,fig.width=5,fig.height=6}

## This chunk calculates how many countries add up to a given % of global emissions, when ranked from highest to lowest emitter. This could be another way to identify a distinct group of countries for analysis.

data_countries <- data_ghg %>% 
  group_by(ISO,country,region_ar6_10,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE)/1e6)

country_list <- data_countries %>% 
  filter(year==2019) %>% 
  arrange(desc(GHG))

# calculate the cumulative sum of emissions, ranked from highest to lowest
country_list$cumulative_total <- cumsum(country_list$GHG)
# calculate the cumulative fraction of total emissions, ranked from highest to lowest
country_list$cumulative_fraction <- country_list$cumulative_total/sum(country_list$GHG[country_list$year==2019])

# looking at the country_list dataframe, 20 countries account for about 75% of total emissions

```

### 2022-10-24 r-examples/emissions_changes.Rmd
examples

---
title: "emissions_changes"
author: "William F. Lamb"
date: "27 9 2022"
output: html_document
---

```{r setup, include=FALSE}

# load packages
library(tidyverse)
library(readxl)

## load data
data_ghg <- read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)

```

```{r nordstream}

## Whats happening in the Baltic sea right now?

data_countries <- data_ghg %>% 
  group_by(ISO,country,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

data_nordstream <- data_countries %>% 
  filter(year==2019) %>% 
  filter(GHG<=12e6) %>% 
  arrange(desc(GHG)) %>% 
  head(10) %>% 
  mutate(blarg="2")

data_nordstream <- data_nordstream %>% 
  ungroup() %>% 
  add_row(country="Nordstream explosion (Baxter)",GHG=115000*29.8,blarg="1") %>% 
  add_row(country="Nordstream explosion (Zerger)",GHG=356247*29.8,blarg="1") %>% 
  mutate(GHG=GHG/1e6)

data_nordstream %>% ggplot(.,aes(x=GHG,y=reorder(country,GHG),fill=blarg)) +
  geom_col(color="#636363") +
  theme_bw() +
  xlab("GHG Emissions at GWP100 (MtCO2eq)") +
  scale_fill_manual(values=c("#41b6c4","#969696")) +
  theme(legend.position="none",
        axis.title.y=element_blank())

```

```{r calculate_and_plot_changes,fig.width=8,fig.height=3}

## lets calculate emissions changes for total country emissions

data_change <- data_ghg %>% 
  group_by(ISO,country,region_ar6_6,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

## in this next chunk I calculate 3 different types of changes for the time period 2010-2019

data_change <- data_change %>% 
  filter(year %in% c(2010,2019)) %>% 
  group_by(ISO,country) %>% 
  mutate(change_abs = last(GHG)-first(GHG),               ## absolute change, or the difference in emissions between t2 and t1
         change_rel = change_abs/first(GHG),              ## relative change, or the ratio of absolute change to emissions in t1
         change_avg_annual = ((last(GHG)/first(GHG))^(1/(2019-2010))-1)) ## average annual change using the CGAR formula

## here I am just making the units nicer

data_change <- data_change %>% 
  filter(year==2019) %>% ## we dont need all the duplicated rows now
  mutate(change_abs=change_abs/1e6) %>% ## Megatons for the absolute change
  mutate(change_rel=change_rel*100) %>% ## % values for the relative change
  mutate(change_avg_annual=change_avg_annual*100) ## and % for the average annual change

## I'd like to plot all three types and compare them, so I need to gather the values into a single variable

data_change <- gather(data_change,var,value,change_abs,change_rel,change_avg_annual)

## this bit is optional. It just creates a nicely formatted label for each facet (subplot) that I can call in ggplot

data_change <- data_change %>% 
  mutate(label=ifelse(var=="change_abs","Absolute change (MtCO2eq)",NA)) %>% 
  mutate(label=ifelse(var=="change_rel","Relative change (%)",label)) %>% 
  mutate(label=ifelse(var=="change_avg_annual","Avg. annual change (%/yr)",label))

data_change %>% 
  filter(country %in% c("United States",
                        "China",
                        "India",
                        "Indonesia",
                        "Japan",
                        "Russia",
                        "Germany")) %>%
  ggplot(.,aes(x=value,y=country,fill=country)) +
  geom_col(color="#636363",width=0.6) +
  geom_vline(aes(xintercept=0)) +        ## I added this line to emphasize 0: some countries are increasing, others are decreasing
  facet_grid(.~label,scales="free") +    ## facet_grid is a variation of facet_wrap that lets us fix the x axis to countries and avoid repeating the scale 3 times across each plot. I facet by "label" to get the nice titles.
  theme_bw() +
  scale_fill_brewer(palette="Set2") +
  theme(legend.position="none",
        axis.title = element_blank()) +
  ggtitle("GHG emissions changes of countries, 2010-2019")

```

```{r plot_decreases,fig.height=6,fig.width=5}

## Now that we have all types of changes calculated, we can rank and plot which countries are decreasing in emissions

data_change %>% 
  filter(year==2019) %>% 
  filter(var=="change_avg_annual") %>% 
  filter(value<=0) %>% 
  filter(GHG>1e6) %>% ## remove the very small island states
  head(20) %>% 
  ggplot(.,aes(x=value,y=reorder(country,-value))) +
  geom_point() +
  theme_bw() +
  xlab("Average annual emissions change (%/yr)") +
  theme(axis.title.y = element_blank()) +
  ggtitle("GHG emissions change, 2010-2019")

```

```{r plot_changes_region,fig.height=4,fig.width=8}

## Or we could compare changes across different regions

data_change %>% 
  filter(year==2019) %>% 
  filter(var=="change_avg_annual") %>% 
  filter(country!="Int. Aviation") %>% 
  filter(country!="Int. Shipping") %>% 
  ggplot(.,aes(y=region_ar6_6,x=value,fill=region_ar6_6,size=GHG)) +  ##note that we define size (i.e. circle radius) by GHG
  geom_point(shape=21,alpha=0.5,color="#636363") +  ## geom_point can have different shapes. Here we use circles with a fill inside (https://r-graphics.org/recipe-scatter-shapes)
  geom_vline(aes(xintercept=0)) +
  theme_bw() +
  scale_fill_brewer(palette="Set2") +
  scale_size_continuous(range=c(1.5,10)) + ## and here we set the size range for the circle size
  xlab("Average annual emissions change of countries (%/yr)") +
  theme(legend.position="none",
        axis.title.y = element_blank())

```

### 2022-10-24 r-examples/emissions_per_capita.Rmd
examples

---
title: "emissions_by_country"
author: "William F. Lamb"
date: "17 9 2022"
output: html_document
---

```{r setup, include=FALSE}

rm(list = ls())
library(tidyverse)
library(WDI)
library(readxl)

data_ghg <- read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)

# ### Use the WDI package to call the Worldbank API and download some indicators 
# ### Look up indicators here: https://data.worldbank.org/
# ### Data is then saved locally and this code commented out
# 
# ## GDP at PPP
# wdi_gdp<-WDI(country = "all",indicator = "NY.GDP.MKTP.PP.KD",start = 1970,end = 2019,extra=TRUE,language = "en") %>%
#   select(ISO=iso3c, country, year, gdp_ppp=`NY.GDP.MKTP.PP.KD`) %>%
#   filter(!is.na(ISO))
# 
# # POP
# wdi_pop<-WDI(country = "all",indicator = "SP.POP.TOTL",start = 1970,end = 2019,extra=TRUE,language = "en")%>%
#   select(ISO=iso3c, country, year, pop=`SP.POP.TOTL`) %>%
#   filter(!is.na(ISO))
# 
# data_wdi <- left_join(wdi_pop,wdi_gdp,by=c("ISO","year","country"))
# data_wdi <- data_wdi %>% 
#   arrange(ISO,country,year)
# 
# save(data_wdi,file="Data/data_wdi.RData")
# 
# ##

load("Data/data_wdi.RData")

```

```{r data_prep_per_capita}

## We want total per capita emissions, so first I would sum GHG emissions to countries

data_countries <- data_ghg %>% 
  group_by(ISO,country,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

## Now we need to join it with the socio-economic data

## Note: we are not certain that country names from the WDI data will match those in EDGAR
## Often countries are spelled differently in different databases
## Therefore we join by country ISO codes, which are have a standardised pattern for each country
## https://en.wikipedia.org/wiki/ISO_3166-1_alpha-3
## Remember to discard the column of country names in one of your databases, as we dont need two

data_countries <- left_join(data_countries,data_wdi %>%
                              select(-country),by=c("ISO","year"))

## calculate per capita GHG emissions

data_countries <- data_countries %>% 
  mutate(GHG_pc=GHG/pop)

```

```{r plot_per_capita_distribution,fig.width=4,fig.height=3}

## here are some example plots to explore the distribution of per capita emissions

data_countries %>% 
  filter(year==2019) %>% 
  ggplot(.,aes(x=GHG_pc)) +
  geom_histogram(bins=50,fill="#66c2a5",color="#636363") +
  theme_bw()

data_countries %>% 
  filter(year==2019) %>% 
  ggplot(.,aes(x=GHG_pc)) +
  geom_density(color="#636363",fill="#66c2a5") +
  theme_bw()

```

```{r plot_per_capita_distribution_by_region,fig.width=6,fig.height=3}

## We now know that emissions are unevenly distributed
## How do regions compare?

## Option 1: repeat the density plot and give the region variable to the "fill" aesthetic
## But even with the alpha turned up (transparency), difficult to extract information...

data_countries %>% 
  filter(year==2019) %>% 
  ggplot(.,aes(x=GHG_pc,fill=region_ar6_6)) +
  geom_density(color="#636363",alpha=0.3) +
  theme_bw()

## Option 2: box plots

data_countries %>% 
  filter(year==2019) %>% 
  filter(region_ar6_6!="Intl. Shipping") %>% 
  filter(region_ar6_6!="Intl. Aviation") %>% 
  ggplot(.,aes(x=GHG_pc,y=region_ar6_6,fill=region_ar6_6)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_brewer(palette="Set2") +
  theme_bw() +
  xlab("GHG emissions per capita (tCO2eq/capita)") +
  ggtitle("Distribution of emissions by country and region") + 
  theme(legend.position="none",
        axis.title.y = element_blank())

## Option 3: a more fancy density plot (https://r-graph-gallery.com/ridgeline-plot.html)

library(ggridges)

data_countries %>% 
  filter(year==2019) %>% 
  filter(region_ar6_6!="Intl. Shipping") %>% 
  filter(region_ar6_6!="Intl. Aviation") %>% 
  ggplot(.,aes(x=GHG_pc,y=region_ar6_6,fill=region_ar6_6)) +
  geom_density_ridges(color="#636363",alpha=0.5) +
  scale_fill_brewer(palette="Set2") +
  theme_bw() +
  xlab("GHG emissions per capita (tCO2eq/capita)") +
  ggtitle("Distribution of emissions by country and region") + 
  theme(legend.position="none",
        axis.title.y = element_blank())

```

```{r density_vs_average,fig.width=6,fig.height=3}

## important point: these distributions are weighted by the number of countries, not by the size of their emissions
## in this sense, the region average can be quite different from the distribution, because of a few high-emitters like the USA or China
## for example, here are the true region averages overlayed on the density plot

region_average <- data_countries %>% 
  group_by(region_ar6_6,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE),pop=sum(pop,na.rm=TRUE)) %>% 
  mutate(GHG_pc=GHG/pop) %>% 
  filter(year==2019) %>% 
  filter(region_ar6_6!="Intl. Shipping") %>% 
  filter(region_ar6_6!="Intl. Aviation")

world_average <- data_countries %>% 
  group_by(year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE),pop=sum(pop,na.rm=TRUE)) %>% 
  mutate(GHG_pc=GHG/pop) %>% 
  filter(year==2019)

data_countries %>% 
  filter(year==2019) %>% 
  filter(region_ar6_6!="Intl. Shipping") %>% 
  filter(region_ar6_6!="Intl. Aviation") %>% 
  ggplot(.,aes(x=GHG_pc,y=region_ar6_6,fill=region_ar6_6)) +
  geom_density_ridges(color="#636363",alpha=0.5) +
  geom_point(data=region_average,aes(x=GHG_pc,y=region_ar6_6,fill=region_ar6_6),shape=21,size=3) + ##here the region averages
  geom_vline(data=world_average,aes(xintercept=GHG_pc),linetype="dashed") +
  scale_fill_brewer(palette="Set2") +
  theme_bw() +
  xlab("GHG emissions per capita (tCO2eq/capita)") +
  ggtitle("Distribution of emissions by country and region") + 
  theme(legend.position="none",
        axis.title.y = element_blank())

```

```{r plot_ranking,fig.width=5,fig.height=3}

## How do we get a ranking of the top emitters?
## Simply filter the year and arrange the column you want to rank by in descending order
## Here I cut the data frame and show only the top 15 rows ("head(15)")
## I also filter out very small countries (<1e6 population) as their per capita emissions tend to be skewed

p1 <- data_countries %>% 
  filter(year==2019) %>% 
  arrange(desc(GHG_pc)) %>% 
  filter(pop>1e6) %>% 
  head(15) %>% 
  ggplot(.,aes(x=GHG_pc,y=reorder(country,GHG_pc))) +
  geom_col(color="#636363",fill="#66c2a5") +
  scale_fill_brewer(palette="Set2") +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  xlab("GHG emissions per capita (tCO2eq/capita)") +
  ggtitle("The top 15 emitters by per capita emissions")

p2 <- data_countries %>% 
  filter(year==2019) %>% 
  arrange(desc(GHG)) %>% 
  head(15) %>% 
  mutate(GHG=GHG/1e9) %>% 
  ggplot(.,aes(x=GHG,y=reorder(country,GHG))) +
  geom_col(color="#636363",fill="#66c2a5") +
  scale_fill_brewer(palette="Set2") +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  xlab("GHG emissions (GtCO2eq)") +
  ggtitle("The top 15 emitters by total emissions")

p1
p2

```

```{r plot_ranking_together,fig.width=6,fig.height=6}

## you can also use the "Patchwork" library to merge figures together
## https://patchwork.data-imaginist.com/articles/patchwork.html

library(patchwork)

p1  / p2

```

### 2022-10-24 r-examples/kaya_analysis.Rmd
examples

---
title: "kaya_analysis"
author: "William F. Lamb"
date: "24 9 2022"
output: html_document
---

```{r setup, include=FALSE}

# load packages
library(tidyverse)
library(readxl)

## load data
data_ghg <- read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)
load("Data/data_wdi.RData")

# ## Here I downloaded some data from the IEA and converted into a clean format for our analysis
# library(countrycode)
# data_iea <- read_excel(path = 'Data/iea_total_final_energy_use.xlsx',range = "A2:X27")
# data_iea <- gather(data_iea,year,energy,`2000`:`2020`)
# data_iea <- data_iea %>% 
#   mutate(ISO=countrycode(Country,'country.name','iso3c')) %>% 
#   select(ISO,year,energy) %>% 
#   mutate(energy=energy*1e6) %>% 
#   mutate(year=as.numeric(year))
# 
# save(data_iea,file="Data/data_iea.RData")

load("Data/data_iea.RData")
## the energy units are gigajoules (GJ), by the way.

```

```{r summarise_and_join, include=FALSE}

## for this analysis we use only CO2 emissions, as these are tightly linked to energy use, unlike the other gases

data_kaya <- data_ghg %>% 
  group_by(ISO,country,year) %>% 
  summarise(CO2=sum(CO2,na.rm=TRUE))

data_kaya <- left_join(data_kaya,data_wdi %>% select(-country),by=c("ISO","year"))

data_kaya <- left_join(data_kaya,data_iea,by=c("ISO","year"))

```

```{r calculate_kaya, include=FALSE}

## there are quite a lot of NA values in the dataset. There is no energy data for some countries, so we cant include them in the analysis
## We can use a simple function - na.omit() - to filter only the "complete" rows

data_kaya <- data_kaya %>% 
  na.omit()

## now simply calculate the kaya identity (we already have CO2 and population)

data_kaya <- data_kaya %>% 
  mutate(GDP_pc = gdp_ppp/pop) %>% 
  mutate(energy_intensity = energy/gdp_ppp) %>% 
  mutate(carbon_intensity = CO2/energy)

```

```{r gather_and_plot, include=FALSE,fig.width=8,fig.height=6}

## we have multiple columns, they need to be in a single column for plotting

data_kaya <- gather(data_kaya,var,value,CO2,pop,GDP_pc,energy_intensity,carbon_intensity)

## and we need to normalise the value for each country-variable combination to 1 in 2000

data_kaya <- data_kaya %>% 
  filter(year>=2000) %>% 
  group_by(ISO,country,var) %>% 
  mutate(value=value/first(value))

## now we can plot each country in a facet

data_kaya %>% 
  filter(country %in% c("Australia","Germany","Denmark","France","United Kingdom","Japan","United States","New Zealand")) %>%
  ggplot(.,aes(x=year,y=value,color=var)) +
  geom_line(size=1) +
  geom_hline(aes(yintercept=1)) +
  facet_wrap(.~country) +
  theme_bw() +
  scale_color_brewer(palette="Set2",labels=c("Carbon intensity (CO2/energy)",
                                             "Carbon emissions",
                                             "Energy intensity (energy/GDP)",
                                             "GDP per capita (GDP/pop)",
                                             "Population"),
                     guide = guide_legend(reverse = TRUE)) +
  theme(legend.title=element_blank(),
        axis.title.x = element_blank())

```

### 2022-10-24 r-examples/packages.R

@@ -1,0 +1,6 @@
+install.packages('tidyverse')
+install.packages('readxl')
+install.packages('rmarkdown')
+
+
+install.packages('countrycode')

### 2022-10-24 r-analysis/analysis.Rmd
working files

---
title: "analysis"
output: pdf_document
date: "2022-10-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='hide', message=FALSE, warning=FALSE)
knitr::opts_chunk$set(fig.height = 4, fig.width = 6)
options(knitr.kable.NA = '',knitr.table.format = "latex")
knitr::read_chunk('../r-imports/init.R')
library(kableExtra)
```

```{r init-setup}
```

---
# ##################################################
# Run this when not knitting (and none of the above)
---

```{r, eval = FALSE}
source('r-imports/init.R')
```

---
# Any collab code below this line :)
# ##################################################
---

```{r}

"hi" %>% print()

```

```{r}

```

```{r}

```

### 2022-10-24 r-imports/init.R

@@ -1,3 +1,8 @@
+##################################################################################
+## INITIAL SETUP
+## ---- init-setup ----
+
+
 rm(list = ls(envir = globalenv()),envir = globalenv())
 
 if (!require("pacman")) install.packages("pacman")

### 2022-10-24 r-imports/init.R
bug

@@ -9,7 +9,7 @@ if (!require("pacman")) install.packages("pacman")
 library(pacman)
 
 p_load(magrittr)
-p_load(readxl)
+p_load(openxlsx)
 p_load(ggplot2)
 p_load(tidyverse)
 

### 2022-10-24 r-imports/init.R
test

@@ -22,3 +22,7 @@ p_load(tidyverse)
 "%.%" = function(x,y){paste(x,y,sep = "")}
 cNA = as.character(NA)
 as.numeric.factor = . %>% as.numeric(levels(.))[.]
+
+if("dataghg/" %cin% getwd()) {
+  setwd("../")
+}

### 2022-10-24 r-imports/init.R
clean_up
Delted unnecessary coder

@@ -24,5 +24,5 @@ cNA = as.character(NA)
 as.numeric.factor = . %>% as.numeric(levels(.))[.]
 
 if("dataghg/" %cin% getwd()) {
-  setwd("../")
+  setwd("..")
 }

### 2022-10-24 r-imports/init.R
bam

@@ -22,7 +22,3 @@ p_load(tidyverse)
 "%.%" = function(x,y){paste(x,y,sep = "")}
 cNA = as.character(NA)
 as.numeric.factor = . %>% as.numeric(levels(.))[.]
-
-if("dataghg/" %cin% getwd()) {
-  setwd("../")
-}

### 2022-10-24 r-imports/init.R
gwp100

@@ -9,7 +9,7 @@ if (!require("pacman")) install.packages("pacman")
 library(pacman)
 
 p_load(magrittr)
-p_load(openxlsx)
+p_load(readxl)
 p_load(ggplot2)
 p_load(tidyverse)
 

### 2022-10-24 r-imports/init.R
wdi

@@ -12,6 +12,7 @@ p_load(magrittr)
 p_load(readxl)
 p_load(ggplot2)
 p_load(tidyverse)
+p_load(WDI)
 
 
 "%cin%" = function(x,y){str_detect(y,x)}

### 2022-10-24 r-imports/data.Rmd
working files
ups
test
gwp100
data_wdi loaded

--- 2022-10-24 r-analysis/analysis.Rmd
@@
 ---
-title: "analysis"
+title: "data import"
 output: pdf_document
@@
 
-"hi" %>% print()
+download.file("https://zenodo.org/record/6483002/files/essd_ghg_data_gwp100.xlsx?download=1","data-raw/gwp100.xlsx")
+
+```
+
+```{r}
+
+# ### Using the WDI package to call the Worldbank API and download some indicators
+
+# # gdp at ppp
+
+wdi_gdp<-WDI(country = "all",indicator = "NY.GDP.MKTP.PP.KD",start = 1970,end = 2019,extra=TRUE,language = "en") %>%
+    select(ISO=iso3c, country, year, gdp_ppp=`NY.GDP.MKTP.PP.KD`) %>%
+    filter(!is.na(ISO))
+# 
+# # POP
+wdi_pop<-WDI(country = "all",indicator = "SP.POP.TOTL",start = 1970,end = 2019,extra=TRUE,language = "en")%>%
+    select(ISO=iso3c, country, year, pop=`SP.POP.TOTL`) %>%
+    filter(!is.na(ISO))
+
+data_wdi <- left_join(wdi_pop,wdi_gdp,by=c("ISO","year","country"))
+data_wdi <- data_wdi %>% 
+   arrange(ISO,country,year)
+
+   save(data_wdi,file="data-raw/data_wdi.RData")
 
@@
 ```
-
-```{r}
-
-```

### 2022-10-24 r-prep/prep.Rmd
working files
data base

--- 2022-10-24 r-analysis/analysis.Rmd
@@
 ---
-title: "analysis"
+title: "preprocessing"
 output: pdf_document
@@
 ```{r}
+data_gwp100 = read_excel("data-raw/essd_ghg_data_gwp100.xlsx",sheet = "data")
+load("data-raw/data_wdi.RData") 
+data_wdi %<>% select(-country)
 
-"hi" %>% print()
+data_base = data_gwp100 %>% left_join(data_wdi,by=c("ISO","year"))
 
+save(data_base,file="data-transf/data_base.RData")
 ```

### 2022-10-24 r-analysis/analysis.Rmd

@@
 
-```{r}
-
-"hi" %>% print()
+```{r load data}
+load("data-raw/data_wdi.RData")
 
@@
 
-```{r}
+```{r overview statistics: emissions per capita 2020}
+data_countries <- data_ghg %>% 
+  group_by(ISO,country,year) %>% 
+  summarise(GHG=sum(GHG,na.rm=TRUE))
+
+#data_countries <- left_join(data_countries,data_wdi %>%
+#                              select(-country),by=c("ISO","year"))
+
+data_countries <- data_countries %>% 
+  mutate(GHG_pc=GHG/pop)
 
@@
 
-```{r}
+```{r overview statistics: emissions by sector development 1970:2020 }
+data_countries <- data_ghg %>% 
+  group_by(ISO,country,year) %>% 
+  summarise(GHG=sum(GHG,na.rm=TRUE))
 
 ```
+
+```{r overview statistics: emissions by Gas development 1970:2020 }
+plot_data_gases <- data_ghg %>%       # create a new variable called "data_gases", copied from "data_ghg"
+  group_by(year) %>%                  # choose "years" as our grouping variable
+  summarise(CO2=sum(CO2,na.rm=TRUE),  # sum up the CO2 column by years, ignoring any missing values
+            CH4=sum(CH4,na.rm=TRUE),  # sum up the CH4 column by years, ...
+            N2O=sum(N2O,na.rm=TRUE),  # etc.
+            Fgas=sum(Fgas,na.rm=TRUE))
+
+```
+
+```{r overview statistics: emissions changes }
+
+```
+
+```{r overview statistics: Kaya decomposition }
+data_kaya <- data_kaya %>% 
+  na.omit()
+
+## now simply calculate the kaya identity (we already have CO2 and population)
+
+data_kaya <- data_kaya %>% 
+  mutate(GDP_pc = gdp_ppp/pop) %>% 
+  mutate(energy_intensity = energy/gdp_ppp) %>% 
+  mutate(carbon_intensity = CO2/energy)
+```

### 2022-10-24 r-analysis/analysis.Rmd

@@
 ```{r load data}
-load("data-raw/data_wdi.RData")
+load("data-transf/data_base.RData")
+
+#load("data-raw/data_kaya.RData")
 
@@
 
-```{r overview statistics: emissions per capita 2020}
+```{r overview statistics: emissions per capita development 1970:2020}
 data_countries <- data_ghg %>% 
@@
 data_countries <- data_ghg %>% 
-  group_by(ISO,country,year) %>% 
+  group_by(ISO,country,year,sector) %>% 
   summarise(GHG=sum(GHG,na.rm=TRUE))
@@
 ```{r overview statistics: emissions changes }
+data_change <- data_ghg %>% 
+  group_by(ISO,country,region_ar6_6,year) %>% 
+  summarise(GHG=sum(GHG,na.rm=TRUE))
+
+## in this next chunk I calculate 3 different types of changes for the time period 2010-2019
+
+data_change <- data_change %>% 
+  filter(year %in% c(2010,2019)) %>% 
+  group_by(ISO,country) %>% 
+  mutate(change_abs = last(GHG)-first(GHG),               ## absolute change, or the difference in emissions between t2 and t1
+         change_rel = change_abs/first(GHG),              ## relative change, or the ratio of absolute change to emissions in t1
+         change_avg_annual = ((last(GHG)/first(GHG))^(1/(2019-2010))-1)) ## average annual change using the CGAR formula
 

### 2022-10-24 r-prep/prep.Rmd
upd

@@
 load("data-raw/data_wdi.RData") 
-data_wdi %<>% select(-country)
+data_wdi %<>%
+  select(-country)
 
-data_base = data_gwp100 %>% left_join(data_wdi,by=c("ISO","year"))
+data_base = data_gwp100 %>%
+  left_join(data_wdi,by=c("ISO","year")) %>%
+  mutate(GHG_pc = GHG/pop) %>%
+  mutate(GDP_pc = gdp_ppp/pop)
 
@@
 ```{r}
+load("data-raw/data_iea.RData")
 
+data_kaya = data_base %>% 
+  group_by(ISO,country,year,GDP_pc) %>% 
+  summarise(CO2=sum(CO2,na.rm=TRUE)) %>%
+  left_join(data_iea,data_iea,by=c("ISO","year")) %>%
+  mutate(energy_intensity = energy/GDP_pc) %>%
+  mutate(carbon_intensity = CO2/energy)
+
+save(data_base,file="data-transf/data_kaya.RData")
 ```

### 2022-10-24 r-prep/prep.Rmd
na omit

@@
   mutate(energy_intensity = energy/GDP_pc) %>%
-  mutate(carbon_intensity = CO2/energy)
+  mutate(carbon_intensity = CO2/energy) %>%
+  na.omit()
 

### 2022-10-24 r-imports/init.R
theme

@@ -24,3 +24,52 @@ p_load(ggridges)
 "%.%" = function(x,y){paste(x,y,sep = "")}
 cNA = as.character(NA)
 as.numeric.factor = . %>% as.numeric(levels(.))[.]
+
+
+theme_ghg = function(){ 
+  #font <- "Georgia"   #assign font family up front
+  
+  theme_minimal() %+replace%    #replace elements we want to change
+    
+    theme(
+      
+      # #grid elements
+      # panel.grid.major = element_blank(),    #strip major gridlines
+      # panel.grid.minor = element_blank(),    #strip minor gridlines
+      # axis.ticks = element_blank(),          #strip axis ticks
+      # 
+      # #since theme_minimal() already strips axis lines, 
+      # #we don't need to do that again
+      # 
+      # #text elements
+      # plot.title = element_text(             #title
+      #   family = font,            #set font family
+      #   size = 20,                #set font size
+      #   face = 'bold',            #bold typeface
+      #   hjust = 0,                #left align
+      #   vjust = 2),               #raise slightly
+      # 
+      # plot.subtitle = element_text(          #subtitle
+      #   family = font,            #font family
+      #   size = 14),               #font size
+      # 
+      # plot.caption = element_text(           #caption
+      #   family = font,            #font family
+      #   size = 9,                 #font size
+      #   hjust = 1),               #right align
+      # 
+      # axis.title = element_text(             #axis titles
+      #   family = font,            #font family
+      #   size = 10),               #font size
+      # 
+      # axis.text = element_text(              #axis text
+      #   family = font,            #axis famuly
+      #   size = 9),                #font size
+      # 
+      # axis.text.x = element_text(            #margin for axis text
+      #   margin=margin(5, b = 10))
+      # 
+      # #since the legend often requires manual tweaking 
+      # #based on plot content, don't define it here
+    )
+}

### 2022-10-24 r-analysis/analysis.Rmd
Analysis on percapita emissiions

@@
 ```{r overview statistics: emissions per capita development 1970:2020}
-data_countries <- data_ghg %>% 
-  group_by(ISO,country,year) %>% 
-  summarise(GHG=sum(GHG,na.rm=TRUE))
 
-#data_countries <- left_join(data_countries,data_wdi %>%
-#                              select(-country),by=c("ISO","year"))
+#summarize per capita emissions by country
+data_countries <- data_base %>% 
+  group_by(country,year,region_ar6_6,pop) %>% 
+  summarise(GHG_pc=sum(GHG_pc,na.rm=TRUE))
 
-data_countries <- data_countries %>% 
-  mutate(GHG_pc=GHG/pop)
+#to show chinas development in rleations to diffrent world regions
+
+data_regions <- data_countries %>%
+  mutate(pop=replace_na(pop,0)) %>% # check if zero transformation changes statitstics
+  group_by(region_ar6_6,year) %>% 
+  summarise(GHG_pc=weighted.mean(GHG_pc,pop,na.rm=TRUE)) %>% 
+  rename(region = region_ar6_6) %>% 
+  filter(region %ni% c("Intl. Aviation", "Intl. Shipping"))
+
+# combining data frames
+
+china_and_regions <- rbind(data_regions, data_china)
+
+glimpse(china_and_regions)
+# plotting
+
+china_and_regions %>% 
+  ggplot(.,aes(y=GHG_pc,fill=as.factor(region), x=year)) +
+  geom_line(color="#636363",alpha=0.3) +
+  theme_ghg()
+
+ggplot(china_and_regions,aes(x=year,y=GHG_pc,fill=region)) +
+  geom_area(color="#636363") +              ## Define a colour (grey) to outline each area 
+  ylab("Total GHG emissions (GtCO2eq)") +   ## replace the label on the y axis
+  theme_bw() +                              ## Use my favourite "black/white" theme 
+  scale_fill_brewer(palette="Set2") +       ## Use my favourite color scale from https://colorbrewer2.org
+  theme(axis.title.x = element_blank()) +   ## Remove the x axis label (years is obvious)
+  ggtitle("Total anthropogenic GHG emissions continue to grow")
+
+  #ggplot(.,aes(x=GHG_pc,y=,fill=Region)) +
+  #  geom_density_ridges(color="#636363",alpha=0.5) +
+  #  scale_fill_brewer(palette="Set2") +
+  #  theme_bw() +
+   # xlab("GHG emissions per capita (tCO2eq/capita)") +
+  #  ggtitle("Distribution of emissions by country and region") + 
+  #  theme(legend.position="none",
+  #        axis.title.y = element_blank())
 

### 2022-10-24 r-analysis/china_and_regions.R
shiny

@@ -1,0 +1,25 @@
+load("data-transf/data_base.RData")
+
+#summarize per capita emissions by country
+data_countries <- data_base %>% 
+  group_by(country,year,region_ar6_6,pop) %>% 
+  summarise(GHG_pc=sum(GHG_pc,na.rm=TRUE))  
+
+data_china<-data_countries %>% 
+  filter(country=="China") %>% 
+  rename(region = country)
+
+
+#to show chinas development in rleations to diffrent world regions
+
+data_regions <- data_countries %>%
+  mutate(pop=replace_na(pop,0)) %>% # check if zero transformation changes statitstics
+  group_by(region_ar6_6,year) %>% 
+  summarise(GHG_pc=weighted.mean(GHG_pc,pop,na.rm=TRUE)) %>% 
+  rename(region = region_ar6_6) %>% 
+  filter(region %ni% c("Intl. Aviation", "Intl. Shipping"))
+
+# combining data frames
+
+china_and_regions <- rbind(data_regions, data_china) %>%
+  filter(year <= {{YEAR}})

### 2022-10-24 r-plots/china_and_regions.R

@@ -1,0 +1,7 @@
+ggplot(china_and_regions,aes(x=year,y=GHG_pc,fill=region)) +
+  geom_area(color="#636363") +              ## Define a colour (grey) to outline each area 
+  ylab("Total GHG emissions (GtCO2eq)") +   ## replace the label on the y axis
+  theme_bw() +                              ## Use my favourite "black/white" theme 
+  scale_fill_brewer(palette="Set2") +       ## Use my favourite color scale from https://colorbrewer2.org
+  theme(axis.title.x = element_blank()) +   ## Remove the x axis label (years is obvious)
+  ggtitle("Total anthropogenic GHG emissions continue to grow")

### 2022-10-24 r-report/shiny/app.R

@@ -1,0 +1,42 @@
+setwd("../../")
+
+source('r-imports/init.R')
+
+p_load(shiny)
+
+ui = fluidPage(
+
+    titlePanel("GHG Emissions"),
+
+    sidebarLayout(
+        sidebarPanel(
+            sliderInput("year",
+                        "Year:",
+                        min = 1970,
+                        max = 2019,
+                        value = 2019)
+        ),
+
+        mainPanel(
+           plotOutput("distPlot")
+        )
+    )
+)
+
+
+server = function(input, output) {
+
+  setwd("../../")
+  
+  output$distPlot = renderPlot({
+    
+    YEAR = input$year
+    
+    source("r-analysis/china_and_regions.R", local = TRUE, print.eval = TRUE)
+    source("r-plots/china_and_regions.R", local = TRUE, print.eval = TRUE)
+    
+  })
+}
+
+
+shinyApp(ui = ui, server = server)

### 2022-10-24 r-analysis/analysis.Rmd
added china
aktueller stand GHG per cap

@@
 
+data_china<-data_countries %>% 
+  filter(country=="China") %>% 
+  rename(region = country)
+
 #to show chinas development in rleations to diffrent world regions
@@
 glimpse(china_and_regions)
+
 # plotting
@@
 china_and_regions %>% 
-  ggplot(.,aes(y=GHG_pc,fill=as.factor(region), x=year)) +
-  geom_line(color="#636363",alpha=0.3) +
+   ggplot( aes(x=year, y=GHG_pc, group=region, color=region)) +
+    geom_line() +
     theme_ghg()
+
+#set order of vlaues
+
+levels<-china_and_regions %>%
+  filter(year==2019) %>% 
+  arrange(desc(GHG_pc)) %>% 
+  pull(region)
+
+levels
+
+levels<-c("China",levels[-4])
+
+china_and_regions %>%
+  filter(year==2019) %>%
+  mutate(region=fct_relevel(region,levels)) %>% 
+   ggplot(., aes(y=GHG_pc,x=region, fill=as.factor(region) )) + 
+    geom_bar( stat = 'identity') +
+    scale_fill_brewer(palette = "Set2") +
+    theme(legend.position="none")
 

### 2022-10-24 r-analysis/analysis.Rmd
exported  code to plot and datasource files

--- 2022-10-24 r-analysis/analysis.Rmd
@@
 ```{r overview statistics: emissions per capita development 1970:2020}
-data_countries <- data_ghg %>% 
-  group_by(ISO,country,year) %>% 
-  summarise(GHG=sum(GHG,na.rm=TRUE))
+YEAR = 2019
 
-#data_countries <- left_join(data_countries,data_wdi %>%
-#                              select(-country),by=c("ISO","year"))
-
-data_countries <- data_countries %>% 
-  mutate(GHG_pc=GHG/pop)
+source("r-analysis/china_and_regions.R", local = TRUE, print.eval = TRUE)
+source("r-plots/china_and_regions.R", local = TRUE, print.eval = TRUE)
 

### 2022-10-24 r-plots/china_and_regions.R

@@ -1,7 +1,0 @@
-ggplot(china_and_regions,aes(x=year,y=GHG_pc,fill=region)) +
-  geom_area(color="#636363") +              ## Define a colour (grey) to outline each area 
-  ylab("Total GHG emissions (GtCO2eq)") +   ## replace the label on the y axis
-  theme_bw() +                              ## Use my favourite "black/white" theme 
-  scale_fill_brewer(palette="Set2") +       ## Use my favourite color scale from https://colorbrewer2.org
-  theme(axis.title.x = element_blank()) +   ## Remove the x axis label (years is obvious)
-  ggtitle("Total anthropogenic GHG emissions continue to grow")

### 2022-10-24 r-plots/plot_bar_percapita_emissions_2019.R

@@ -1,0 +1,11 @@
+china_and_regions %>%
+  filter(year==2019) %>%
+  ggplot(., aes(y=GHG_pc,x=factor(region,levels=level), fill=as.factor(region) )) + 
+  geom_bar( stat = 'identity') +
+  scale_fill_brewer(palette = "Set2") +
+  theme(legend.position="none")+             
+  ylab("Percapita Emissions (GtCO2eq)") +   
+  theme_ghg()+                               
+  scale_fill_brewer(palette="Set2") +       
+  theme(axis.title.x = element_blank()) +   
+  ggtitle("Per Capita Emissions China and World Regions in 2019 ")

### 2022-10-24 r-plots/plot_line_percapita_emissions_china_and_regions.R

@@ -1,0 +1,11 @@
+china_and_regions %>%
+  filter(region==c("China", "Developed Countries","Asia and developing Pacific")) %>% #think about whether another comparison makes sense? 
+  ggplot( aes(x=year, y=GHG_pc, group=region, color=region)) +
+  geom_line() +
+  scale_fill_brewer(palette = "Set2") +
+  theme(legend.position="none")+            
+  ylab("Per Capita Emissions (GtCO2eq)") +   
+  theme_ghg()+                              
+  scale_fill_brewer(palette="Set2") +       
+  theme(axis.title.x = element_blank()) +   
+  ggtitle("Per Capita Emissions China vs. Developed Countries vs. Asia & Developing Pacific 1970-2019 ")

### 2022-10-24 r-analysis/analysis.Rmd
bugfix

@@
 
-source("r-analysis/china_and_regions.R", local = TRUE, print.eval = TRUE)
-source("r-plots/china_and_regions.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/per_capita_emissions_china_and_regions", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_bar_per_capita_emissions_2019", local = TRUE, print.eval = TRUE)
 

### 2022-10-24 r-analysis/per_capita_emissions_china_and_regions.R
sum
push

@@ -23,3 +23,6 @@ data_regions <- data_countries %>%
 
 china_and_regions <- rbind(data_regions, data_china) %>%
   filter(year <= {{YEAR}})
+
+
+

### 2022-10-24 r-plots/plot_bar_per_capita_emissions_2019.R

@@ -1,5 +1,16 @@
+#set levels 
+
+plot_level<-china_and_regions %>%
+  filter(year=={{YEAR}}) %>% 
+  arrange(desc(GHG_pc)) %>% 
+  pull(region)
+
+plot_level<-c("China",level[-4])
+
+#plot
+
 china_and_regions %>%
-  filter(year==2019) %>%
+  filter(year=={{YEAR}}) %>%
   ggplot(., aes(y=GHG_pc,x=factor(region,levels=level), fill=as.factor(region) )) + 
   geom_bar( stat = 'identity') +
   scale_fill_brewer(palette = "Set2") +
@@ -7,5 +18,7 @@ china_and_regions %>%
   ylab("Percapita Emissions (GtCO2eq)") +   
   theme_ghg()+                               
   scale_fill_brewer(palette="Set2") +       
-  theme(axis.title.x = element_blank()) +   
-  ggtitle("Per Capita Emissions China and World Regions in 2019 ")
+  theme(axis.title.x = element_blank(), 
+        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
+        legend.position="none") +   
+  ggtitle("Per Capita Emissions China and World Regions in " %.% YEAR)

### 2022-10-24 r-plots/plot_line_percapita_emissions_china_and_regions.R

@@ -9,3 +9,4 @@ china_and_regions %>%
   scale_fill_brewer(palette="Set2") +       
   theme(axis.title.x = element_blank()) +   
   ggtitle("Per Capita Emissions China vs. Developed Countries vs. Asia & Developing Pacific 1970-2019 ")
+

### 2022-10-24 r-analysis/data_per_capita_emissions.R
Changed_variables_4-shiny

@@ -6,7 +6,7 @@ data_countries <- data_base %>%
   summarise(GHG_pc=sum(GHG_pc,na.rm=TRUE))  
 
 data_china<-data_countries %>% 
-  filter(country=="China") %>% 
+  filter(country=={{COUNTRY}}) %>% 
   rename(region = country)
 
 

### 2022-10-24 r-analysis/meta.R
app

@@ -1,0 +1,5 @@
+load("data-transf/data_base.RData")
+
+meta_countries = data_base %>% distinct(country,ISO)
+meta_country_list = meta_countries %$% setNames(country,ISO)
+meta_country_list

### 2022-10-24 r-report/shiny/app_bar_per_capita_emissions.R

@@ -1,0 +1,48 @@
+setwd("../../")
+
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
+p_load(shiny)
+
+ui = fluidPage(
+  
+  titlePanel("GHG Emissions"),
+
+  sidebarLayout(
+      sidebarPanel(
+          sliderInput("year",
+                      "Year:",
+                      min = 1970,
+                      max = 2019,
+                      value = 2019),
+          selectInput("country",
+                      "Country:",
+                      meta_country_list,
+                      selected = "CHN"
+                      )
+    ),
+
+    mainPanel(
+         plotOutput("distPlot")
+    )
+  )
+)
+
+
+server = function(input, output) {
+
+  setwd("../../")
+  
+  output$distPlot = renderPlot({
+    
+    YEAR = input$year
+    
+    source("r-analysis/per_capita_emissions_china_and_regions.R", local = TRUE, print.eval = TRUE)
+    source("r-plots/plot_bar_per_capita_emissions_2019.R", local = TRUE, print.eval = TRUE)
+    
+  })
+}
+
+
+shinyApp(ui = ui, server = server)

### 2022-10-24 r-imports/init.R
added EU27

@@ -14,6 +14,7 @@ p_load(ggplot2)
 p_load(tidyverse)
 p_load(WDI)
 p_load(ggridges)
+p_load(eurostat)
 
 
 "%cin%" = function(x,y){str_detect(y,x)}

### 2022-10-24 r-analysis/meta.R
shiny 1

@@ -1,5 +1,5 @@
 load("data-transf/data_base.RData")
 
 meta_countries = data_base %>% distinct(country,ISO)
-meta_country_list = meta_countries %$% setNames(country,ISO)
-meta_country_list
+meta_country_list_iso = meta_countries %$% setNames(ISO,country)
+meta_country_list = meta_countries %$% setNames(country,country)

### 2022-10-24 r-plots/plot_bar_per_capita_emissions.R

@@ -2,17 +2,17 @@
 
 plot_level<-china_and_regions %>%
   filter(year=={{YEAR}}) %>% 
-  filter(country!={{COUNTRY}})
+  filter(region!={{COUNTRY}}) %>%
   arrange(desc(GHG_pc)) %>% 
   pull(region)
 
-plot_level<-c({{COUNTRY}},level)
+plot_level<-c(COUNTRY,plot_level)
 
 #plot
 
 china_and_regions %>%
   filter(year=={{YEAR}}) %>%
-  ggplot(., aes(y=GHG_pc,x=factor(region,levels=level), fill=as.factor(region) )) + 
+  ggplot(., aes(y=GHG_pc,x=factor(region,levels=plot_level), fill=as.factor(region) )) + 
   geom_bar( stat = 'identity') +
   scale_fill_brewer(palette = "Set2") +
   theme(legend.position="none")+             
@@ -22,4 +22,4 @@ china_and_regions %>%
   theme(axis.title.x = element_blank(), 
         axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
         legend.position="none") +   
-  ggtitle("Per Capita Emissions China and World Regions in " %.% YEAR)
+  ggtitle("Per Capita Emissions " %.% COUNTRY %.% " and World Regions in " %.% YEAR)

### 2022-10-24 r-report/shiny/app_bar_per_capita_emissions.R

@@ -19,7 +19,7 @@ ui = fluidPage(
           selectInput("country",
                       "Country:",
                       meta_country_list,
-                      selected = "CHN"
+                      selected = "China"
                       )
     ),
 
@@ -37,9 +37,10 @@ server = function(input, output) {
   output$distPlot = renderPlot({
     
     YEAR = input$year
+    COUNTRY = input$country
     
-    source("r-analysis/per_capita_emissions_china_and_regions.R", local = TRUE, print.eval = TRUE)
-    source("r-plots/plot_bar_per_capita_emissions_2019.R", local = TRUE, print.eval = TRUE)
+    source("r-analysis/data_per_capita_emissions.R", local = TRUE, print.eval = TRUE)
+    source("r-plots/plot_bar_per_capita_emissions.R", local = TRUE, print.eval = TRUE)
     
   })
 }

### 2022-10-24 r-prep/prep.Rmd
2020

@@
   mutate(GHG_pc = GHG/pop) %>%
-  mutate(GDP_pc = gdp_ppp/pop)
+  mutate(GDP_pc = gdp_ppp/pop) %>%
+  filter(year <= 2019) %>% 
+  mutate(EU= case_when(country %cin% eurostat::eu_countries[2]~ "Yes"))
 

### 2022-10-24 r-analysis/analysis.Rmd
added EU to PerCapAnalysis

--- 2022-10-24 r-analysis/analysis.Rmd
@@
 
-```{r overview statistics: emissions per capita development 1970:2020}
+```{r overview statistics: emissions per capita }
 YEAR = 2019
-
-source("r-analysis/china_and_regions.R", local = TRUE, print.eval = TRUE)
-source("r-plots/china_and_regions.R", local = TRUE, print.eval = TRUE)
+COUNTRY= "China"    
+source("r-analysis/per_capita_emissions_china_and_regions", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_bar_per_capita_emissions_2019", local = TRUE, print.eval = TRUE)
 
@@
 
-```{r overview statistics: emissions by sector development 1970:2020 }
-data_countries <- data_ghg %>% 
-  group_by(ISO,country,year,sector) %>% 
+```{r overview statistics: emissions by sector }
+data_countries <- data_base %>% 
+  group_by(ISO,country,year,sector_title) %>% 
   summarise(GHG=sum(GHG,na.rm=TRUE))
+
+#plot
+
+```
+
+```{r overview statistics: absolute emissions by gas}
+data_countries <- data_base %>% 
+  group_by(ISO,country,year,sector_title) %>% 
+  summarise(GHG=sum(GHG,na.rm=TRUE))
+
+#plot
 

### 2022-10-24 r-prep/prep.Rmd
added EU to PerCapAnalysis

--- 2022-10-24 r-prep/prep.Rmd
@@
   mutate(GHG_pc = GHG/pop) %>%
-  mutate(GDP_pc = gdp_ppp/pop)
+  mutate(GDP_pc = gdp_ppp/pop) %>%
+  filter(year <= 2019) %>% 
+  mutate(EU= case_when(country %cin% eurostat::eu_countries[2]~ TRUE))
 

### 2022-10-24 r-analysis/data_per_capita_emissions.R

@@ -2,17 +2,23 @@ load("data-transf/data_base.RData")
 
 #summarize per capita emissions by country
 data_countries <- data_base %>% 
-  group_by(country,year,region_ar6_6,pop) %>% 
+  group_by(country,year,region_ar6_6,pop,EU) %>% 
   summarise(GHG_pc=sum(GHG_pc,na.rm=TRUE))  
 
 data_china<-data_countries %>% 
   filter(country=={{COUNTRY}}) %>% 
   rename(region = country)
 
+data_EU<-data_countries %>% 
+  filter(EU) %>% 
+  select(-country) %>%
+  mutate(region_ar6_6 = "EU")
 
 #to show chinas development in rleations to diffrent world regions
 
-data_regions <- data_countries %>%
+
+data_regions <- data_countries %>% 
+  rbind(data_EU) %>% #appending data for EU countries to show in plot
   mutate(pop=replace_na(pop,0)) %>% # check if zero transformation changes statitstics
   group_by(region_ar6_6,year) %>% 
   summarise(GHG_pc=weighted.mean(GHG_pc,pop,na.rm=TRUE)) %>% 
@@ -21,7 +27,8 @@ data_regions <- data_countries %>%
 
 # combining data frames
 
-china_and_regions <- rbind(data_regions, data_china) %>%
+china_and_regions <- data_regions %>% 
+  rbind(data_china) %>%
   filter(year <= {{YEAR}})
 
 

### 2022-10-24 r-analysis/data_per_capita_emissions.R
EU-28

@@ -12,7 +12,7 @@ data_china<-data_countries %>%
 data_EU<-data_countries %>% 
   filter(EU) %>% 
   select(-country) %>%
-  mutate(region_ar6_6 = "EU")
+  mutate(region_ar6_6 = "EU-28")
 
 #to show chinas development in rleations to diffrent world regions
 

### 2022-10-24 r-plots/plot_line_per_capita_emissions_regions.R
plot2

@@ -1,5 +1,5 @@
 china_and_regions %>%
-  filter(region==c("China", "Developed Countries","Asia and developing Pacific")) %>% #think about whether another comparison makes sense? 
+  filter(region==c(COUNTRY, "Developed Countries","Asia and developing Pacific")) %>% #think about whether another comparison makes sense? 
   ggplot( aes(x=year, y=GHG_pc, group=region, color=region)) +
   geom_line() +
   scale_fill_brewer(palette = "Set2") +
@@ -8,5 +8,5 @@ china_and_regions %>%
   theme_ghg()+                              
   scale_fill_brewer(palette="Set2") +       
   theme(axis.title.x = element_blank()) +   
-  ggtitle("Per Capita Emissions China vs. Developed Countries vs. Asia & Developing Pacific 1970-2019 ")
+  ggtitle("Per Capita Emissions " %.% COUNTRY %.% " vs. Dev' Countries vs. Asia & Dev' Pacific, 1970-" %.% YEAR)
 

### 2022-10-24 r-analysis/data_per_capita_emissions.R
renaming

@@ -5,7 +5,7 @@ data_countries <- data_base %>%
   group_by(country,year,region_ar6_6,pop,EU) %>% 
   summarise(GHG_pc=sum(GHG_pc,na.rm=TRUE))  
 
-data_china<-data_countries %>% 
+data_first_country<-data_countries %>% 
   filter(country=={{COUNTRY}}) %>% 
   rename(region = country)
 
@@ -13,6 +13,10 @@ data_EU<-data_countries %>%
   filter(EU) %>% 
   select(-country) %>%
   mutate(region_ar6_6 = "EU-28")
+
+data_us<-data_countries %>% 
+  filter(country=="United States") %>% 
+  rename(region = country)
 
 #to show chinas development in rleations to diffrent world regions
 
@@ -27,8 +31,8 @@ data_regions <- data_countries %>%
 
 # combining data frames
 
-china_and_regions <- data_regions %>% 
-  rbind(data_china) %>%
+country_and_regions <- data_regions %>% 
+  rbind(data_first_country,data_us) %>%
   filter(year <= {{YEAR}})
 
 

### 2022-10-24 r-plots/plot_bar_per_capita_emissions.R

@@ -1,6 +1,6 @@
 #set levels 
 
-plot_level<-china_and_regions %>%
+plot_level<-country_and_regions %>%
   filter(year=={{YEAR}}) %>% 
   filter(region!={{COUNTRY}}) %>%
   arrange(desc(GHG_pc)) %>% 
@@ -10,7 +10,7 @@ plot_level<-c(COUNTRY,plot_level)
 
 #plot
 
-china_and_regions %>%
+country_and_regions %>%
   filter(year=={{YEAR}}) %>%
   ggplot(., aes(y=GHG_pc,x=factor(region,levels=plot_level), fill=as.factor(region) )) + 
   geom_bar( stat = 'identity') +

### 2022-10-24 r-plots/plot_line_per_capita_emissions_regions.R

@@ -1,5 +1,5 @@
-china_and_regions %>%
-  filter(region==c(COUNTRY, "Developed Countries","Asia and developing Pacific")) %>% #think about whether another comparison makes sense? 
+country_and_regions %>%
+  filter(region==c(COUNTRY, "Developed Countries","Asia and developing Pacific")) %>% #line breaks 
   ggplot( aes(x=year, y=GHG_pc, group=region, color=region)) +
   geom_line() +
   scale_fill_brewer(palette = "Set2") +
@@ -8,5 +8,5 @@ china_and_regions %>%
   theme_ghg()+                              
   scale_fill_brewer(palette="Set2") +       
   theme(axis.title.x = element_blank()) +   
-  ggtitle("Per Capita Emissions " %.% COUNTRY %.% " vs. Dev' Countries vs. Asia & Dev' Pacific, 1970-" %.% YEAR)
+  ggtitle("Per Capita Emissions " %.% COUNTRY %.% " vs. Developed Countries vs. Asia & Developing Pacific, 1970-" %.% YEAR)
 

### 2022-10-24 r-plots/plot_bar_per_capita_emissions.R
Changed Labels

@@ -14,11 +14,11 @@ country_and_regions %>%
   filter(year=={{YEAR}}) %>%
   ggplot(., aes(y=GHG_pc,x=factor(region,levels=plot_level), fill=as.factor(region) )) + 
   geom_bar( stat = 'identity') +
-  scale_fill_brewer(palette = "Set2") +
+  scale_fill_brewer(palette = "Set1") +
   theme(legend.position="none")+             
-  ylab("Percapita Emissions (GtCO2eq)") +   
+  ylab("Percapita Emissions (tCO2eq)") +   
   theme_ghg()+                               
-  scale_fill_brewer(palette="Set2") +       
+  scale_fill_brewer(palette="Set1") +       
   theme(axis.title.x = element_blank(), 
         axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
         legend.position="none") +   

### 2022-10-24 r-plots/plot_line_per_capita_emissions_regions.R

@@ -4,7 +4,7 @@ country_and_regions %>%
   geom_line() +
   scale_fill_brewer(palette = "Set2") +
   theme(legend.position="none")+            
-  ylab("Per Capita Emissions (GtCO2eq)") +   
+  ylab("Per Capita Emissions (tCO2eq)") +   
   theme_ghg()+                              
   scale_fill_brewer(palette="Set2") +       
   theme(axis.title.x = element_blank()) +   

### 2022-10-24 r-plots/plot_line_per_capita_emissions_regions.R
Updated Lineplot

@@ -1,5 +1,5 @@
 country_and_regions %>%
-  filter(region==c(COUNTRY, "Developed Countries","Asia and developing Pacific")) %>% #line breaks 
+  filter(region==c(COUNTRY, "Asia and developing Pacific","EU-28", "United States")) %>% #line breaks 
   ggplot( aes(x=year, y=GHG_pc, group=region, color=region)) +
   geom_line() +
   scale_fill_brewer(palette = "Set2") +
@@ -8,5 +8,5 @@ country_and_regions %>%
   theme_ghg()+                              
   scale_fill_brewer(palette="Set2") +       
   theme(axis.title.x = element_blank()) +   
-  ggtitle("Per Capita Emissions " %.% COUNTRY %.% " vs. Developed Countries vs. Asia & Developing Pacific, 1970-" %.% YEAR)
+  ggtitle("Per Capita Emissions " %.% COUNTRY %.% " vs. selected Regions and US, 1970-" %.% YEAR)
 

### 2022-11-14 r-prep/prep.Rmd
EU-28
renaming
data set

--- 2022-10-24 r-prep/prep.Rmd
@@
 ```{r}
-data_gwp100 = read_excel("data-raw/essd_ghg_data_gwp100.xlsx",sheet = "data")
+data_gwp100 = read_excel("data-raw/egr22_country_data.xlsx",sheet = "data")
 load("data-raw/data_wdi.RData") 
@@
 data_base = data_gwp100 %>%
+  rename(ISO = iso) %>%
   left_join(data_wdi,by=c("ISO","year")) %>%
   mutate(GHG_pc = GHG/pop) %>%
-  mutate(GDP_pc = gdp_ppp/pop)
+  mutate(GDP_pc = gdp_ppp/pop) %>%
+  filter(year <= 2020) %>% 
+  mutate(
+    EU = case_when(country %cin% eurostat::eu_countries[2]~ TRUE),
+
+  )
 

### 2022-11-14 r-imports/data.Rmd
lulucf fix

@@
 download.file("https://zenodo.org/record/6483002/files/essd_ghg_data_gwp100.xlsx?download=1","data-raw/gwp100.xlsx")
+download.file("https://zenodo.org/record/7190601/files/LULUCF%20NGHGI%20database%20August%202022.xlsx?download=1","data-raw/lulucf.xlsx")
+
+library(httr)
+url = "https://zenodo.org/record/7190601/files/LULUCF%20NGHGI%20database%20August%202022.xlsx?download=1"
+GET(url, write_disk("data-raw/lulucf.xlsx", overwrite=TRUE))
 

### 2022-11-14 r-prep/prep.Rmd
lulucf fix

--- 2022-10-24 r-prep/prep.Rmd
@@
 data_gwp100 = read_excel("data-raw/essd_ghg_data_gwp100.xlsx",sheet = "data")
+
+#data_lulucf = read_excel("data-raw/lulucf.xlsx",sheet = "data")
+data_lulucf = read_excel("data-raw/egr22_country_data.xlsx",sheet = "data") %>%
+  rename(ISO = iso, co2_lulucf = CO2_LULUCF_NGHGI) %>%
+  select(ISO, year, co2_lulucf)
+
 load("data-raw/data_wdi.RData") 
@@
   left_join(data_wdi,by=c("ISO","year")) %>%
+  left_join(data_lulucf,by=c("ISO","year")) %>%
   mutate(GHG_pc = GHG/pop) %>%
@@
   filter(year <= 2019) %>% 
-  mutate(EU= case_when(country %cin% eurostat::eu_countries[2]~ TRUE))
+  mutate(
+    EU = case_when(country %in% eurostat::eu_countries[2]$name~ TRUE, TRUE ~ FALSE),
+
+  )
 

### 2022-11-14 r-prep/prep.Rmd
kaya data

@@
 data_kaya = data_base %>% 
-  group_by(ISO,country,year,GDP_pc) %>% 
+  group_by(ISO,country,year,GDP_pc,pop) %>% 
   summarise(CO2=sum(CO2,na.rm=TRUE)) %>%
-  left_join(data_iea,data_iea,by=c("ISO","year")) %>%
+  left_join(data_iea,by=c("ISO","year")) %>%
   mutate(energy_intensity = energy/GDP_pc) %>%
   mutate(carbon_intensity = CO2/energy) %>%
-  na.omit()
+  na.omit() %>% 
+  pivot_longer(c(CO2,pop,GDP_pc,energy_intensity,carbon_intensity),names_to = "var",values_to = "value")
 
-save(data_base,file="data-transf/data_kaya.RData")
+save(data_kaya,file="data-transf/data_kaya.RData")
 ```

### 2022-11-14 r-imports/data.Rmd
backlog

@@
 download.file("https://zenodo.org/record/6483002/files/essd_ghg_data_gwp100.xlsx?download=1","data-raw/gwp100.xlsx")
-download.file("https://zenodo.org/record/7190601/files/LULUCF%20NGHGI%20database%20August%202022.xlsx?download=1","data-raw/lulucf.xlsx")
+#download.file("https://zenodo.org/record/7190601/files/LULUCF%20NGHGI%20database%20August%202022.xlsx?download=1","data-raw/lulucf.xlsx")
 

### 2022-11-14 r-prep/prep.Rmd
prep

@@
   mutate(
-    EU = case_when(country %in% eurostat::eu_countries[2]$name~ TRUE, TRUE ~ FALSE),
-
-  )
+    EU = country %in% eurostat::eu_countries[2]$name,
+    woc = country != "China",
+    deving_woc = woc & data_base$region_ar6_dev == "developing",
+    deved = data_base$region_ar6_dev == "developed",
+    adp_region_woc = woc & data_base$region_ar6_6 == "Asia and developing Pacific",
+    adp_region_deving_woc = adp_region_woc & deving_woc
+  ) %>% 
+  select(-woc)
 

### 2022-11-14 r-prep/prep.Rmd
countries & kaya add

--- 2022-11-14 r-prep/prep.Rmd
@@
   mutate(
-    EU = case_when(country %in% eurostat::eu_countries[2]$name~ TRUE, TRUE ~ FALSE),
-
-  )
+    EU = country %in% eurostat::eu_countries[2]$name,
+    woc = country != "China",
+    deving_woc = woc & region_ar6_dev == "developing",
+    deved = region_ar6_dev == "developed",
+    adp_region_woc = woc & region_ar6_6 == "Asia and developing Pacific",
+    adp_region_deving_woc = adp_region_woc & deving_woc
+  ) %>% 
+  select(-woc)
 
@@
 data_kaya = data_base %>% 
-  group_by(ISO,country,year,GDP_pc,pop) %>% 
+  group_by(ISO,country,year,GDP_pc,pop,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>% 
   summarise(CO2=sum(CO2,na.rm=TRUE)) %>%

### 2022-11-14 r-report/countries.Rmd
countries & kaya add

---
title: "countries & logical columns in adp region"
output: pdf_document
date: "2022-10-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='hide', message=FALSE, warning=FALSE)
knitr::opts_chunk$set(fig.height = 4, fig.width = 6)
options(knitr.kable.NA = '',knitr.table.format = "latex")
knitr::read_chunk('r-imports/init.R')
library(kableExtra)
```

```{r init-setup}
```

---
# ##################################################
# Run this when not knitting (and none of the above)
---

```{r, eval = FALSE}
source('r-imports/init.R')
```

---
# Any collab code below this line :)
# ##################################################
---

\footnotesize

```{r, results='asis'}
load("data-transf/data_base.RData")

data_base %>%
  filter(region_ar6_6 == "Asia and developing Pacific") %>%
  distinct(country,ISO,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>%
  kable("latex",booktabs = T, longtable = T)
```

### 2022-11-14 r-report/countries_deved.Rmd
countries fix

--- 2022-11-14 r-report/countries.Rmd
@@
 ---
-title: "countries & logical columns in adp region"
+title: "countries & logical columns: dev'ed countries"
 output: pdf_document
@@
 data_base %>%
-  filter(region_ar6_6 == "Asia and developing Pacific") %>%
+  filter(deved) %>%
   distinct(country,ISO,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>%

### 2022-11-14 r-prep/prep.Rmd
kaya

@@
 data_kaya = data_base %>% 
-  group_by(ISO,country,year,GDP_pc,pop,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>% 
+  group_by(across(-c(sector_title,subsector_title))) %>% 
   summarise(CO2=sum(CO2,na.rm=TRUE)) %>%

### 2022-11-14 r-report/countries_deving_woc.Rmd
deving countries

--- 2022-11-14 r-report/countries_deved.Rmd
@@
 ---
-title: "countries & logical columns: dev'ed countries"
+title: "countries & logical columns: dev'ing countries w/o China"
 output: pdf_document
@@
 data_base %>%
-  filter(deved) %>%
+  filter(deving_woc) %>%
   distinct(country,ISO,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>%

### 2022-11-16 r-plots/plot_facet_regions_sectors_emissions_abs.R
total anpassung

@@ -1,12 +1,12 @@
 PDATA$data_abs %>%
 #  filter(region==c(COUNTRY, "Developed","Developing")) %>% #line breaks
   ggplot( aes(x=year, y=GHG_s_r, color=region)) +
-  facet_grid(sector_title ~ region,scales="free_y") +
+  facet_wrap(sector_title ~ region,scales="free_y",nrow=length(unique(PDATA$data_abs$sector_title))) +
   geom_line() +
   scale_fill_brewer(palette = "Set2") +
   theme(legend.position="none")+
   ylab("Per Capita Emissions (tCO2eq)") +
   theme_ghg()+
   scale_fill_brewer(palette="Set2") +
-  theme(axis.title.x = element_blank()) +
+  theme(axis.title.x = element_blank(),axis.text.y=element_blank(),strip.text.x = element_text(size = 5)) +
   ggtitle("Total Emissions " %.% COUNTRY %.% " vs. Developed/Developing Countries by Sector, 1970-" %.% YEAR_U)

### 2022-11-16 r-analysis/data_per_capita_emissions.R
fix

@@ -33,4 +33,4 @@ data_regions <- data_countries %>%
 
 PDATA$country_and_regions <- data_regions %>% 
   rbind(data_first_country,data_us) %>%
-  filter(year <= {{YEAR}})
+  filter(between(year,{{YEAR_L}},{{YEAR_U}}))

### 2022-11-16 r-plots/plot_bar_per_capita_emissions.R

@@ -1,18 +1,18 @@
 #set levels
 
-plot_level<-PDATA$country_and_regions %>%
-  filter(year=={{YEAR}}) %>%
-  filter(region!={{COUNTRY}}) %>%
-  arrange(desc(GHG_pc)) %>%
-  pull(region)
-
-plot_level<-c(COUNTRY,plot_level)
+# plot_level<-PDATA$country_and_regions %>%
+#   filter(region!={{COUNTRY}}) %>%
+#   arrange(desc(GHG_pc)) %>%
+#   pull(region)
+# 
+# plot_level<-c(COUNTRY,plot_level)
 
 #plot
 
+# ,levels=plot_level
+
 PDATA$country_and_regions %>%
-  filter(year=={{YEAR}}) %>%
-  ggplot(., aes(y=GHG_pc,x=factor(region,levels=plot_level), fill=as.factor(region) )) +
+  ggplot(., aes(y=GHG_pc,x=factor(region), fill=as.factor(region) )) +
   geom_bar( stat = 'identity') +
   scale_fill_brewer(palette = "Set1") +
   theme(legend.position="none")+

### 2022-11-16 r-report/shiny/app_bar_per_capita_emissions.R

@@ -39,7 +39,8 @@ server = function(input, output) {
   
   .init = reactive({
     
-    YEAR = input$year
+    YEAR_L = input$year[1]
+    YEAR_U = input$year[2]
     COUNTRY = input$country
     
     source("r-analysis/data_per_capita_emissions.R", local = TRUE, print.eval = TRUE)
@@ -49,7 +50,8 @@ server = function(input, output) {
   
   output$plot1 = renderPlot({
     
-    YEAR = input$year
+    YEAR_L = input$year[1]
+    YEAR_U = input$year[2]
     COUNTRY = input$country
     .init()
     
@@ -60,7 +62,8 @@ server = function(input, output) {
   
   output$plot2 = renderPlot({
     
-    YEAR = input$year
+    YEAR_L = input$year[1]
+    YEAR_U = input$year[2]
     COUNTRY = input$country
     .init()
     

### 2022-11-16 r-analysis/data_sector_regions.R
absolute average

@@ -23,6 +23,17 @@ PDATA$data_abs = data_base %>%
   filter(between(year,{{YEAR_L}},{{YEAR_U}}))
 
 
+PDATA$data_absavg = data_base %>%
+  mutate(region = case_when(deving_woc ~ "Developing",country == {{COUNTRY}} ~ {{COUNTRY}},deved ~ "Developed")) %>%
+  filter(!is.na(region)) %>%
+  group_by(region,country,year,sector_title,pop) %>% # !!!! only include pop for na removal consistency
+  summarise(GHG_s=sum(GHG,na.rm=TRUE)) %>% # within country: sum
+  na.omit() %>%
+  group_by(region,year,sector_title) %>%
+  summarise(GHG_s_r_avg=mean(GHG_s,na.rm=TRUE)) %>% # across countries: weighted mean
+  filter(between(year,{{YEAR_L}},{{YEAR_U}}))
+
+
 PDATA$data_rel = data_base %>%
   mutate(region = case_when(deving_woc ~ "Developing",country == {{COUNTRY}} ~ {{COUNTRY}},deved ~ "Developed")) %>%
   filter(!is.na(region)) %>%

### 2022-11-16 r-plots/plot_facet_regions_sectors_emissions_abs.R

@@ -5,7 +5,7 @@ PDATA$data_abs %>%
   geom_line() +
   scale_fill_brewer(palette = "Set2") +
   theme(legend.position="none")+
-  ylab("Per Capita Emissions (tCO2eq)") +
+  ylab("Total Emissions (tCO2eq)") +
   theme_ghg()+
   scale_fill_brewer(palette="Set2") +
   theme(axis.title.x = element_blank(),axis.text.y=element_blank(),strip.text.x = element_text(size = 5)) +

### 2022-11-16 r-plots/plot_facet_regions_sectors_emissions_absavg.R

@@ -1,12 +1,12 @@
-PDATA$data_rel %>%
+PDATA$data_absavg %>%
 #  filter(region==c(COUNTRY, "Developed","Developing")) %>% #line breaks
-  ggplot( aes(x=year, y=GHG_s_r_perc, color=region)) +
+  ggplot( aes(x=year, y=GHG_s_r_avg, color=region)) +
   facet_grid(sector_title ~ region,scales="free_y") +
   geom_line() +
   scale_fill_brewer(palette = "Set2") +
   theme(legend.position="none")+
-  ylab("Relative Emissions %") +
+  ylab("Avg Total Emissions (tCO2eq)") +
   theme_ghg()+
   scale_fill_brewer(palette="Set2") +
   theme(axis.title.x = element_blank()) +
-  ggtitle("Relative Emissions " %.% COUNTRY %.% " vs. Developed/Developing Countries by Sector, 1970-" %.% YEAR_U)
+  ggtitle("Absolute Emissions " %.% COUNTRY %.% " vs. Avg'ed Developed/Developing Countries by Sector, 1970-" %.% YEAR_U)

### 2022-11-16 r-report/shiny/app_regions_sectors.R

@@ -26,7 +26,8 @@ ui = fluidPage(
 
     mainPanel(
          plotOutput("plot1"),
-         plotOutput("plot2"),
+         plotOutput("plot2_1"),
+         plotOutput("plot2_2"),
          plotOutput("plot3")
     )
   )
@@ -61,7 +62,7 @@ server = function(input, output) {
     
   })
   
-  output$plot2 = renderPlot({
+  output$plot2_1 = renderPlot({
     
     YEAR_L = input$year[1]
     YEAR_U = input$year[2]
@@ -69,6 +70,18 @@ server = function(input, output) {
     .init()
     
     source("r-plots/plot_facet_regions_sectors_emissions_abs.R", local = TRUE, print.eval = TRUE)
+    
+  })
+  
+  
+  output$plot2_2 = renderPlot({
+    
+    YEAR_L = input$year[1]
+    YEAR_U = input$year[2]
+    COUNTRY = input$country
+    .init()
+    
+    source("r-plots/plot_facet_regions_sectors_emissions_absavg.R", local = TRUE, print.eval = TRUE)
     
   })
   

### 2022-11-16 r-prep/prep.Rmd
per GDP emissions

@@
   left_join(data_lulucf,by=c("ISO","year")) %>%
-  mutate(GHG_pc = GHG/pop) %>%
-  mutate(GDP_pc = gdp_ppp/pop) %>%
+  mutate(
+    GHG_pc = GHG/pop,
+    GHG_pg = GHG/gdp_ppp,
+    GDP_pc = gdp_ppp/pop
+  ) %>%
   filter(year <= 2019) %>% 
@@
 
+data_kaya$value[0]<-NA
+
+data_kaya%<>%
+  na.omit()
+
 save(data_kaya,file="data-transf/data_kaya.RData")

### 2022-11-16 r-analysis/data_sector_regions.R

@@ -12,6 +12,17 @@ PDATA$data = data_base %>%
   filter(between(year,{{YEAR_L}},{{YEAR_U}}))
 
 
+PDATA$data_gdp = data_base %>%
+  mutate(region = case_when(deving_woc ~ "Developing",country == {{COUNTRY}} ~ {{COUNTRY}},deved ~ "Developed")) %>%
+  filter(!is.na(region)) %>%
+  group_by(region,country,year,sector_title,gdp_ppp,pop) %>% #!!!! only include pop for na removal consistency; check for gdp na removal effect!
+  summarise(GHG_pg_s=sum(GHG_pg,na.rm=TRUE)) %>% # within country: sum
+  na.omit() %>%
+  group_by(region,year,sector_title) %>%
+  summarise(GHG_pg_s_r=weighted.mean(GHG_pg_s,gdp_ppp,na.rm=TRUE)) %>% # across countries: weighted mean
+  filter(between(year,{{YEAR_L}},{{YEAR_U}}))
+
+
 PDATA$data_abs = data_base %>%
   mutate(region = case_when(deving_woc ~ "Developing",country == {{COUNTRY}} ~ {{COUNTRY}},deved ~ "Developed")) %>%
   filter(!is.na(region)) %>%

### 2022-11-16 r-plots/plot_facet_regions_sectors_emissions_gdp.R

@@ -1,0 +1,13 @@
+PDATA$data_gdp %>%
+#  filter(region==c(COUNTRY, "Developed","Developing")) %>% #line breaks
+  ggplot( aes(x=year, y=GHG_pg_s_r, color=region)) +
+  facet_grid(sector_title ~ region,scales="free_y") +
+  geom_line() +
+  scale_fill_brewer(palette = "Set2") +
+  theme(legend.position="none")+
+  ylab("Per GDP Emissions (tCO2eq)") +
+  theme_ghg()+
+  scale_fill_brewer(palette="Set2") +
+  theme(axis.title.x = element_blank()) +
+  ggtitle("Per GDP Emissions " %.% COUNTRY %.% " vs. Developed/Developing Countries by Sector, 1970-" %.% YEAR_U)
+

### 2022-11-16 r-report/shiny/app_regions_sectors.R

@@ -25,7 +25,8 @@ ui = fluidPage(
     ),
 
     mainPanel(
-         plotOutput("plot1"),
+         plotOutput("plot1_1"),
+         plotOutput("plot1_2"),
          plotOutput("plot2_1"),
          plotOutput("plot2_2"),
          plotOutput("plot3")
@@ -51,7 +52,7 @@ server = function(input, output) {
   })
   
   
-  output$plot1 = renderPlot({
+  output$plot1_1 = renderPlot({
     
     YEAR_L = input$year[1]
     YEAR_U = input$year[2]
@@ -59,6 +60,18 @@ server = function(input, output) {
     .init()
     
     source("r-plots/plot_facet_regions_sectors_emissions.R", local = TRUE, print.eval = TRUE)
+    
+  })
+  
+  
+  output$plot1_2 = renderPlot({
+    
+    YEAR_L = input$year[1]
+    YEAR_U = input$year[2]
+    COUNTRY = input$country
+    .init()
+    
+    source("r-plots/plot_facet_regions_sectors_emissions_gdp.R", local = TRUE, print.eval = TRUE)
     
   })
   

### 2022-11-21 r-prep/prep.Rmd
Integrated new energy data for deving countries

@@
 ```{r}
-load("data-raw/data_iea.RData")
+
+#load("data-raw/data_iea.RData") Thanks to Will we got better Data now. 
+#load better energy data 
+data_energy<-read_excel("data-raw/data_energy_co2_countries.xlsx",sheet = "data")
+# filter for ISO, Year and Energy
+data_energy%<>%
+  select(ISO,year,energy)
 
 data_kaya = data_base %>% 
-  group_by(across(-c(sector_title,subsector_title))) %>% 
-  summarise(CO2=sum(CO2,na.rm=TRUE)) %>%
-  left_join(data_iea,by=c("ISO","year")) %>%
+  group_by(across(-c(sector_title,subsector_title,N2O, CH4,GHG,co2_lulucf,gdp_ppp, Fgas,GHG_pc,GHG_pg,CO2))) %>% 
+  na.omit() %>% 
+  summarise(CO2=sum(CO2,na.rm=T))%>%
+  left_join(data_energy,by=c("ISO","year")) %>%
   mutate(energy_intensity = energy/GDP_pc) %>%
@@
   pivot_longer(c(CO2,pop,GDP_pc,energy_intensity,carbon_intensity),names_to = "var",values_to = "value")
-
-data_kaya$value[0]<-NA
-
-data_kaya%<>%
-  na.omit()
 

### 2022-11-21 r-analysis/data_kaya_analysis.R

@@ -1,9 +1,9 @@
 load("data-transf/data_kaya.RData")
 
 #normalize to 1 in 2000
-data_kaya_tests<-data_kaya %>%
+data_kaya<-data_kaya %>%
   group_by(country,var) %>% 
-  summarise(value=value/first(value))
+  mutate(value=value/first(value))
 
 data_kaya_countries <- data_kaya %>%
   select(c(year,energy,var,value,country)) 

### 2022-11-21 r-analysis/data_sectors_bycountry.R
stacked charts

@@ -1,0 +1,31 @@
+load("data-transf/data_base.RData")
+
+
+PDATA$data_abs = data_base %>%
+  filter(country == {{COUNTRY}}) %>%
+  rename(GAS := {{GAS}}) %>%
+  group_by(year,sector_title) %>%
+  summarise(GAS_s=sum(GAS,na.rm=TRUE)) %>%
+  na.omit() %>%
+  filter(between(year,{{YEAR_L}},{{YEAR_U}}))
+
+
+
+PDATA$data_rel = PDATA$data_abs %>%
+  group_by(year) %>%
+  mutate(GAS_s_perc=GAS_s/sum(GAS_s,na.rm=TRUE))
+
+
+
+# 
+# PDATA$data_rel = data_base %>%
+#   mutate(region = case_when(deving_woc ~ "Developing",country == {{COUNTRY}} ~ {{COUNTRY}},deved ~ "Developed")) %>%
+#   filter(!is.na(region)) %>%
+#   group_by(region,country,year,sector_title,pop) %>% # !!!! only include pop for na removal consistency
+#   summarise(GHG_s=sum(GHG,na.rm=TRUE)) %>% # within country: sum
+#   na.omit() %>%
+#   group_by(region,year,sector_title) %>%
+#   summarise(GHG_s_r=sum(GHG_s,na.rm=TRUE)) %>% #across countries: weighted mean
+#   group_by(region,year) %>%
+#   mutate(GHG_s_r_perc=GHG_s_r/sum(GHG_s_r,na.rm=TRUE)) %>% # 
+#   filter(between(year,{{YEAR_L}},{{YEAR_U}}))

### 2022-11-21 r-analysis/meta.R

@@ -3,3 +3,17 @@ load("data-transf/data_base.RData")
 meta_countries = data_base %>% distinct(country,ISO)
 meta_country_list_iso = meta_countries %$% setNames(ISO,country)
 meta_country_list = meta_countries %$% setNames(country,country)
+
+meta_gas_list = data_base %>%
+  select(where(is_numeric)) %>%
+  select(matches("^[A-Z]",ignore.case=F)) %>%
+  select(-GDP_pc) %>%
+  select(-contains("_")) %>%
+  names() %>% setNames(.,.)
+
+meta_gas_transf_list = data_base %>%
+  select(where(is_numeric)) %>%
+  select(matches("^[A-Z]",ignore.case=F)) %>%
+  select(-GDP_pc) %>%
+  select(contains("_")) %>%
+  names() %>% setNames(.,.)

### 2022-11-21 r-imports/init.R

@@ -81,3 +81,4 @@ COUNTRY = "China"
 YEAR = 2019
 YEAR_L = 1970
 YEAR_U = 2019
+GAS = "GHG"

### 2022-11-21 r-plots/plot_sectors_bycountry_stacked_rel.R

@@ -1,0 +1,9 @@
+PDATA$data_rel %>% 
+  ggplot(aes(x=year,y=GAS_s_perc,fill=sector_title)) +
+  geom_area(color="#636363") +
+  theme_bw() +
+  scale_fill_brewer(palette="Set2") +
+  ylab(GAS %.% " Emissions (MtCO2eq)") +
+  theme_ghg()+
+  theme(axis.title.x=element_blank()) +
+  ggtitle("Total Emissions, " %.% COUNTRY %.% ", by Sector, " %.% YEAR_L %.% "-" %.% YEAR_U)

### 2022-11-21 r-plots/plot_kaya_country_vs.developed-vs_developing.R
Kaya Plot levels

@@ -1,6 +1,15 @@
+
+#set levels
+
+
+PDATA$plot_level_kay<-c(COUNTRY,"Developed Countries","Developing Countries")
+
+
+
 #plot
 
-PDATA$kaya_regions %>% 
+PDATA$kaya_regions %>%
+  mutate(region = fct_relevel(region,PDATA$plot_level_kay)) %>% 
   ggplot(.,aes(x=year,y=value,color=var)) +
   geom_line(size=1) +
   geom_hline(aes(yintercept=1)) +

### 2022-11-22 r-prep/prep.Rmd
Plotting and export

@@
 ```{r}
+load("data-raw/data_cumulative_co2.RData")
 
+# need to add filling values when joining
+dev_status=data_base %>% 
+    select(ISO, country, region_ar6_dev, year)
+
+data_hist_co2=data_cumulative_co2 %>% 
+  left_join(dev_status, by= c("ISO","year","country")) %>% 
+  filter(year <= 2019) %>% 
+    mutate(
+      EU = country %in% eurostat::eu_countries[2]$name,
+      woc = country != "China",
+      deving_woc = woc & region_ar6_dev == "developing",
+      deved = region_ar6_dev == "developed",
+      adp_region_woc = woc & region_ar6_6 == "Asia and developing Pacific",
+      adp_region_deving_woc = adp_region_woc & deving_woc
+    ) %>% 
+  select(-woc)
+
+save(data_hist_co2,file="data-transf/data_hist_co2.RData")
 ```

### 2022-11-22 r-analysis/data_kaya_analysis.R

@@ -2,6 +2,7 @@ load("data-transf/data_kaya.RData")
 
 #normalize to 1 in 2000
 data_kaya<-data_kaya %>%
+  filter(year>=2000) %>% 
   group_by(country,var) %>% 
   mutate(value=value/first(value))
 
@@ -41,4 +42,24 @@ kaya_regions <- data_kaya_first_country %>%
 
 #make data available to shiny
 PDATA$kaya_regions <-kaya_regions
+
+#### intermediate plot for presentation
+data_kaya %>% 
+  filter(country %in% c("China")) %>%
+  ggplot(.,aes(x=year,y=value,color=var)) +
+  geom_line(size=1.5) +
+  geom_hline(aes(yintercept=1)) +
+  theme_bw() +
+  scale_color_brewer(palette="Set2",labels=c("Carbon intensity (CO2/energy)",
+                                             "Carbon emissions",
+                                             "Energy intensity (energy/GDP)",
+                                             "GDP per capita (GDP/pop)",
+                                             "Population"),
+                     guide = guide_legend(reverse = TRUE)) +
+  theme(legend.title=element_blank(),
+        axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        text = element_text(size = 25))+
+  guides(fill=guide_legend(title="Country/Region"))+
+  ggtitle("China's Kaya Identity from 2000-2019")
 

### 2022-11-22 r-analysis/data_sector_regions.R

@@ -78,3 +78,4 @@ PDATA$data_rel = data_base %>%
   group_by(region,year) %>%
   mutate(GHG_s_r_perc=GHG_s_r/sum(GHG_s_r,na.rm=TRUE)) %>% # 
   filter(between(year,{{YEAR_L}},{{YEAR_U}}))
+

### 2022-11-22 r-analysis/data_single_polluters.R

@@ -28,8 +28,13 @@ PDATA$data_rel = data_base %>%
   mutate(GAS_s_perc=100*GAS_s/sum(GAS_s,na.rm=TRUE))
 
 
+#find out since when china is the single biggest polluter over all GHGs
 
+wide_df<-PDATA$data_rel %>% 
+  select(year,region,GAS_s_perc) %>% 
+  pivot_wider(names_from = region, values_from = GAS_s_perc)
 
+wide_df$year[wide_df$China>wide_df$`United States`]
 
 # 
 # PDATA$data_rel = data_base %>%

### 2022-11-22 r-plots/plot_facet_regions_sectors_emissions_absavg_pc.R

@@ -8,5 +8,7 @@ PDATA$data_absavg_pg %>%
   ylab("Avg Total Emissions (tCO2eq)") +
   theme_ghg()+
   scale_fill_brewer(palette="Set2") +
-  theme(axis.title.x = element_blank()) +
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5)) +
+  guides(color=guide_legend(title="Country/Category"))+
   ggtitle("Absolute Emissions " %.% COUNTRY %.% " vs. pc-Avg'ed Developed/Developing Countries by Sector, 1970-" %.% YEAR_U)

### 2022-11-22 r-plots/plot_sectors_bycountry_stacked_abs.R

@@ -5,5 +5,7 @@ PDATA$data_abs %>%
   scale_fill_brewer(palette="Set2") +
   ylab(GAS %.% " Emissions (MtCO2eq)") +
   theme_ghg()+
-  theme(axis.title.x=element_blank()) +
+  theme(axis.title.x=element_blank(),
+        text = element_text(size = 25)) +
+  guides(fill=guide_legend(title="Sectors"))+
   ggtitle("Total Emissions, " %.% COUNTRY %.% ", by Sector, " %.% YEAR_L %.% "-" %.% YEAR_U)

### 2022-11-22 r-plots/plot_single_polluters_stacked_rel.R

@@ -5,5 +5,8 @@ PDATA$data_rel %>%
   scale_fill_brewer(palette="Set2") +
   ylab(GAS %.% " Emissions, %") +
   theme_ghg()+
-  theme(axis.title.x=element_blank()) +
-  ggtitle("Relative Emissions, " %.% COUNTRY %.% " vs. Dev'ed/Dev'ing Countries by Sector, " %.% YEAR_L %.% "-" %.% YEAR_U)
+  theme(axis.title.x=element_blank(),
+        text = element_text(size = 20)) +
+  geom_vline(xintercept=2004, linetype="dashed", color = "red")+
+  guides(fill=guide_legend(title="Country/Region"))+
+  ggtitle("Relative Emissions of the Top- 5 Polluters " %.% YEAR_L %.% "-" %.% YEAR_U)

### 2022-11-22 r-prep/prep.Rmd
Created Cumulative CO Emissions data

--- 2022-11-21 r-prep/prep.Rmd
@@
 ```{r}
+load("data-raw/data_cumulative_co2.RData")
 
+# need to add filling values when joining
+dev_status=data_base %>% 
+    group_by(country, year,region_ar6_dev) %>% 
+    summarise()
+
+data_hist_co2=data_cumulative_co2 %>% 
+  left_join(dev_status, by= c("country","year")) %>% 
+  filter(year <= 2019) %>% 
+    mutate(
+      EU = country %in% eurostat::eu_countries[2]$name,
+      woc = country != "China",
+      deving_woc = woc & region_ar6_dev == "developing",
+      deved = region_ar6_dev == "developed",
+      adp_region_woc = woc & region_ar6_6 == "Asia and developing Pacific",
+      adp_region_deving_woc = adp_region_woc & deving_woc
+    ) %>% 
+  select(-woc)
+
+save(data_hist_co2,file="data-transf/data_hist_co2.RData")
 ```

### 2022-11-22 r-analysis/data_cumulative_co2.R
Cumulative meissions plots

@@ -1,0 +1,47 @@
+load("data-transf/data_hist_co2.RData")
+
+
+#Hard setting yearL
+YEAR_L<-1950
+
+data_cum_co2 = data_hist_co2 %>%
+  select(ISO, country, EU,  year, CO2_FFI) %>% 
+  mutate(region = case_when(country == {{COUNTRY}} ~ {{COUNTRY}},
+                            EU ~ "EU-28",
+                            ISO %in% c("USA","CHN","IND","RUS") ~ country,
+                            TRUE ~ "Other")) %>% 
+  mutate(CO2_FFI=replace_na(CO2_FFI, 0)) %>% 
+  group_by(region,year) %>% 
+  summarise(CO2=sum(CO2_FFI)) %>%
+  mutate(cum_CO2=cumsum(CO2)) %>%
+  filter(between(year,{{YEAR_L}},{{YEAR_U}})) %>% 
+  group_by(year) %>%
+  mutate(cum_CO2_perc=100*round(cum_CO2/sum(cum_CO2,na.rm=TRUE),4))
+
+
+# testing plots 
+
+data_cum_co2 %>% 
+  ggplot(aes(x=year,y=cum_CO2,color=region)) +
+  geom_line(size=1)  +
+  theme_bw() +
+  scale_fill_brewer(palette="Set2") +
+  ylab("Cumulative CO2 Emissions (MtCO2eq)") +
+  theme_ghg()+
+  theme(axis.title.x=element_blank(),
+        text = element_text(size = 20)) +
+  guides(color=guide_legend(title="Country"))+
+  ggtitle("Cummulative Co2 " %.% COUNTRY %.% " vs. Top Emitters, " %.% YEAR_L %.% "-" %.% YEAR_U)
+
+
+data_cum_co2 %>% 
+  ggplot(aes(x=year,y=cum_CO2_perc,fill=region)) +
+  geom_area(color="#636363") +
+  theme_bw() +
+  scale_fill_brewer(palette="Set2") +
+  ylab("Cumulative CO2 Emissions, %") +
+  theme_ghg()+
+  theme(axis.title.x=element_blank(),
+        text = element_text(size = 15)) +
+  guides(fill=guide_legend(title="Country/Region"))+
+  ggtitle("Relative Cumulative Emissions of the Top- 5 Polluters " %.% YEAR_L %.% "-" %.% YEAR_U)

### 2022-12-05 r-prep/prep.Rmd
In cluded Consumption data and Income levels

@@
 
+# load Consumption emissions
+data_consumption = read_excel("data-raw/National_Fossil_Carbon_Emissions_2022v1.0.xlsx",range =  "Consumption Emissions!A9:IB41")
+data_consumption%<>%
+  pivot_longer(2:236,names_to = "country", values_to = "con_co2") %>% 
+  mutate(year= Year) %>% 
+  select(-Year)
+# worldbank income data for classification
+
+data_income_wb<-read_excel("data-raw/data_wb.xlsx",range =  "Data!A4:BN270")
+data_income_wb%<>%
+  select(-c("Indicator Name","Indicator Code")) %>% 
+  pivot_longer(3:64,names_to = "year", values_to = "gni_per_capita") %>% 
+  mutate(dev_status_income = case_when(
+        gni_per_capita >=1035 ~ "Lower-middle income",
+        gni_per_capita >=4046 ~ "Upper-middle income",
+        gni_per_capita >=12535 ~ "High income",
+        gni_per_capita= NA ~ "",
+        TRUE ~ "Low income"
+  )) %>% 
+  rename(country="Country Name", ISO = "Country Code") %>% 
+  mutate(year=as.numeric(year)) %>% 
+  select(-country)
+
 load("data-raw/data_wdi.RData") 
@@
   left_join(data_wdi,by=c("ISO","year")) %>%
+  left_join(data_consumption,by=c("country","year")) %>%
+  left_join(data_income_wb,by=c("ISO","year")) %>%
   left_join(data_lulucf,by=c("ISO","year")) %>%
@@
 
-```{r}
+```{r- loading and prepping Kaya Data}
 
@@
 
-```{r}
+```{r -  Data Cumulative CO2}
 load("data-raw/data_cumulative_co2.RData")
@@
 ```
+
+```{r - loading and prepping}
+
+# need to add filling values when joining
+dev_status=data_base %>% 
+    group_by(country, year,region_ar6_dev) %>% 
+    summarise()
+
+data_hist_co2=data_cumulative_co2 %>% 
+  left_join(dev_status, by= c("country","year")) %>% 
+  filter(year <= 2019) %>% 
+    mutate(
+      EU = country %in% eurostat::eu_countries[2]$name,
+      woc = country != "China",
+      deving_woc = woc & region_ar6_dev == "developing",
+      deved = region_ar6_dev == "developed",
+      adp_region_woc = woc & region_ar6_6 == "Asia and developing Pacific",
+      adp_region_deving_woc = adp_region_woc & deving_woc
+    ) %>% 
+  select(-woc)
+
+save(data_hist_co2,file="data-transf/data_hist_co2.RData")
+```

### 2022-12-08 r-prep/prep.Rmd
Graphics for report and first resposibility consideration

--- 2022-11-22 r-prep/prep.Rmd
@@
 
+# load Consumption emissions
+data_consumption = read_excel("data-raw/National_Fossil_Carbon_Emissions_2022v1.0.xlsx",range =  "Consumption Emissions!A9:IB41")
+data_consumption%<>%
+  pivot_longer(2:236,names_to = "country", values_to = "con_co2") %>% 
+  mutate(year= Year) %>% 
+  select(-Year)
+# worldbank income data for classification
+
+data_income_wb<-read_excel("data-raw/data_wb.xlsx",range =  "Data!A4:BN270")
+data_income_wb%<>%
+  select(-c("Indicator Name","Indicator Code")) %>% 
+  pivot_longer(3:64,names_to = "year", values_to = "gni_per_capita") %>% 
+  mutate(dev_status_income = case_when(
+        between(gni_per_capita,0, 1025) ~ "Low income",
+        between(gni_per_capita,1026, 3095) ~"Lower-middle income",
+        between(gni_per_capita,3996, 12375) ~ "Upper-middle income",
+        gni_per_capita > 12375  ~ "High income",
+        gni_per_capita == NA ~ ""  )) %>% 
+  rename(country="Country Name", ISO = "Country Code") %>% 
+  mutate(year=as.numeric(year)) %>% 
+  select(-country) %>% 
+  filter(year==2019) %>% 
+  select(-year)
+
 load("data-raw/data_wdi.RData") 
@@
   left_join(data_wdi,by=c("ISO","year")) %>%
+  left_join(data_consumption,by=c("country","year")) %>%
+  left_join(data_income_wb,by=c("ISO")) %>%
   left_join(data_lulucf,by=c("ISO","year")) %>%
@@
 
-```{r}
+```{r loading and prepping Kaya Data}
 
@@
   group_by(across(-c(sector_title,subsector_title,N2O, CH4,GHG,co2_lulucf,gdp_ppp, Fgas,GHG_pc,GHG_pg,CO2))) %>% 
+  summarise(CO2=sum(CO2,na.rm=T))%>%
   na.omit() %>% 
@@
   left_join(data_energy,by=c("ISO","year")) %>% 
-  mutate(energy_intensity = energy/GDP_pc) %>%
-  mutate(carbon_intensity = CO2/energy) %>%
-  na.omit() %>% 
-  pivot_longer(c(CO2,pop,GDP_pc,energy_intensity,carbon_intensity),names_to = "var",values_to = "value")
+  mutate(dev_status_reg = case_when(deved ~ "developed",
+                                    TRUE ~ "developing"))
 

### 2022-12-08 r-analysis/data_kaya_analysis.R

@@ -1,65 +1,115 @@
 load("data-transf/data_kaya.RData")
 
-#normalize to 1 in 2000
-data_kaya<-data_kaya %>%
+
+
+#for regions ar6 
+data_kaya_regions<-data_kaya%>%
+mutate(dev_status_reg = case_when(country=={{COUNTRY}} ~ as.character({{COUNTRY}}),
+       country!={{COUNTRY}} ~ dev_status_reg)) %>% 
+group_by(dev_status_reg, year) %>% 
+  na.omit() %>% 
+  summarise(CO2 = sum(CO2),
+            energy = sum(energy),
+            GDP = sum(GDP_pc*pop),
+            pop = sum(pop),
+            GDP_pc = GDP/pop) %>% 
+  mutate(energy_intensity = energy/GDP_pc) %>%
+  mutate(carbon_intensity = CO2/energy) %>%
+  na.omit() %>% 
+  pivot_longer(c(CO2,pop,GDP_pc,energy_intensity,carbon_intensity),names_to = "var",values_to = "value") %>% 
   filter(year>=2000) %>% 
-  group_by(country,var) %>% 
+  group_by(dev_status_reg,var) %>% 
   mutate(value=value/first(value))
 
-#get country level data 
-data_kaya_countries <- data_kaya %>%
-  select(c(year,energy,var,value,country)) 
-
-#get specific data for country of choice/ China
-data_kaya_first_country<-data_kaya %>%
-  select(c(year,energy,var,value,country)) %>% 
-  filter(country=={{COUNTRY}}) %>%
-  rename(region = country)
-
-#filter for developed country Data
-data_kaya_deved<-data_kaya %>%
-  filter(deved) %>%
-  group_by(year,energy,var,value,country) %>% 
-  rename(region = country) %>% 
-  mutate(region = "Developed Countries")
-
-#filter for developing country Data
-data_kaya_deving<-data_kaya %>%
-  filter(deving_woc) %>%
-  select(c(year,energy,var,value,country)) %>% 
-  rename(region = country) %>% 
-  mutate(region = "Developing Countries")
-
-#to show China's development in releation to developing or developed nations
+# for income class
+data_kaya_incomelevels<-data_kaya%<>%
+  mutate(dev_status_income = case_when(country=={{COUNTRY}} ~ as.character({{COUNTRY}}),
+                                    country!={{COUNTRY}} ~ dev_status_income)) %>% 
[…]

### 2022-12-08 r-analysis/data_sectror_incomelevel_yemissions.R

@@ -1,0 +1,66 @@
+load("data-transf/data_base.RData")
+
+
+PDATA$data_inc_rel = data_base %>%
+  mutate(dev_status_income = case_when(country=={{COUNTRY}} ~ as.character({{COUNTRY}}),
+                                       country!={{COUNTRY}} ~ dev_status_income)) %>% 
+  filter(!is.na(dev_status_income)) %>%
+  rename(GAS := {{GAS}}) %>%
+  na.omit() %>% # !!
+  filter(year == {{YEAR}}) %>%
+  group_by(dev_status_income,sector_title) %>%
+  summarise(GAS_s=sum(GAS,na.rm=TRUE)) %>%
+  group_by(dev_status_income) %>%
+  mutate(GAS_s_perc=100*GAS_s/sum(GAS_s,na.rm=TRUE))
+
+
+PDATA$data_inc_rel_pc = data_base %>%
+  mutate(dev_status_income = case_when(country=={{COUNTRY}} ~ as.character({{COUNTRY}}),
+                                       country!={{COUNTRY}} ~ dev_status_income)) %>% 
+  filter(!is.na(dev_status_income)) %>%
+  rename(GAS := {{GAS}}) %>%
+  na.omit() %>% # !!
+  filter(year == {{YEAR}}) %>%
+  group_by(dev_status_income,sector_title) %>%
+  summarise(GAS_s=weighted.mean(GAS,pop,na.rm=TRUE)) %>%
+  group_by(dev_status_income) %>%
+  mutate(GAS_s_perc=100*GAS_s/sum(GAS_s,na.rm=TRUE))
+
+
+PDATA$data_inc_rel_pg = data_base %>%
+  mutate(dev_status_income = case_when(country=={{COUNTRY}} ~ as.character({{COUNTRY}}),
+                                       country!={{COUNTRY}} ~ dev_status_income)) %>% 
+  filter(!is.na(dev_status_income)) %>%
+  rename(GAS := {{GAS}}) %>%
+  na.omit() %>% # !!
+  filter(year == {{YEAR}}) %>%
+  group_by(dev_status_income,sector_title) %>%
+  summarise(GAS_s=weighted.mean(GAS,gdp_ppp,na.rm=TRUE)) %>%
+  group_by(dev_status_income) %>%
[…]

### 2022-12-08 r-plots/plot_facet_incomelevels_sectors_emissions.R

@@ -1,0 +1,15 @@
+PDATA$data_inc %>%
+#  filter(region==c(COUNTRY, "Developed","Developing")) %>% #line breaks
+  ggplot( aes(x=year, y=GHG_pc_s_r, color=dev_status_income)) +
+  facet_grid(sector_title ~ dev_status_income,scales="free_y") +
+  geom_line(show.legend = FALSE) +
+  scale_fill_brewer(palette = "Set2") +
+  theme(legend.position="none")+
+  ylab("Per Capita Emissions (tCO2eq)") +
+  theme_ghg()+
+  theme(axis.title.x = element_blank(),
+        text = element_text(size = 14),
+        axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5)) +
+  guides(colour =guide_legend("Income Level /" %.% COUNTRY%.% " " ))+
+  ggtitle("Per Capita Emissions " %.% COUNTRY %.% " vs. Income Levels by Sector, 1970-" %.% YEAR_U)
+

### 2022-12-08 r-plots/plot_facet_incomelevels_sectors_emissions_abs.R

@@ -1,0 +1,13 @@
+PDATA$data_inc_abs %>%
+#  filter(region==c(COUNTRY, "Developed","Developing")) %>% #line breaks
+  ggplot( aes(x=year, y=GHG_s_r, color=dev_status_income)) +
+  facet_wrap(sector_title ~ dev_status_income,scales="free_y",nrow=length(unique(PDATA$data_abs$sector_title))) +
+  geom_line() +
+  scale_fill_brewer(palette = "Set2") +
+  theme(legend.position="none")+
+  ylab("Total Emissions (tCO2eq)") +
+  theme_ghg()+
+  guides(colour =guide_legend("Income Level /" %.% COUNTRY%.% " " ))+
+  
+  theme(axis.title.x = element_blank(),strip.text.x = element_text(size = 5)) +
+  ggtitle("Total Emissions " %.% COUNTRY %.% " vs. Income Levels by Sector, 1970-" %.% YEAR_U)

### 2022-12-08 r-plots/plot_facet_regions_sectors_yemission_stacked_rel.R

@@ -8,4 +8,6 @@ PDATA$data_rel %>%
   theme_ghg()+
   #scale_fill_brewer(palette="Set2") +
   theme(axis.title.x = element_blank()) +
+  geom_text(aes(label = round(GAS_s_perc)), position = position_stack(vjust = 0.5), size = 3) +
+  guides(fill =guide_legend("Sector"))+
   ggtitle("Relative Emissions " %.% COUNTRY %.% " vs. Developed/Developing Countries, by Sector, " %.% YEAR)

### 2022-12-08 r-plots/plot_kaya_incomelevels.R

@@ -1,0 +1,26 @@
+
+#set levels
+
+
+PDATA$plot_level_kay<-c(COUNTRY,"Low income","Lower middle-income","Upper middle-income","High income")
+
+
+
+#plot
+
+PDATA$kaya_incomelevels %>%
+  mutate(region = fct_relevel(dev_status_income,PDATA$plot_level_kay)) %>% 
+  ggplot(.,aes(x=year,y=value,color=var)) +
+  geom_line(size=1) +
+  geom_hline(aes(yintercept=1)) +
+  facet_wrap(.~region) +
+  theme_bw() +
+  scale_y_log10()+
+  scale_color_brewer(palette="Set2",labels=c("Carbon intensity (CO2/energy)",
+                                             "Carbon emissions",
+                                             "Energy intensity (energy/GDP)",
+                                             "GDP per capita (GDP/pop)",
+                                             "Population"),
+                     guide = guide_legend(reverse = TRUE)) +
+  theme(legend.title=element_blank(),
+        axis.title.x = element_blank())

### 2022-12-12 r-analysis/data_cumulative_mergeforecast.R
cumulative app

@@ -2,7 +2,7 @@ load("data-transf/data_cghg_1750_2019.RData")
 data = data_cghg_1750_2019
 
 load("data-transf/forecast_GHG_2040.RData")
-fdata_2040 = forecast %>%
+fdata_2040_ghg = forecast %>%
   mutate(country = ifelse(country == "EU","EU-27",country)) %>%
   filter(year > 2019) %>%
   group_by(country,year) %>%
@@ -10,14 +10,38 @@ fdata_2040 = forecast %>%
   rename(GHG = GAS_ss) %>%
   mutate(cum_ghg = NA)
 
+load("data-transf/forecast_CO2_2040.RData")
+fdata_2040_co2 = forecast %>%
+  mutate(country = ifelse(country == "EU","EU-27",country)) %>%
+  filter(year > 2019) %>%
+  group_by(country,year) %>%
+  summarise(GAS_ss = sum(GAS_s)) %>%
+  rename(co2 = GAS_ss) %>%
+  mutate(cum_co2 = NA)
+
+fdata_2040 = fdata_2040_ghg %>%
+  left_join(fdata_2040_co2)
+
 load("data-transf/forecast_GHG_2030.RData")
-fdata_2030 = forecast %>%
+fdata_2030_ghg = forecast %>%
   mutate(country = ifelse(country == "EU","EU-27",country)) %>%
   filter(year > 2019) %>%
   group_by(country,year) %>%
   summarise(GAS_ss = sum(GAS_s)) %>%
   rename(GHG = GAS_ss) %>%
   mutate(cum_ghg = NA)
+
+load("data-transf/forecast_CO2_2030.RData")
+fdata_2030_co2 = forecast %>%
+  mutate(country = ifelse(country == "EU","EU-27",country)) %>%
+  filter(year > 2019) %>%
+  group_by(country,year) %>%
+  summarise(GAS_ss = sum(GAS_s)) %>%
+  rename(co2 = GAS_ss) %>%
+  mutate(cum_co2 = NA)
+
+fdata_2030 = fdata_2030_ghg %>%
+  left_join(fdata_2030_co2)
 
 data_2040 = data %>% rbind(fdata_2040) %>%
   arrange(year) %>% 
@@ -25,7 +49,6 @@ data_2040 = data %>% rbind(fdata_2040) %>%
   mutate(cum_ghg = cumsum(coalesce(GHG, 0)) + GHG*0)
 
[…]

### 2022-12-12 r-plots/plot_cumulative_china_2030.R

@@ -1,0 +1,10 @@
+OUT = PDATA$data_cumulative_2030 %>%
+  ggplot( aes(x=year, y=cumulative, color=country)) +
+  geom_line() +
+  scale_fill_brewer(palette = "Set2") +
+  theme(legend.position="none")+
+  ylab("Cumulative Emissions (tCO2eq)") +
+  theme_ghg()+
+  scale_fill_brewer(palette="Set2") +
+  theme(axis.title.x = element_blank()) +
+  ggtitle("Cumulative "%.% GAS %.%" Emissions, Main Scenario, China vs. EU vs. US, "%.% YEAR_L %.%"-" %.% YEAR_U)

### 2022-12-12 r-plots/plot_cumulative_china_2040.R

@@ -1,0 +1,10 @@
+OUT = PDATA$data_cumulative_2040 %>%
+  ggplot( aes(x=year, y=cumulative, color=country)) +
+  geom_line() +
+  scale_fill_brewer(palette = "Set2") +
+  theme(legend.position="none")+
+  ylab("Cumulative Emissions (tCO2eq)") +
+  theme_ghg()+
+  scale_fill_brewer(palette="Set2") +
+  theme(axis.title.x = element_blank()) +
+  ggtitle("Cumulative "%.% GAS %.%" Emissions, Realistic Scenario, China vs. EU vs. US, "%.% YEAR_L %.%"-" %.% YEAR_U)

### 2022-12-12 r-report/shiny/app_cumulative_china.R

@@ -1,0 +1,82 @@
+setwd("../../")
+
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
+p_load(shiny)
+
+
+ui = fluidPage(
+  
+  titlePanel("Cumulative Emissions China vs. EU vs. US, with Forecast Data"),
+
+  sidebarLayout(
+      sidebarPanel(
+          sliderInput("year",
+                      "Years:",
+                      min = 1750,
+                      max = 2080,
+                      value = c(1900,2060),
+                      sep = ""),
+          selectInput("gas",
+                      "Gas:",
+                      meta_gas_list,
+                      selected = "GHG"),
+    ),
+
+    mainPanel(
+         plotlyOutput("plot1"),
+         plotlyOutput("plot2")
+    )
+  )
+)
+
+
+server = function(input, output) {
+
+  setwd("../../")
+  PDATA = reactiveValues()
+  DIRECT_PLOTTING = FALSE
+  
+  
+  .init = reactive({
+    
+    YEAR_L = input$year[1]
+    YEAR_U = input$year[2]
+    GAS = input$gas
+    
+    source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+    
+  })
+  
+  
+  output$plot1 = renderPlotly({
+    
+    YEAR_L = input$year[1]
+    YEAR_U = input$year[2]
+    GAS = input$gas
+    .init()
+    
+    source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+    plot(OUT)
+    
+  })
+  
+  output$plot2 = renderPlotly({
+    
+    YEAR_L = input$year[1]
+    YEAR_U = input$year[2]
+    GAS = input$gas
+    .init()
+    
+    source("r-plots/plot_cumulative_china_2040.R", local = TRUE, print.eval = TRUE)
+    plot(OUT)
+    
+  })
+  
+
+  
+}
+
+
+shinyApp(ui = ui, server = server)

### 2022-12-12 r-report/shiny/app_forecast_china.R

@@ -8,7 +8,7 @@ p_load(shiny)
 
 ui = fluidPage(
   
-  titlePanel("Emissions Forecast for China"),
+  titlePanel("Emissions Forecast, China vs. EU vs. US"),
 
   sidebarLayout(
       sidebarPanel(

### 2022-12-12 r-prep/prep.Rmd
fix

@@
       adp_region_woc = woc & region_ar6_6 == "Asia and developing Pacific",
-      adp_region_deving_woc = adp_region_woc & deving_woc
+      adp_region_deving_woc = adp_region_woc & deving_woc,
+      CO2_FFI = CO2_FFI*1e9
     ) %>% 

### 2022-12-12 r-analysis/data_cumulative_mergeforecast.R

@@ -46,14 +46,16 @@ fdata_2030 = fdata_2030_ghg %>%
 data_2040 = data %>% rbind(fdata_2040) %>%
   arrange(year) %>% 
   group_by(country) %>% 
-  mutate(cum_ghg = cumsum(coalesce(GHG, 0)) + GHG*0)
+  mutate(cum_ghg = cumsum(coalesce(GHG, 0)) + GHG*0,
+         cum_co2 = cumsum(coalesce(co2, 0)) + co2*0)
 
 data_2040 %>% write.xlsx("data-transf/data_cumulative_2040.xlsx", asTable = FALSE, overwrite = TRUE)
 
 data_2030 = data %>% rbind(fdata_2030) %>%
   arrange(year) %>% 
   group_by(country) %>% 
-  mutate(cum_ghg = cumsum(coalesce(GHG, 0)) + GHG*0)
+  mutate(cum_ghg = cumsum(coalesce(GHG, 0)) + GHG*0,
+         cum_co2 = cumsum(coalesce(co2, 0)) + co2*0)
 
 data_2030 %>% write.xlsx("data-transf/data_cumulative_2030.xlsx", asTable = FALSE, overwrite = TRUE)
 

### 2022-12-12 r-report/shiny/app_cumulative_china.R

@@ -15,12 +15,12 @@ ui = fluidPage(
           sliderInput("year",
                       "Years:",
                       min = 1750,
-                      max = 2080,
-                      value = c(1900,2060),
+                      max = 2065,
+                      value = c(1750,2065),
                       sep = ""),
           selectInput("gas",
                       "Gas:",
-                      meta_gas_list,
+                      meta_gas_list[c(1,5)],
                       selected = "GHG"),
     ),
 

### 2022-12-12 r-analysis/data_cumulative_mergeforecast.R
fix

@@ -70,5 +70,8 @@ data_2030 %<>% select(-co2,-GHG) %>%
   gather(key = "gas", value="cumulative",-country,-year) %>%
   filter(gas == {{GAS}} & between(year,{{YEAR_L}},{{YEAR_U}}))
 
+PDATA$is_us = c(2038,NA,NA,NA,2032)
+PDATA$is_eu = c(2031,NA,NA,NA,2027)
+
 PDATA$data_cumulative_2040 = data_2040
 PDATA$data_cumulative_2030 = data_2030

### 2022-12-12 r-plots/plot_cumulative_china_2040.R

@@ -6,5 +6,8 @@ OUT = PDATA$data_cumulative_2040 %>%
   ylab("Cumulative Emissions (tCO2eq)") +
   theme_ghg()+
   scale_fill_brewer(palette="Set2") +
-  theme(axis.title.x = element_blank()) +
-  ggtitle("Cumulative "%.% GAS %.%" Emissions, Realistic Scenario, China vs. EU vs. US, "%.% YEAR_L %.%"-" %.% YEAR_U)
+  theme(axis.title.x = element_blank(),axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
+  ggtitle("Cumulative "%.% GAS %.%" Emissions, Main Scenario, China vs. EU vs. US, "%.% YEAR_L %.%"-" %.% YEAR_U) +
+  geom_vline(aes(xintercept = PDATA$is_us[meta_gas_alc[GAS]],color="United States"), show.legend = NA, linetype = "dotted",size=.2) +
+  geom_vline(aes(xintercept = PDATA$is_eu[meta_gas_alc[GAS]],color="EU-27"), show.legend = NA,linetype = "dotted",size=.2) +
+  scale_x_continuous(breaks=c(seq(1750,2050,by=50),PDATA$is_eu[meta_gas_alc[GAS]],PDATA$is_us[meta_gas_alc[GAS]]))

### 2022-12-12 r-report/Paper.Rmd
latex

---
title: |
  | Asessing China's Climate Responsibility
  | 
  | 
  |
  |
title-meta: "Asessing China's Climate Responsibility"
subtitle: | 
  | **Final Paper**
  |
  | 
  | GRAD-E1402
  | Data Perspectives on GHG Emissions
  | Hertie School of Governance
  |
  |
author: | 
  | submitted by
  | Meier, Constantin
  | Metz, Fabian
  | Mohn, Anna
  | Salzmann, Johann-Friedrich
  |
  | 
author-meta: Johann-Friedrich Salzmann
date: "12 December 2022"
output:
  pdf_document:
    number_sections: true
    citation_package: natbib
    keep_tex: true
    df_print: kable
    latex_engine: pdflatex
bibliography:
  - anna.bib
  - fabian.bib
  - packages.bib
urlcolor: MidnightBlue
linkcolor: MidnightBlue
citecolor: MidnightBlue
geometry: "left=3cm,right=2cm,top=2cm,bottom=2cm"
fontsize: 12pt
biblio-style: agsm
# dcu apacite
header-includes:
  - \usepackage{mathtools}
  - \usepackage{amsmath}
  - \numberwithin{equation}{section}
  - \numberwithin{table}{section}
  - \numberwithin{figure}{section}
  - \usepackage{float}
  - \usepackage{gensymb}
  - \usepackage{setspace}\singlespacing
  - \usepackage{titlesec}
  - \titlespacing*{\section}{0pt}{3cm}{1cm}
  - \usepackage[nottoc]{tocbibind}
  - \setcounter{secnumdepth}{2}
  - \setcounter{tocdepth}{2}
  - \widowpenalties 3 10000 10000 150
  - \displaywidowpenalties 3 10000 10000 150
  - \clubpenalties 3 10000 10000 150
  - \interfootnotelinepenalty 5000
  - \raggedbottom
  - \usepackage{enumitem}
  - \setlist{itemsep=3pt,topsep=5pt,parsep=0pt,partopsep=0pt}
  - \usepackage{hyperref}
  - \hypersetup{bookmarksnumbered=true}
  - \usepackage{bookmark}
  - \newcommand{\sectionbreak}{\clearpage\phantomsection}
  - \let\Begin\begin
  - \let\End\end
  - \newcommand{\Newrow}{\\}
  - \AtBeginDocument{\pdfbookmark[section]{Deckblatt}{front}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='hide', message=FALSE, warning=FALSE)
knitr::opts_chunk$set(fig.height = 4, fig.width = 6)
options(knitr.kable.NA = '',knitr.table.format = "latex")
knitr::read_chunk('r-report/Paper.R')
library(kableExtra)
```

```{r setup-ex}
```

\renewcommand{\harvardand}{\&}
\setcitestyle{authoryear,round,aysep={},notesep={: }}

\thispagestyle{empty}
\pagenumbering{gobble}

\newpage
\pdfbookmark[section]{List of Abbreviations}{decl}
\section*{List of Abbreviations}
\thispagestyle{empty}
\pagenumbering{arabic} 
\onehalfspacing

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|}
    \hline
        AFOLU &  Agriculture, Forestry, Land Use  \\ \hline
        CAT &  Climate Action Tracker  \\ \hline
        CBRD &  Common but differentiated responsibilities and respective capabilities  \\ \hline
        COP &  Conference of the Parties  \\ \hline
        EDGAR &  Emissions Database for Global Atmospheric Research  \\ \hline
        GDP &  Gross domestic product  \\ \hline
        GHG &  Greenhouse gas  \\ \hline
        GNI &  Gross national income  \\ \hline
        GW &  Gigawatt  \\ \hline
        NDC &  Nationally determined contributions  \\ \hline
        REDD+ &  Reducing Emissions from Deforestation and Forest Degradation  \\ \hline
        UNFCCC & United Nations Framework Convention on Climate Change \\ \hline
    \end{tabular}
\end{table}

\singlespacing
\newpage
\pdfbookmark[section]{\contentsname}{toc}
\tableofcontents
\thispagestyle{empty}
\onehalfspacing

# Introduction

\nocite{R-rmarkdown,R-tidyverse,R-eurostat,R-WDI,R-plotly,R-imputeTS,R-kableExtra}
@WorldBank2022a @WorldBank2022b @Worldbank2022c @Giacomo2022

# Data & Assumptions

## Used Data

## General Assumptions

# Analysis

## China’s Self-Characterization as a Developing Country
### Categorization of Developed and Developing Countries
### Comparison of Kaya Identities 
### Comparison of China’s Sector Trends
### Discussion

## China’s Equitable Share in Climate Change Mitigation
### Future Development of China’s Emissions

```{r,fig.cap="Label TEst"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

### Equity Metrics
### Discussion

# Discussion and Conclusion

\appendix
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
\renewcommand{\thesubsection}{\Alph{subsection}}
\newcommand{\subsectionbreak}{\clearpage\phantomsection}
\numberwithin{table}{subsection}

\normalsize
## Session Info (RStudio)

\footnotesize

```{r session-info, results='asis'}
toLatex(sessionInfo(), locale=F) 
```

\normalsize
\singlespacing
\listoffigures
\listoftables

\def\bibpreamble{All online resources were last accessed on 12 December 2022.}
\footnotesize

### 2022-12-12 r-report/Paper.tex
latex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=3cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{mathtools}
\usepackage{amsmath}
\numberwithin{equation}{section}
\numberwithin{table}{section}
\numberwithin{figure}{section}
\usepackage{float}
\usepackage{gensymb}
\usepackage{setspace}\singlespacing
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{3cm}{1cm}
\usepackage[nottoc]{tocbibind}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}
\widowpenalties 3 10000 10000 150
\displaywidowpenalties 3 10000 10000 150
\clubpenalties 3 10000 10000 150
\interfootnotelinepenalty 5000
\raggedbottom
\usepackage{enumitem}
\setlist{itemsep=3pt,topsep=5pt,parsep=0pt,partopsep=0pt}
\usepackage{hyperref}
\hypersetup{bookmarksnumbered=true}
\usepackage{bookmark}
\newcommand{\sectionbreak}{\clearpage\phantomsection}
\let\Begin\begin
\let\End\end
\newcommand{\Newrow}{\\}
\AtBeginDocument{\pdfbookmark[section]{Deckblatt}{front}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{agsm}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Asessing China's Climate Responsibility},
  pdfauthor={Johann-Friedrich Salzmann},
  colorlinks=true,
  linkcolor={MidnightBlue},
  filecolor={Maroon},
  citecolor={MidnightBlue},
  urlcolor={MidnightBlue},
  pdfcreator={LaTeX via pandoc}}

\title{Asessing China's Climate Responsibility\\
\strut \\
\strut \\
\strut \\}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{\textbf{Final Paper}\\
\strut \\
\strut \\
GRAD-E1402\\
Data Perspectives on GHG Emissions\\
Hertie School of Governance\\
\strut \\}
\author{submitted by\\
Meier, Constantin\\
Metz, Fabian\\
Mohn, Anna\\
Salzmann, Johann-Friedrich\\
\strut \\}
\date{12 December 2022}

\begin{document}
\maketitle

\renewcommand{\harvardand}{\&}
\setcitestyle{authoryear,round,aysep={},notesep={: }}

\thispagestyle{empty}
\pagenumbering{gobble}

\newpage
\pdfbookmark[section]{List of Abbreviations}{decl}
\section*{List of Abbreviations}
\thispagestyle{empty}
\pagenumbering{arabic} 
\onehalfspacing

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|}
    \hline
        AFOLU &  Agriculture, Forestry, Land Use  \\ \hline
        CAT &  Climate Action Tracker  \\ \hline
        CBRD &  Common but differentiated responsibilities and respective capabilities  \\ \hline
        COP &  Conference of the Parties  \\ \hline
        EDGAR &  Emissions Database for Global Atmospheric Research  \\ \hline
        GDP &  Gross domestic product  \\ \hline
        GHG &  Greenhouse gas  \\ \hline
        GNI &  Gross national income  \\ \hline
        GW &  Gigawatt  \\ \hline
        NDC &  Nationally determined contributions  \\ \hline
        REDD+ &  Reducing Emissions from Deforestation and Forest Degradation  \\ \hline
        UNFCCC & United Nations Framework Convention on Climate Change \\ \hline
    \end{tabular}
\end{table}

\singlespacing
\newpage
\pdfbookmark[section]{\contentsname}{toc}
\tableofcontents
\thispagestyle{empty}
\onehalfspacing

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\nocite{R-rmarkdown,R-tidyverse,R-eurostat,R-WDI,R-plotly,R-imputeTS,R-kableExtra}
\citet{WorldBank2022a} \citet{WorldBank2022b} \citet{Worldbank2022c}
\citet{Giacomo2022}

\hypertarget{data-assumptions}{%
\section{Data \& Assumptions}\label{data-assumptions}}

\hypertarget{used-data}{%
\subsection{Used Data}\label{used-data}}

\hypertarget{general-assumptions}{%
\subsection{General Assumptions}\label{general-assumptions}}

\hypertarget{analysis}{%
\section{Analysis}\label{analysis}}

\hypertarget{chinas-self-characterization-as-a-developing-country}{%
\subsection{China's Self-Characterization as a Developing
Country}\label{chinas-self-characterization-as-a-developing-country}}

\hypertarget{categorization-of-developed-and-developing-countries}{%
\subsubsection{Categorization of Developed and Developing
Countries}\label{categorization-of-developed-and-developing-countries}}

\hypertarget{comparison-of-kaya-identities}{%
\subsubsection{Comparison of Kaya
Identities}\label{comparison-of-kaya-identities}}

\hypertarget{comparison-of-chinas-sector-trends}{%
\subsubsection{Comparison of China's Sector
Trends}\label{comparison-of-chinas-sector-trends}}

\hypertarget{discussion}{%
\subsubsection{Discussion}\label{discussion}}

\hypertarget{chinas-equitable-share-in-climate-change-mitigation}{%
\subsection{China's Equitable Share in Climate Change
Mitigation}\label{chinas-equitable-share-in-climate-change-mitigation}}

\hypertarget{future-development-of-chinas-emissions}{%
\subsubsection{Future Development of China's
Emissions}\label{future-development-of-chinas-emissions}}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{Label TEst}
\end{figure}

\hypertarget{equity-metrics}{%
\subsubsection{Equity Metrics}\label{equity-metrics}}

\hypertarget{discussion-1}{%
\subsubsection{Discussion}\label{discussion-1}}

\hypertarget{discussion-and-conclusion}{%
\section{Discussion and Conclusion}\label{discussion-and-conclusion}}

\appendix
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
\renewcommand{\thesubsection}{\Alph{subsection}}
\newcommand{\subsectionbreak}{\clearpage\phantomsection}
\numberwithin{table}{subsection}

\normalsize

\hypertarget{session-info-rstudio}{%
\subsection{Session Info (RStudio)}\label{session-info-rstudio}}

\footnotesize

\begin{itemize}\raggedright
  \item R version 4.2.1 (2022-06-23 ucrt), \verb|x86_64-w64-mingw32|
  \item Running under: \verb|Windows 10 x64 (build 22621)|
  \item Matrix products: default
  \item Base packages: base, datasets, graphics, grDevices, methods,
    stats, utils
  \item Other packages: dplyr~1.0.10, eurostat~3.7.10, forcats~0.5.2,
    ggplot2~3.3.6, ggridges~0.5.4, imputeTS~3.3, kableExtra~1.3.4,
    magrittr~2.0.3, openxlsx~4.2.5, pacman~0.5.1, plotly~4.10.1,
    purrr~0.3.4, readr~2.1.2, readxl~1.4.1, stringr~1.4.1,
    tibble~3.1.8, tidyr~1.2.1, tidyverse~1.3.2, WDI~2.7.8
  \item Loaded via a namespace (and not attached): assertthat~0.2.1,
    backports~1.4.1, bibtex~0.5.0, broom~1.0.1, cellranger~1.1.0,
    class~7.3-20, classInt~0.4-8, cli~3.4.0, colorspace~2.0-3,
    compiler~4.2.1, countrycode~1.4.0, crayon~1.5.1, curl~4.3.2,
    data.table~1.14.2, DBI~1.1.3, dbplyr~2.2.1, digest~0.6.29,
    e1071~1.7-11, ellipsis~0.3.2, evaluate~0.16, fansi~1.0.3,
    farver~2.1.1, fastmap~1.1.0, forecast~8.18, fracdiff~1.5-2,
    fs~1.5.2, gargle~1.2.1, generics~0.1.3, ggtext~0.1.2, glue~1.6.2,
    googledrive~2.0.0, googlesheets4~1.0.1, grid~4.2.1, gridtext~0.1.5,
    gtable~0.3.1, haven~2.5.1, here~1.0.1, highr~0.9, hms~1.1.2,
    htmltools~0.5.3, htmlwidgets~1.5.4, httr~1.4.4, jsonlite~1.8.0,
    KernSmooth~2.23-20, knitr~1.40, labeling~0.4.2, lattice~0.20-45,
    lazyeval~0.2.2, lifecycle~1.0.2, lmtest~0.9-40, lubridate~1.8.0,
    modelr~0.1.9, munsell~0.5.0, nlme~3.1-157, nnet~7.3-17,
    parallel~4.2.1, pillar~1.8.1, pkgconfig~2.0.3, plyr~1.8.7,
    proxy~0.4-27, quadprog~1.5-8, quantmod~0.4.20, R6~2.5.1,
    Rcpp~1.0.9, RefManageR~1.4.0, regions~0.1.8, reprex~2.0.2,
    rlang~1.0.5, rmarkdown~2.16, rprojroot~2.0.3, rstudioapi~0.14,
    rvest~1.0.3, scales~1.2.1, stinepack~1.4, stringi~1.7.8,
    svglite~2.1.0, systemfonts~1.0.4, tidyselect~1.1.2,
    timeDate~4021.104, tools~4.2.1, tseries~0.10-52, TTR~0.24.3,
    tzdb~0.3.0, urca~1.3-3, utf8~1.2.2, vctrs~0.4.1, viridisLite~0.4.1,
    webshot~0.5.3, withr~2.5.0, xfun~0.33, xml2~1.3.3, xts~0.12.2,
    yaml~2.3.5, zip~2.2.1, zoo~1.8-11
\end{itemize}

\normalsize
\singlespacing
\listoffigures
\listoftables

\def\bibpreamble{All online resources were last accessed on 12 December 2022.}
\footnotesize

  \bibliography{anna.bib,fabian.bib,packages.bib}

\end{document}

### 2022-12-12 r-report/Paper.R

@@ -1,0 +1,17 @@
+# This is the R code used in the Markdown document. 
+# It is organised in sections like setup-ex below, and will be
+# included in the Markdown main file using the section name.
+
+
+
+##################################################################################
+## ---- setup-ex ----
+
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
+
+
+##################################################################################
+## DATA PREPARATION
+## ---- data-prep ----

### 2022-12-12 r-report/Paper - Copy.Rmd
push

---
title: |
  | Asessing China's Climate Responsibility
  | 
  | 
  |
  |
title-meta: "Asessing China's Climate Responsibility"
subtitle: | 
  | **Final Paper**
  |
  | 
  | GRAD-E1402
  | Data Perspectives on GHG Emissions
  | Hertie School of Governance
  |
  |
author: | 
  | submitted by
  | Meier, Constantin
  | Metz, Fabian
  | Mohn, Anna
  | Salzmann, Johann-Friedrich
  |
  | 
author-meta: Johann-Friedrich Salzmann
date: "12 December 2022"
output:
  pdf_document:
    number_sections: true
    citation_package: natbib
    keep_tex: true
    df_print: kable
    latex_engine: pdflatex
bibliography:
  - anna.bib
  - fabian.bib
  - packages.bib
urlcolor: MidnightBlue
linkcolor: MidnightBlue
citecolor: MidnightBlue
geometry: "left=3cm,right=2cm,top=2cm,bottom=2cm"
fontsize: 12pt
biblio-style: agsm
# dcu apacite
header-includes:
  - \usepackage{mathtools}
  - \usepackage{amsmath}
  - \numberwithin{equation}{section}
  - \numberwithin{table}{section}
  - \numberwithin{figure}{section}
  - \usepackage{float}
  - \usepackage{gensymb}
  - \usepackage{setspace}\singlespacing
  - \usepackage{titlesec}
  - \titlespacing*{\section}{0pt}{3cm}{1cm}
  - \usepackage[nottoc]{tocbibind}
  - \setcounter{secnumdepth}{2}
  - \setcounter{tocdepth}{2}
  - \widowpenalties 3 10000 10000 150
  - \displaywidowpenalties 3 10000 10000 150
  - \clubpenalties 3 10000 10000 150
  - \interfootnotelinepenalty 5000
  - \raggedbottom
  - \usepackage{enumitem}
  - \setlist{itemsep=3pt,topsep=5pt,parsep=0pt,partopsep=0pt}
  - \usepackage{hyperref}
  - \hypersetup{bookmarksnumbered=true}
  - \usepackage{bookmark}
  - \newcommand{\sectionbreak}{\clearpage\phantomsection}
  - \let\Begin\begin
  - \let\End\end
  - \newcommand{\Newrow}{\\}
  - \AtBeginDocument{\pdfbookmark[section]{Deckblatt}{front}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='hide', message=FALSE, warning=FALSE)
knitr::opts_chunk$set(fig.height = 4, fig.width = 6)
options(knitr.kable.NA = '',knitr.table.format = "latex")
#knitr::read_chunk('r-report/Paper.R')
library(kableExtra)
```

```{r setup-ex}
source('r-imports/init.R')
source('r-analysis/meta.R')
```

\renewcommand{\harvardand}{\&}
\setcitestyle{authoryear,round,aysep={},notesep={: }}
\nocite{R-rmarkdown,R-tidyverse,R-eurostat,R-WDI,R-plotly,R-imputeTS,R-kableExtra}

\thispagestyle{empty}
\pagenumbering{gobble}

\newpage
\pdfbookmark[section]{List of Abbreviations}{decl}
\section*{List of Abbreviations}
\thispagestyle{empty}
\pagenumbering{arabic} 
\onehalfspacing

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|}
    \hline
        AFOLU &  Agriculture, Forestry, Land Use  \\ \hline
        CAT &  Climate Action Tracker  \\ \hline
        CBRD &  Common but differentiated responsibilities and respective capabilities  \\ \hline
        COP &  Conference of the Parties  \\ \hline
        EDGAR &  Emissions Database for Global Atmospheric Research  \\ \hline
        GDP &  Gross domestic product  \\ \hline
        GHG &  Greenhouse gas  \\ \hline
        GNI &  Gross national income  \\ \hline
        GW &  Gigawatt  \\ \hline
        NDC &  Nationally determined contributions  \\ \hline
        REDD+ &  Reducing Emissions from Deforestation and Forest Degradation  \\ \hline
        UNFCCC & United Nations Framework Convention on Climate Change \\ \hline
    \end{tabular}
\end{table}

\singlespacing
\newpage
\pdfbookmark[section]{\contentsname}{toc}
\tableofcontents
\thispagestyle{empty}
\onehalfspacing

# Introduction

The development that the People's Republic of China has taken in recent decades is nothing short of remarkable. While the country, under the dictatorial leadership of Mao Zedong, was plagued by poverty and famine during the first three decades after its founding in 1949, Deng Xiaoping's policy of reform and opening started the country's economic boom in the late 1970s. Millions of Chinese have made the leap out of poverty since, and the country, which at the beginning of the 21st century was still considered the "workbench of the world", has now developed into an economic and technological superpower that is readying itself to overturn the global supremacy of the U.S..

During the same period, China's emissions have risen rapidly. In 2004, the country surpassed the U.S. as the world's largest greenhouse gas emitter and is likely to retain that title for some time. In 2019, more than 25% of all global greenhouse gas emissions came from China, more than the U.S. and (at the time still) EU-28 combined (see Figure 1). As a consequence of this development, China's emissions profile changed dramatically: While the agricultural sector still accounted for a large share of emissions in the early 1970s, its contribution has been only marginal in recent years. Figure 2 shows the large-scale industrialization of the country starting in the mid-1990s and the corresponding increase in emissions from the energy sector. More recently, transport sector emissions have picked up speed, likely reflecting the wealthy share of China’s citizens spending more money on individual (fossil-fuel based) modes of transport.

China’s energy mix is still largely dominated by coal. In 2020, more than 60% of the country’s total energy supply stemmed from this fossil fuel. Renewables on the other hand only contributed 6.2% to total energy supply (excluding biofuel and waste). Looking at just the electricity production, the numbers are a bit different: Here the renewable sources’ share was approx. 28% [@IEA2022]. However, China remains the country with the world’s largest coal fleet and also the highest planned coal capacity additions. In 2021, the country started building 33 GW of additional coal-based power generation and consumed about five times as much coal as India, and nearly six times as much as the U.S. [@Green2022].

Chinese carbon emissions growth was predominantly driven by its rapid economic development, which in turn caused the energy sector to grow too. Since the year 2000, China's GDP per capita has more than quadrupled, while carbon emissions have more than tripled in the same period (see Figure 3). However, the growth of emissions has slowed in recent years, as energy intensity of GDP had started decreasing after the year 2005 and also carbon intensity of energy peaked in 2010 and has been slowly decreasing since. While for the first two decades of the 21st century carbon emissions growth rates were closely resembling the growth rates of GDP per capita, since 2010 the two numbers have decoupled. China’s immense expansion of renewable energy sources over the last years is likely an underlying driver of this trend, however, as we have seen, Chinese annual emissions remain very high at 14.2 GtCO2e in 2019.

The question arises, how China plans to curb its emissions. At the United Nations General Assembly in 2020, Chinese President Xi Jinping announced the goal of Chinese carbon neutrality before 2060 [@Jinping2020]. This was the first time China officially committed to a long-term emissions reductions goal [@CAT2022]. One year later, in November 2021, ahead of COP26, China submitted its updated NDC to the UNFCCC. Accordingly, the country plans to peak its carbon emissions before 2030, decrease the carbon intensity of GDP by over 65% (relative to 2005), have around 25% of non-fossil fuels in primary energy consumption by 2030, increase the forest stock volume by six billion cubic meters until 2030 and have 1,200 GW of wind and solar power capacity installed by the same year [@China2022]. Although some of these objectives are vague to some degree, and the emissions reduction target is only a relative goal, the ambitions China has set for itself are a marked improvement over the targets set out in the previous 2016 NDC. Additionally, it is important to note that these goals are unconditional and hence not relying on external climate finance. China has adopted numerous policies to support its international targets, such as the “Working Guidance for Carbon Dioxide Peaking and Carbon Neutrality” and the “Action Plan for Carbon Dioxide Peaking Before 2030”. The former spells out a set of principles and sectoral goals to achieve carbon dioxide peaking and carbon neutrality, among them the need to exercise nationwide planning and the prioritization of conversing energy (Department of Resource Conservation and Environmental Protection, 2021a). The latter defines key tasks for driving the low-carbon energy transition or saving energy, carbon emission mitigation and efficiency improvement [@DRCEP2021b]. With its “14th Five-Year Plan on Renewable Energy”, the country aims to further accelerate its renewable energy expansion. By 2025, 33% of electricity ought to be supplied by renewable sources (18% non-hydro), which could decrease annual carbon emissions by 2.6 gigatons [@Zhou2022].

Nonetheless, China's goals and policies are widely viewed as inadequate by various parties. The CAT for example projects that China is likely to comfortably overachieve its NDC targets without substantially increasing its current mitigation efforts. Hence, their overall rating of the country’s goals and policies is “insufficient”. If all countries were to pursue the same level of ambition as China, global warming would reach approx. 3°C. Therefore, China’s current goals and policies leave significant room for further target-raising ambition. The CAT additionally concludes that China’s contributions are also not sufficient to do its “fair-share” in fighting climate change and limiting global warming under the Paris Agreement [@CAT2022].

China itself assesses its responsibility for climate change mitigation measures very differently though. In its 2021 NDC update, China assigns responsibility for global warming to developed countries. It were their emissions that had caused the dramatic increase of GHGs in the atmosphere. China, on the other hand, was a developing country, thereby having the right to develop [@China2022].

This line of argument is as old as the UNFCCC itself. In 1992, at the first COP in Rio de Janeiro, where the parties agreed on the UNFCCC, they classified countries into two groups of “Annex-I” and “non-Annex I” countries, consisting of mostly developed and (at the time) developing countries respectively. At the same time the principle of common but differentiated responsibilities and respective capabilities (CBRD) was introduced. According to this principle, the industrialized nations would need to bear the main responsibility when it comes to emission reductions, while the "non-Annex I" countries would initially have no obligations to avoid emissions. This principle was also enshrined in the 1997 Kyoto Protocol. The 2015 Paris Agreement reaffirmed the CBRD principle, but, for the first time, brought all signatory countries together to undertake ambitious efforts to tackle climate change and adapt to its impacts [@UNFCCC2015]. However, it has caused long-standing debates, whether China should continue to be classified as a developing country, given its economic and emissions growth since the UNFCCC was adopted, or whether it has a greater responsibility in addressing climate change.

With these developments in mind and following up on China’s claim to be a developing country, we set out in this paper to discuss equity considerations for China, focusing on two research questions. First, we will investigate whether China, from an emissions perspective, can still be characterized as a developing nation. For this we compare China’s Kaya identity with other developing and developed nations. Furthermore, we consider China’s sectoral emissions trends and contrast them with those of (other) developing and developed nations, controlling for differences in population size and GDP. Secondly, we investigate China’s claim of developed countries’ being the driver of climate change, by calculating different measures of (historic) responsibility and assess the level of responsibility China bears in combatting climate change. We discuss these findings with regards to a projection of China’s cumulative emissions.

The remainder of this paper is structured as follows: In section 2 we provide an overview of our data and main assumptions, before analyzing China’s self-characterization as a developing country in section 3. Section 4 compares different equity metrics for China and other big emitters and discusses China’s role in addressing climate change against different scenarios of future Chinese cumulative emissions. In section 5 we discuss our findings in light of other available assessments of China’s role and conclude.

```{r,fig.cap="Figure 1"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

```{r,fig.cap="Figure 2"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

```{r,fig.cap="Figure 3"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

# Data & Assumptions

Our project is data-driven in nature and relies heavily on the availability of various metrics on both greenhouse gas emissions and measures of (economic) development. Furthermore, there are key assumptions connected to our analysis that impact our findings. This section provides an overview of the data-sets we use, and makes our underlying assumptions about the data explicit.

## Used Data

In terms of data on GHG emissions we make use of the EDGAR database as the core of our analysis. It contains yearly emissions data on the major greenhouse gases by country and sector and makes them commensurable based on global warming potentials on a 100-year scale. The database and its development are a joint project of the European Commission Joint Research Center and the Netherlands Environmental Assessment Agency [@EC2022].

We supplemented this data set with data on LULUCF emissions from the national GHG inventory database and add them to the total GHG emissions. The data itself was sourced from annual GHG inventories for Annex I countries and gathered from recent communications, biennial update reports, REDD+ submissions and NDCs for Non-annex I countries [@Giacomo2022].

For consumption-based emissions of selected countries since 1990 we make use of an updated dataset from Peters et. al [updated from @Peters2011]. Additionally, we rely on world bank data for GDP, GNI and population [@WorldBank2022d].  We further hand code variables for countries, specifically their membership to the EU 27 & 28 respectively, as well as their income classification according to the 2019-word-bank-classification for gross national income per capita [@WorldBank2018]. Lastly two datasets were made available to us a) an inventory of CO2 emissions since 1750 and b) IEA data for energy consumption.

## General Assumptions

Regarding our main assumptions we limit our analysis to years until 2019 as we believe that the pandemic heavily distorted prior trends and hit countries and their economies to varying extents, making any meaningful interpretation and comparison difficult. Our main assumption here is that the trends and developments up to 2019 are more meaningful indicators for developments in the years and decades to come, compared to the pandemic years.

To make information accessible and to allow for comparisons across gases we choose to provide all information on multiple GHGs based on 100-year global warming potentials, as provided in our core database EDGAR.

# Analysis

TO BE DONE: Intro statement.

## China’s Self-Characterization as a Developing Country

In the following, China’s self-characterization as a developing country will be critically reviewed from an emissions perspective. For this, a definition of developed and developing countries will be developed. This is followed by a comparison of China’s emissions development with the emissions development of other developed and developing nations by using a Kaya decomposition. As the distribution of emissions by sector is another way to distinguish between developing and developed countries, China’s sectoral emissions are also compared to other countries. With this, we strive to find an answer to our first research question.

### Categorization of Developed and Developing Countries

To distinguish between developed and developing countries, different indicators can be considered for instance GDP per capita, the gross national income GNI per capita or the human development index (HDI). Furthermore, other indicators such as the level of education or democracy can be taken into account when determining whether a country is developed, developing or underdeveloped [@Kinnunen2019].

Our main data set, the EDGAR dataset, already provides a classification of countries in two groups – developed and developing – which we will use as a starting point. According to this, China is categorized as a developing country. However, we realized that a more granular categorization of countries might be helpful to answer our first research question. Especially since any type of self-categorization might be biased as countries stand to gain from underestimating their development in order to receive more aid and have less responsibilities in the UNFCCC process.

Thus, we decided to use a second country classification scheme for comparison. Although a financial indicator might not completely summarize a country’s level of development, we decided to use the GNI cut-offs as our main indicator of development. This is mainly because research finds that the GNI correlates with a number of accepted indicators of development outcomes [@Fantom2016]. Furthermore, the income classification is the standard classification in discussions on development. The World Bank, but also other international organizations and aid agencies, use this for analytical and operational purposes. The GNI is calculated in the following way:

TO BE DONE FOrmula

Thus, going forward we will also use the World Bank’s Classification of Countries by income, which assigns countries into four different groups: high income, upper-middle income, lower-middle income, low income. Income is measured using the GNI per capita of the previous year in U.S. dollars using a three-year average exchange rate. The classification is updated each year. For our analysis, we are using the threshold valid as of July 2019, as our emissions analysis considers this year as the last year. The thresholds are as follows:

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|}
    \hline
        \textbf{Group  } & \textbf{Thresholds July 2019 in \$  } \\ \hline
        Low income   & \$< 1,026\$ \\ \hline
        Lower-middle income   & \$1,026 - 3,955\$ \\ \hline
        Upper-middle income  & \$3,966 - 12,375\$ \\ \hline
        High income  & \$> 12,375\$ \\ \hline
    \end{tabular}
\end{table}

According to the World Bank’s classification, China is classified as an upper-middle income country since 2010 [@WorldBank2022d].

To make use of the more granular look at country groups in relation to our research question, we assume low- and lower-middle income countries to be more likely resembling  developing nations and middle-upper- and high-income countries to be more likely resembling developed nations.

### Comparison of Kaya Identities

With a Kaya identity, one can identify the main driving forces of CO2 emissions in a certain period. The Kaya identity expresses CO2 emissions (F) as a function of GDP (G), population (P) and energy (E):

TO BE DONE FOrmula

The term highlights the different components of the identity: G/P is GDP per capita, E/G is the energy intensity of GDP and F/E is the carbon intensity of energy [@Lamb2021]. By comparing Kaya identities of different regions, we can also discuss regional differences. Hence, we use the Kaya identity to discuss if the driving forces of emissions show similarities with developing or developed nations.

Figure 4 displays China’s and developing and developed countries’ Kaya identities according to the IPCC classification in the Sixth Assessment Report from 2000 to 2019. In those years, China’s GDP per capita was growing with a factor close to five, thereby being the strongest upward driver of emissions. GDP per capita increased almost in tandem with carbon emissions until 2010, in which a decoupling took place. Ever since, Chinese emission’s growth rates have been much slower than those of GDP per capita. This decoupling is likely due to the decreasing energy intensity of GDP and carbon intensity of energy at the same time. The energy intensity is the main counteracting factor on Chinese emissions and decreased constantly since 2005. The decreasing trend seemed to have already started in 2000 but had rebounded before 2005, which can be traced back to 2001, when China joined the WTO [@Zheng2020]. However, since 2010 the decrease has been significant, hence driving the reduction of overall emissions growth rate. Furthermore, one can see that carbon intensity of energy decreased since 2010 meaning that the amount of CO2 per unit of energy is decreasing. Nevertheless, the relationship remains a positive one. The decline of both the energy intensity and carbon intensity is likely due to economic efficiency improvements. Additionally, carbon intensity further declined because of increasing capacity additions of renewable energies (changes in the fossil share) and the reduced emission intensity of fossil fuels (changes in the fossil intensity, fuel switch) [@Zheng2020] TBD  [@Peters2017]. Population changes only played a minor role but can be considered as a persistent upward driver of emissions.

Comparing China’s Kaya identity to the decomposition of the development of CO2 emissions of developing and developed countries does not provide a clear result on whether China can be considered a developing or developed nation. In general, economic growth is the main driver of CO2 emissions, both in developed and developing nations. However, GDP per capita growth is much larger and hence closer to China’s figures in developing nations as they show a greater growth potential. Overall carbon emissions are decreasing in developed nations while they are increasing in developing nations and China. This supports the notion of China being a developing country relying on emissions driven growth. On the other hand, China’s energy and carbon intensity are decreasing as it is the case for developed countries. The population’s development of China also more closely resembles the trend of developed countries than those of developing countries. To sum up, this classification does not clearly indicate whether China is a developing or developed country. As mentioned above, comparing China to a more granular classification of countries might be worthwhile, as the EDGAR dataset for example considers Saudi-Arabia, a country with one of the highest GDP per capita as a developing nation.

```{r,fig.cap="Figure 4"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

Thus, in the next steps, the World Bank’s Income Classification Scheme will be used for comparison (Figure 5). In high-income countries, GDP per capita and population are increasing only at low levels (by roughly the factor 0.5 and 0.2 respectively). Carbon intensity and energy intensity are decreasing, keeping carbon emissions down. The carbon intensity is decreasing because of two factors: the fossil intensity and the fossil share. In contrast, in low-income countries, the growth of CO2 emissions is exceeding the growth of GDP per capita, both rising by a factor of 2.8 and 5 respectively over the observed time span. This is driven by a high and increasing carbon intensity. Furthermore, population growth plays an important role in this group, and can be considered a further driving factor of CO2 emissions. The only contrasting factor is the decreasing energy intensity. Comparing both groups of countries to China, one can resume that China’s development does not fit in either of the groups perfectly. Like before China’s Kaya decomposition shares similar characteristics as both groups: The small population growth resembles the trend of high-income countries, the dramatically decreasing energy resembles the trend of low-income countries. Considering lower-middle income countries, they seem to show upwards trends in any of the indicators except for energy intensity. In comparison, in upper-middle income countries carbon emissions and GDP per capita develop in tandem, while carbon intensity and energy intensity only fluctuate around zero in the years from 2000 to 2019.

```{r,fig.cap="Figure 5"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

To conclude, China seems to be an exception considering the driving forces of emissions and thus cannot be assigned uniquely to any of the studied group of countries. This is especially due to the exceptionally high GDP growth which only recently decoupled from carbon emissions. In terms of GDP growth rates and carbon emission growth, China can be considered a developing nation as they base their GDP growth on growing carbon emissions. However, the carbon and energy intensity that keep CO2 emissions down, show that China is already getting more efficient in its production and that it has the capacity to invest in renewable energy source. Considering only those two indicators, China can be better compared to developed countries. Thus, it seems that China has a responsibility to put forward this trend of efficiency gains in order to decouple economic growth and emissions even more. To examine the status of China in more depth, China’s sectoral trends will be compared to the two discussed classification schemes in the following. This can provide further information on China’s classification, since developing and developed nations usually generate wealth in different economic sectors.

### Comparison of China’s Sector Trends

In this part, sector trends of different groups of countries will be considered using the same two categories of country groups as before. We take into account five sectors: energy, industry, transport, AFOLU (which in the EDGAR database only includes agricultural emissions), and buildings. China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 6 & 7. Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively. Only smaller shares are attributable to transport (6%), buildings (5%) and AFOLU (6%).

In developed countries (according to the EDGAR classification), energy and industry still account for the majority of emissions (58% in total), but transport emissions play a much larger role (21%) of the GHG emissions than in China. This high share of transport emissions can be accounted to the high use of private cars in developed economies. For instance, the EU road transport accounts for 77% of GHG emissions in the transport sector in 2020 [@EEA2022]. AFOLU emissions and emissions from buildings each account for roughly 10% of the total GHG emissions.  
In contrast, in developing nations, the share of AFOLU emissions is much larger (21%). The high share is typically associated with the expansion of agriculture into carbon-dense tropical forests, but also the lack of economic development of other sectors. The share of transport, however, is much lower than in developed countries as individual transport is not that widely spread. The relative emissions in energy and industry are comparable to those in developed countries as developing countries are rapidly growing to fulfil their own and the developed countries’ consumption needs. However, absolute emissions levels are much lower.

Again, China’s split of emissions does not fit in either of the two categories. On the one hand, China’s share of emissions coming from the AFOLU sector is relatively small resembling developed country characteristics. On the other hand, their emissions from transport sector are small as well. This is due to the immense share of emissions stemming from industry and energy, which reduces the share of emissions in the other sectors.

```{r,fig.cap="Figure 6"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 7).

In this classification, differences between high-income and low-income countries are very pronounced. While in high-income countries a major share of emissions resulted from energy systems (37%) in 2019, the share of emissions from energy only accounts for 9% of all GHG emissions in low-income countries. This highlights an energy system largely depending on fossil fuels in high-income countries on the one hand, and the lack thereof in low-income countries on the other hand. The differences are also immense considering the transport sector. In high-income nations, 20% of the GHG emissions stem from transport, while in low-income countries, the share is only 7%. However, the biggest differences are the AFOLU emissions. High-income countries have a share of 9% for AFOLU emissions while in low-income countries this sector accounts for 57% of emissions. The reasons for these differences were discussed above.

The emissions by sector for lower-middle and upper-middle income countries are more similar, the only difference is that the share of AFOLU is larger in lower-middle income countries and the share of transport is larger for upper-middle income countries, indicating further progress on the typical developing path of the latter country group.

Again, China does not really fit into either of the categories due to its very high share of emissions stemming from the energy and industry sector. China's relative emissions from these two sectors are much larger than in any of the other groups studied.

```{r,fig.cap="Figure 7"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 8).

Comparing trends is particularly helpful, as emissions from the energy and industry sector in China are so large, that it makes any comparison of the remaining sectors with the potential peers very difficult.

China’s AFOLU emissions per capita are relatively low and decreasing over time, similar to the emissions in lower-middle income countries in this sector. The AFOLU emissions per capita of high income and upper-middle income countries are large because a relatively high agricultural output spread over relatively small populations. In the building sector, Chinese emissions per capita are relatively low compared to high-income countries and rather on the same level as upper-middle income countries. The per-capita emissions of the building sector are high in richer countries as people require more floor space per capita compared to lower-income countries. For transport, China’s emissions stayed on a low level until 2000 and then increased at high speed. Now, they are comparable to per capita emissions of upper-middle-income countries.

Considering the three sectors mentioned above, China seems to resemble more the emissions per capita characteristics of lower-middle or upper-middle income countries, however this is different for the energy and industry sectors. In the energy sector, China’s emissions per capita increased up to roughly 4 tCO2eq in 2019. This is much higher than for upper-middle income countries, in which per capita emissions stayed relatively constant at 3 tCO2eq in 2019. In high-income countries, the per capita emissions from energy are still higher (5 tCO2eq) in 2019 than in China, however, one can see a downward trend there. Thus, one could argue that China can soon be compared to a high-income country regarding its per capita energy system emissions. The same holds for the industry sector, where this development is even more pronounced. Emissions per capita in the industry sector in China increased massively in the 2000s and are now at a plateau of 4 tCO2eq annually. The per capita emissions of high-income countries in the industry sector in contrast have decreased since the 1970s and are now at 3 tCO2eq. In the industry China has thus already surpassed per capita emissions levels of high-income countries and has the highest value among the five studied panels in this sector.

```{r,fig.cap="Figure 8"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

### Discussion

The prior analysis has shown that clearly classifying China as either a developed or a developing from an emissions perspective remains difficult.

However, what this analysis has clearly shown, is that the simple self-characterization of China as a developing country, that is mirrored by Sixth assessment report of the IPCC, does not do justice to the drastic economic and emissions development China has witnessed in the last decades. As the analysis has shown, China clearly exhibits certain emission characteristics of developed countries in some sectors like industry and energy systems. When it comes to agricultural per capita emissions trends it is comparable to lower-income countries. Maybe most importantly, in the industry sector it has the highest per capita emissions of any of the candidates that were up for comparison.

What this analysis has undoubtedly confirmed is the realization that China is a special case in every respect. China's unique economic development, which has led to a five-fold increase in GDP per capita over the past two decades, saw the country develop an energy and industrial system that together accounts for 82% of the country’s total emissions, a share 20% higher than that of high-income countries.

Nevertheless, one needs to consider that development is not equally distributed in China. The rural population has benefited significantly less from the economic development than the urban population (East-West divide) [@Knight2004].  However, the argument that one still has the right to predominantly emissions-based development (as in 1992) is no longer in line with China's current status as the world’s biggest emitter. Hence, China's NDC’s storyline, which seeks the main responsibility for climate change in developed nations, is too undercomplex and does not do justice to the evolved realities.

To further investigate this issue, in the next we will predict the future development of emissions of China and other countries and further consider different equity metrics.

## China’s Equitable Share in Climate Change Mitigation

The following chapter discusses China’s equitable share in climate change mitigation. In order to answer the research question, we will first discuss the future development of China’s emissions, to determine when China will become the biggest cumulative emitter. For this, we consider multiple development pathways of China in terms of emissions and discuss China’s cumulative emissions in comparison to other countries. Moreover, we will present different rankings of absolute emissions, per capita emissions, GDP and GDP per capita, cumulative emissions and consumption-based CO2 emissions to discuss China’s responsibility from different perspectives.

### Future Development of China’s Emissions

The first equity metric we consider is cumulative emissions, as China claims historic developed countries’ emissions being the main driver of climate change. Looking at cumulative emissions from 1750 until 2019, China is on 3 rd position, only behind the U.S. and the EU-27. According to this, in 2019 China would already have the 3rd-largest responsibility to reduce emissions, since it has historically  emitted a total of 12.4% of all greenhouse gases. This is in direct contrast to the country’s claim to be less responsible for the warming climate.

Importantly, if China continues its emissions pathway, it will become the largest cumulative emitter at some point. In order to estimate when China will move into first place, we have modeled expected emission trends for China as well as for the EU and the U.S. Our modelling is based on the following assumptions:

First, for simplicity, we assume that China will reduce not only CO2 emissions, as communicated internationally, but all GHG emissions to zero. As we have seen in section 3, Chinese emissions trends vary strongly across sectors. Therefore, we have modelled each sector’s future emissions pathway following different assumptions. In general, we assume a constantly declining growth rate of emissions in each sector until a peak year starting with the 2018 to 2019 growth factor. After the peak we consider an s-curve emissions reduction for the following years until zero emissions are reached, as China might first use the simple levers to reduce emissions fast and then needs to work on emissions which are difficult to bring down.

As emissions in the AFOLU sector have already been decreasing in China, we expect a relative flat emissions level until 2025, followed by a decrease until zero emissions are reached in 2060. Buildings are assumed to peak emissions in 2030 and are at zero in 2060. The energy systems sector is expected to peak the earliest, in 2028, due to the continued heavy roll-out of renewable energy sources in China and the experiences from other countries decarbonization journeys. Complete decarbonization is then assumed to be reached by 2055. We assume the industry sector to peak by 2030 and reach complete decarbonization by 2065. As transport is the fastest growing sector of Chinese emissions, we assume this trend to continue (but slowed down) until 2040, and complete decarbonization in 2065.

In modeling the development of emissions for the EU-27 and the U.S., we are guided by data from the PBL Netherlands Environmental Agency [@PBL2022]. For simplicity we do not differentiate by sector but assume a linear decrease in annual emissions up to the projected emissions value for 2030 in both the U.S. and the EU-27. Thereafter, we also use an s-shaped reduction curve to achieve zero emissions by 2050.

The resulting sectoral emissions pathways for each country/region are depicted in figure xx. The resulting cumulative emissions forecasts for the three countries/blocks are shown in figure xx. Accordingly, China will pass the EU-27 in cumulative GHG emissions in 2027 and is projected to pass the U.S. in 2032 . Afterwards it will be the largest cumulative emitter.

These projections hold even when modelling each sector according to the Chinese NDC (assuming peak years of 2030 and zero emissions by 2060). In the NDC-scenario China will surpass the EU and US respectively in the same years as modeled in our main scenarios, but at different emission levels – 452.4 GtCO2eq (main scenario)  451.8 GtCO2eq (NDC-scenario). When projecting only  CO2 emission developments1 China will surpass the EU in 2031 and the US in 2038 according to both scenarios.

This analysis shows that maintaining targets that are ambitious in absolute terms but relatively easy to achieve compared to China's size and economic power, have already put China at the forefront of global responsibility for climate change. From a cumulative emissions perspective, China definitely has the same if not larger GHG reduction obligations as many developed countries, especially when considering that a majority of China’s emissions were emitted after the problem of climate change has made it on top of the global policy agenda. Moreover, the statement of the Chinese NDC that climate change is mainly caused by others is not tenable.

```{r,fig.cap="Figure 9"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

However, cumulative emissions, while easily understood, are not the only conceivable equity metric to consider when attempting to assess a country's fair share in responding to climate change. Therefore, in the following sub-section we investigate other equity metrics.

### Equity Metrics

This chapter presents different rankings which can shed light on the question of China’s responsibility to mitigate climate change from different angles. The following rankings always display the top 10 countries (or in case of the EU regions) in the respective category. Furthermore, other important countries are added for comparison as well as a category named “Other” which summarizes the share of all remaining countries. The EU-27 is mentioned as a point of reference, but emissions of the separate countries are displayed in the ranking or summarized in the “Other” category. Every graph also provides reference points for the rank position where cumulative 50 % of global GDP, population and emissions are surpassed.

First, we consider China’s responsibility based on absolute emissions in the year 2019 (Figure X). In the ranking, China ranks on first place with absolute emissions of 14,219.37 Mt CO2 eq. This is more than double of the U.S. emissions (6,266.8 Mt CO2 eq) and also close to the emissions of all other countries that do not belong to the group of the top 10 emitters combined (14,075.12 Mt CO2 eq). Together with the U.S., India and Russia, China makes up for 50% of global emissions, but these four countries do not produce half of the global GDP, nor do they represent half of the world’s population. This highlights that the responsibility of these four countries to drastically reduce emissions is high. Considering that China is producing more than double the emissions of the U.S., China has by far the highest responsibility to mitigate climate change from a current absolute emissions perspective.

```{r,fig.cap="Figure 10"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

Next, we consider emissions per capita (Figure x). This is important as China is the country with the biggest population worldwide of approx. 1.4 billion people [@WorldBank2022c]. Looking at this ranking, it is important to consider that the top emitters according to per capita emissions are relatively small countries with low absolute emissions but also small populations. Thus, when it comes to reducing absolute emissions and fighting climate change, they can only play a minor role. China interestingly ranks on place 43 with roughly 10t CO2 eq / capita, before EU-27 but behind the U.S. (Ranking: 17). According to this equity metric, China’s fair share to mitigate climate change from this perspective should be located between the share of these two countries/groups of countries.

```{r,fig.cap="Figure 11"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

Considering GDP and GDP per capita refers to the capacity of acting on climate change, following the assumption that richer countries have more resources available to fight climate change. As Figure XX shows, China had the highest GDP of all countries in 2019, with USD 22.49 trillion. Based on this, China would theoretically have to make the greatest conribution to reduce emissions. Absolute GDP, however, is limited in telling us about a country's actual capacity because it ignores population size. Therefore, considering GDP per capita might be more worthwhile. Here China only ranks 81st place in the world. Therefore, China’s responsibility is relatively low from the GDP per capita perspective. In comparison, the U.S. rank on place 11. Countries that are in the top 10 emitters are often relatively small countries deriving their wealth from natural resources. Hence, they have a high responsibility to mitigate climate change as they have the ability to pay for climate change mitigation measures. However, their absolute emissions are relatively small and thus an ambitious reduction might not make a huge difference for achieving climate targets. Thus, one should consider that these countries should specifically contribute by providing financial aid to mitigate emissions elsewhere.

```{r,fig.cap="Figure 12"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

```{r,fig.cap="Figure 13"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)

plot(OUT)
```

### Discussion TBD

To sum up, China has a very high responsibility to mitigate climate change, even the highest responsibility of all countries when considering some of the discussed equity metrics. Based on our calculations, China is likely surpass the EU well before 2030 and the US shortly after in 2032  in terms of cumulative emissions over all GHGs from 1850 to 2019 and a modeling of emissions thereafter. The difference in emissions from all GHGs to CO2 emissions highlights the importance to extend the frame of historic respon

Therefore, China now has a major responsibility to reduce emissions which is reinforced when considering that the country’s massive emissions growth only started after the adoption of the Kyoto Protocol in 1997, at a time when the consequences of climate change were already being heavily discussed.

However, we also need to consider that China only ranks on 81st. and 43rd place considering their GDP per capita and their emissions per capita, respectively. This diminishes China’s responsibility to some extent, showing that the global community needs to grant space for economic development to be fair. However, this economic development should ideally be decoupled from a growth in emissions. If we look at the per capita emissions of the countries that rank first, we see that these are mostly very small and, from the perspective of absolute emissions, less important countries. Although these countries might have a high ability to pay from a per capita perspective, their overall economic power is not high. The opposite is true for China. China ranks first place in absolute emissions and GDP in 2019 with a great distance to the following places.

Thus, China has one of the greatest responsibilities to reduce emissions from a historic emissions, current emissions and economic capacity perspective.

# Discussion and Conclusion TBD

In our analysis, we were striving to answer two research questions, namely if China can be considered a developing country and what China’s fair share in climate change mitigation should be.

Regarding out first research question, we find that China cannot be easily classified as a developed or developing country. This is due to the unique economic growth (China’s GDP per capita quintupled in the last 20 years), which went hand in hand with very high energy and industrial sectors’ emissions. Comparing these to other developed countries, one can see that China clearly exhibits these countries’ characteristics in term of sectoral emissions. However, China’s agricultural per capita emissions trends are more comparable to lower-income countries.

Our analysis of different equity metrics for the second research question has shown that China not only has a huge responsibility to curb emissions, but also the financial capability to do so. The country is the world’s largest emitter in annual and cumulative terms (based on our data) and has the highest GDP of all countries. While it is important to acknowledge further room for development, one cannot disregard the fact that without significant emission reductions from China, any attempt to stay within the temperature limits of the Paris Agreement is sure to fail.

Hence, we believe that China’s fair share is much higher than what they currently plan to do. Together with the EU-27 and the U.S., China should bear the highest responsibility for climate change mitigation. Its self-classification as a developing country is clearly politically motivated, to not give in to the demands of having to do more. At the same time, the political leadership in Beijing can present itself as a top student in the international community by effortlessly surpassing its own goals, as it is expected by different observers (Climate Action Tracker, 2022).

In the following, our analysis will be contrasted with two other assessments of China’s fair share – the assessment by the Climate Action Tracker and by the Climate Equity Monitor.

The CAT evaluates the fair share of a country based on assessments in the literature. The results of the literature are categorized using seven equity indicators ranging around considerations of responsibility, capability, cost-effectiveness and equality, which are weighted equally in the analysis. All results of the evaluated studies are then depicted on a scale for each category and a 90% confidence interval is built. Based on this, the CAT develops a range of what would be a fair share and where to categorize the different countries. The CAT values China’s share in mitigation efforts as highly insufficient. In comparison, the U.S.’s, India’s and the EU’s planned policies and targets are only considered insufficient for achieving a fair share target under the Paris Agreement (Climate Action Tracker, 2022).

Another equity metric is developed by the Climate Equity Monitor. The Climate Equity Monitor is the first initiative from the Global South that tracks equity in climate action for Annex 1 and Non-Annex 1 countries. The initiative calculates the fair share of the carbon budget by using the share of cumulative emissions based on the share in the global population for a contemporary base year (2019). The cumulative annual emissions of a country are calculated for the period from 1850 to 2019. Based on this, the Climate Equity Monitor calculates if a country has a carbon debt or carbon credit. This measure is calculated as the difference between cumulative emissions of a country and the country’s fair share of the global carbon budget already consumed. For China as a Non-Annex 1 country, they conclude that the country has a carbon credit of 122.4 Gt CO2eq. In comparison, India has a carbon credit of 337.6 Gt CO2eq while the US has a carbon debt of 445 Gt CO2eq, and Russia has a carbon debt of 125.44 Gt CO2eq (Climate Equity Monitor, 2022). Accordingly, if China kept emitting at its current rate, it would have used up its remaining carbon credit until 2031.

It is interesting that the Climate Action Tracker and the Climate Equity Monitor come to conclusions that can be interpreted differently. While the latter initiative only considers cumulative emissions allowances in relation to population size, the former’s assessment benchmarks climate targets and policies against a larger variety of equity metrics. The remaining carbon credit derived from the Climate Equity Monitor might be misleading to a certain degree, as it might suggest little urgency to act, especially when comparing the credit numbers to the debt numbers of other countries. The CAT’s assessment, while being methodically more sophisticated, better communicates the implications of current emission reduction targets and respective policies from an equity perspective.

Our analysis has the following limitations: We only consider cumulative emissions from 1850-2019, but the consideration of other time periods could also be conceivable. The problem of climate change caused by anthropogenic greenhouse gas emissions has only been known since the 1970s, and since the 1990s there has been a dedicated international process to address the problem. Against this background, an additional consideration of cumulative emissions in these time periods might be worthwhile. For a comprehensive assessment of China’s fair share, it would have also been interesting to discuss further equity metrics such as a ranking of consumption-based emissions. However, this was not possible for us, as our data only included consumption-based data for approx. 100 countries and crucially missing the US, making a comparison less meaningful.

\appendix
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
\renewcommand{\thesubsection}{\Alph{subsection}}
\newcommand{\subsectionbreak}{\clearpage\phantomsection}
\numberwithin{table}{subsection}

\normalsize
## Session Info (RStudio)

\footnotesize

```{r session-info, results='asis'}
toLatex(sessionInfo(), locale=F) 
```

\normalsize
\singlespacing
\listoffigures
\listoftables

\def\bibpreamble{All online resources were last accessed on 12 December 2022.}
\footnotesize

### 2022-12-12 r-report/Paper.tex
push

@@
 \newcommand{\Newrow}{\\}
-\AtBeginDocument{\pdfbookmark[section]{Deckblatt}{front}}
+\AtBeginDocument{\pdfbookmark[section]{Cover Page}{front}}
 \usepackage{booktabs}
@@
 \renewcommand{\harvardand}{\&}
+\renewcommand{\harvardurl}{\textbf{URL:} \url}
 \setcitestyle{authoryear,round,aysep={},notesep={: }}
+
+\nocite{R-rmarkdown,R-tidyverse,R-eurostat,R-WDI,R-plotly,R-imputeTS,R-kableExtra}
 
@@
 
-\nocite{R-rmarkdown,R-tidyverse,R-eurostat,R-WDI,R-plotly,R-imputeTS,R-kableExtra}
-\citet{WorldBank2022a} \citet{WorldBank2022b} \citet{Worldbank2022c}
-\citet{Giacomo2022}
+The development that the People's Republic of China has taken in recent
+decades is nothing short of remarkable. While the country, under the
+dictatorial leadership of Mao Zedong, was plagued by poverty and famine
+during the first three decades after its founding in 1949, Deng
+Xiaoping's policy of reform and opening started the country's economic
+boom in the late 1970s. Millions of Chinese have made the leap out of
+poverty since, and the country, which at the beginning of the 21st
+century was still considered the ``workbench of the world'', has now
+developed into an economic and technological superpower that is readying
+itself to overturn the global supremacy of the U.S..
+
+During the same period, China's emissions have risen rapidly. In 2004,
+the country surpassed the U.S. as the world's largest greenhouse gas
+emitter and is likely to retain that title for some time. In 2019, more
+than 25\% of all global greenhouse gas emissions came from China, more
+than the U.S. and (at the time still) EU-28 combined (see Figure 1). As
+a consequence of this development, China's emissions profile changed
+dramatically: While the agricultural sector still accounted for a large
+share of emissions in the early 1970s, its contribution has been only
+marginal in recent years. Figure 2 shows the large-scale
+industrialization of the country starting in the mid-1990s and the
+corresponding increase in emissions from the energy sector. More
+recently, transport sector emissions have picked up speed, likely
+reflecting the wealthy share of China's citizens spending more money on
+individual (fossil-fuel based) modes of transport.
+
+China's energy mix is still largely dominated by coal. In 2020, more
+than 60\% of the country's total energy supply stemmed from this fossil
+fuel. Renewables on the other hand only contributed 6.2\% to total
+energy supply (excluding biofuel and waste). Looking at just the
+electricity production, the numbers are a bit different: Here the
+renewable sources' share was approx. 28\% \citep{IEA2022}. However,
+China remains the country with the world's largest coal fleet and also
+the highest planned coal capacity additions. In 2021, the country
+started building 33 GW of additional coal-based power generation and
+consumed about five times as much coal as India, and nearly six times as
+much as the U.S. \citep{Green2022}.
+
+Chinese carbon emissions growth was predominantly driven by its rapid
+economic development, which in turn caused the energy sector to grow
+too. Since the year 2000, China's GDP per capita has more than
+quadrupled, while carbon emissions have more than tripled in the same
+period (see Figure 3). However, the growth of emissions has slowed in
+recent years, as energy intensity of GDP had started decreasing after
+the year 2005 and also carbon intensity of energy peaked in 2010 and has
+been slowly decreasing since. While for the first two decades of the
+21st century carbon emissions growth rates were closely resembling the
+growth rates of GDP per capita, since 2010 the two numbers have
+decoupled. China's immense expansion of renewable energy sources over
+the last years is likely an underlying driver of this trend, however, as
+we have seen, Chinese annual emissions remain very high at 14.2 GtCO2e
+in 2019.
+
+The question arises, how China plans to curb its emissions. At the
+United Nations General Assembly in 2020, Chinese President Xi Jinping
+announced the goal of Chinese carbon neutrality before 2060
+\citep{Jinping2020}. This was the first time China officially committed
+to a long-term emissions reductions goal \citep{CAT2022}. One year
+later, in November 2021, ahead of COP26, China submitted its updated NDC
+to the UNFCCC. Accordingly, the country plans to peak its carbon
+emissions before 2030, decrease the carbon intensity of GDP by over 65\%
+(relative to 2005), have around 25\% of non-fossil fuels in primary
+energy consumption by 2030, increase the forest stock volume by six
+billion cubic meters until 2030 and have 1,200 GW of wind and solar
+power capacity installed by the same year \citep{China2022}. Although
+some of these objectives are vague to some degree, and the emissions
+reduction target is only a relative goal, the ambitions China has set
+for itself are a marked improvement over the targets set out in the
+previous 2016 NDC. Additionally, it is important to note that these
+goals are unconditional and hence not relying on external climate
+finance. China has adopted numerous policies to support its
+international targets, such as the ``Working Guidance for Carbon Dioxide
+Peaking and Carbon Neutrality'' and the ``Action Plan for Carbon Dioxide
+Peaking Before 2030''. The former spells out a set of principles and
+sectoral goals to achieve carbon dioxide peaking and carbon neutrality,
+among them the need to exercise nationwide planning and the
+prioritization of conversing energy (Department of Resource Conservation
+and Environmental Protection, 2021a). The latter defines key tasks for
+driving the low-carbon energy transition or saving energy, carbon
+emission mitigation and efficiency improvement \citep{DRCEP2021b}. With
+its ``14th Five-Year Plan on Renewable Energy'', the country aims to
+further accelerate its renewable energy expansion. By 2025, 33\% of
+electricity ought to be supplied by renewable sources (18\% non-hydro),
+which could decrease annual carbon emissions by 2.6 gigatons
+\citep{Zhou2022}.
+
+Nonetheless, China's goals and policies are widely viewed as inadequate
+by various parties. The CAT for example projects that China is likely to
+comfortably overachieve its NDC targets without substantially increasing
+its current mitigation efforts. Hence, their overall rating of the
+country's goals and policies is ``insufficient''. If all countries were
+to pursue the same level of ambition as China, global warming would
+reach approx. 3°C. Therefore, China's current goals and policies leave
+significant room for further target-raising ambition. The CAT
+additionally concludes that China's contributions are also not
+sufficient to do its ``fair-share'' in fighting climate change and
+limiting global warming under the Paris Agreement \citep{CAT2022}.
+
+China itself assesses its responsibility for climate change mitigation
+measures very differently though. In its 2021 NDC update, China assigns
+responsibility for global warming to developed countries. It were their
+emissions that had caused the dramatic increase of GHGs in the
+atmosphere. China, on the other hand, was a developing country, thereby
+having the right to develop \citep{China2022}.
+
+This line of argument is as old as the UNFCCC itself. In 1992, at the
+first COP in Rio de Janeiro, where the parties agreed on the UNFCCC,
+they classified countries into two groups of ``Annex-I'' and ``non-Annex
+I'' countries, consisting of mostly developed and (at the time)
+developing countries respectively. At the same time the principle of
+common but differentiated responsibilities and respective capabilities
+(CBRD) was introduced. According to this principle, the industrialized
+nations would need to bear the main responsibility when it comes to
+emission reductions, while the ``non-Annex I'' countries would initially
+have no obligations to avoid emissions. This principle was also
+enshrined in the 1997 Kyoto Protocol. The 2015 Paris Agreement
+reaffirmed the CBRD principle, but, for the first time, brought all
+signatory countries together to undertake ambitious efforts to tackle
+climate change and adapt to its impacts \citep{UNFCCC2015}. However, it
+has caused long-standing debates, whether China should continue to be
+classified as a developing country, given its economic and emissions
+growth since the UNFCCC was adopted, or whether it has a greater
+responsibility in addressing climate change.
+
+With these developments in mind and following up on China's claim to be
+a developing country, we set out in this paper to discuss equity
+considerations for China, focusing on two research questions. First, we
+will investigate whether China, from an emissions perspective, can still
+be characterized as a developing nation. For this we compare China's
+Kaya identity with other developing and developed nations. Furthermore,
+we consider China's sectoral emissions trends and contrast them with
+those of (other) developing and developed nations, controlling for
+differences in population size and GDP. Secondly, we investigate China's
+claim of developed countries' being the driver of climate change, by
+calculating different measures of (historic) responsibility and assess
+the level of responsibility China bears in combatting climate change. We
+discuss these findings with regards to a projection of China's
+cumulative emissions.
+
+The remainder of this paper is structured as follows: In section 2 we
+provide an overview of our data and main assumptions, before analyzing
+China's self-characterization as a developing country in section 3.
+Section 4 compares different equity metrics for China and other big
+emitters and discusses China's role in addressing climate change against
+different scenarios of future Chinese cumulative emissions. In section 5
+we discuss our findings in light of other available assessments of
+China's role and conclude.
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-1-1.pdf}
+\caption{Figure 1}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{Figure 2}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{Figure 3}
+\end{figure}
 
@@
 
+Our project is data-driven in nature and relies heavily on the
+availability of various metrics on both greenhouse gas emissions and
+measures of (economic) development. Furthermore, there are key
+assumptions connected to our analysis that impact our findings. This
+section provides an overview of the data-sets we use, and makes our
+underlying assumptions about the data explicit.
+
 \hypertarget{used-data}{%
 \subsection{Used Data}\label{used-data}}
+
+In terms of data on GHG emissions we make use of the EDGAR database as
+the core of our analysis. It contains yearly emissions data on the major
+greenhouse gases by country and sector and makes them commensurable
+based on global warming potentials on a 100-year scale. The database and
+its development are a joint project of the European Commission Joint
+Research Center and the Netherlands Environmental Assessment Agency
+\citep{EC2022}.
+
+We supplemented this data set with data on LULUCF emissions from the
+national GHG inventory database and add them to the total GHG emissions.
+The data itself was sourced from annual GHG inventories for Annex I
+countries and gathered from recent communications, biennial update
+reports, REDD+ submissions and NDCs for Non-annex I countries
+\citep{Giacomo2022}.
+
+For consumption-based emissions of selected countries since 1990 we make
+use of an updated dataset from Peters et. al \citep[updated
+from][]{Peters2011}. Additionally, we rely on world bank data for GDP,
+GNI and population \citep{WorldBank2022d}. We further hand code
+variables for countries, specifically their membership to the EU 27 \&
+28 respectively, as well as their income classification according to the
+2019-word-bank-classification for gross national income per capita
+\citep{WorldBank2018}. Lastly two datasets were made available to us a)
+an inventory of CO2 emissions since 1750 and b) IEA data for energy
+consumption.
 
@@
 
+Regarding our main assumptions we limit our analysis to years until 2019
+as we believe that the pandemic heavily distorted prior trends and hit
+countries and their economies to varying extents, making any meaningful
+interpretation and comparison difficult. Our main assumption here is
+that the trends and developments up to 2019 are more meaningful
+indicators for developments in the years and decades to come, compared
+to the pandemic years.
+
+To make information accessible and to allow for comparisons across gases
+we choose to provide all information on multiple GHGs based on 100-year
+global warming potentials, as provided in our core database EDGAR.
+
 \hypertarget{analysis}{%
 \section{Analysis}\label{analysis}}
+
+TO BE DONE: Intro statement.
 
@@
 
+In the following, China's self-characterization as a developing country
+will be critically reviewed from an emissions perspective. For this, a
+definition of developed and developing countries will be developed. This
+is followed by a comparison of China's emissions development with the
+emissions development of other developed and developing nations by using
+a Kaya decomposition. As the distribution of emissions by sector is
+another way to distinguish between developing and developed countries,
+China's sectoral emissions are also compared to other countries. With
+this, we strive to find an answer to our first research question.
+
 \hypertarget{categorization-of-developed-and-developing-countries}{%
@@
 Countries}\label{categorization-of-developed-and-developing-countries}}
+
+To distinguish between developed and developing countries, different
+indicators can be considered for instance GDP per capita, the gross
+national income GNI per capita or the human development index (HDI).
+Furthermore, other indicators such as the level of education or
+democracy can be taken into account when determining whether a country
+is developed, developing or underdeveloped \citep{Kinnunen2019}.
+
+Our main data set, the EDGAR dataset, already provides a classification
+of countries in two groups -- developed and developing -- which we will
+use as a starting point. According to this, China is categorized as a
+developing country. However, we realized that a more granular
+categorization of countries might be helpful to answer our first
+research question. Especially since any type of self-categorization
+might be biased as countries stand to gain from underestimating their
+development in order to receive more aid and have less responsibilities
+in the UNFCCC process.
+
+Thus, we decided to use a second country classification scheme for
+comparison. Although a financial indicator might not completely
+summarize a country's level of development, we decided to use the GNI
+cut-offs as our main indicator of development. This is mainly because
+research finds that the GNI correlates with a number of accepted
+indicators of development outcomes \citep{Fantom2016}. Furthermore, the
+income classification is the standard classification in discussions on
+development. The World Bank, but also other international organizations
+and aid agencies, use this for analytical and operational purposes. The
+GNI is calculated in the following way:
+
+TO BE DONE FOrmula
+
+Thus, going forward we will also use the World Bank's Classification of
+Countries by income, which assigns countries into four different groups:
+high income, upper-middle income, lower-middle income, low income.
+Income is measured using the GNI per capita of the previous year in U.S.
+dollars using a three-year average exchange rate. The classification is
+updated each year. For our analysis, we are using the threshold valid as
+of July 2019, as our emissions analysis considers this year as the last
+year. The thresholds are as follows:
+
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{|l|l|}
+    \hline
+        \textbf{Group  } & \textbf{Thresholds July 2019 in USD  } \\ \hline
+        Low income   & $< 1,026$ \\ \hline
+        Lower-middle income   & $1,026 - 3,955$ \\ \hline
+        Upper-middle income  & $3,966 - 12,375$ \\ \hline
+        High income  & $> 12,375$ \\ \hline
+    \end{tabular}
+\end{table}
+
+According to the World Bank's classification, China is classified as an
+upper-middle income country since 2010 \citep{WorldBank2022d}.
+
+To make use of the more granular look at country groups in relation to
+our research question, we assume low- and lower-middle income countries
+to be more likely resembling developing nations and middle-upper- and
+high-income countries to be more likely resembling developed nations.
 
@@
 
+With a Kaya identity, one can identify the main driving forces of CO2
+emissions in a certain period. The Kaya identity expresses CO2 emissions
+(F) as a function of GDP (G), population (P) and energy (E):
+
+TO BE DONE FOrmula
+
+The term highlights the different components of the identity: G/P is GDP
+per capita, E/G is the energy intensity of GDP and F/E is the carbon
+intensity of energy \citep{Lamb2021}. By comparing Kaya identities of
+different regions, we can also discuss regional differences. Hence, we
+use the Kaya identity to discuss if the driving forces of emissions show
+similarities with developing or developed nations.
+
+Figure 4 displays China's and developing and developed countries' Kaya
+identities according to the IPCC classification in the Sixth Assessment
+Report from 2000 to 2019. In those years, China's GDP per capita was
+growing with a factor close to five, thereby being the strongest upward
+driver of emissions. GDP per capita increased almost in tandem with
+carbon emissions until 2010, in which a decoupling took place. Ever
+since, Chinese emission's growth rates have been much slower than those
+of GDP per capita. This decoupling is likely due to the decreasing
+energy intensity of GDP and carbon intensity of energy at the same time.
+The energy intensity is the main counteracting factor on Chinese
+emissions and decreased constantly since 2005. The decreasing trend
+seemed to have already started in 2000 but had rebounded before 2005,
+which can be traced back to 2001, when China joined the WTO
+\citep{Zheng2020}. However, since 2010 the decrease has been
+significant, hence driving the reduction of overall emissions growth
+rate. Furthermore, one can see that carbon intensity of energy decreased
+since 2010 meaning that the amount of CO2 per unit of energy is
+decreasing. Nevertheless, the relationship remains a positive one. The
+decline of both the energy intensity and carbon intensity is likely due
+to economic efficiency improvements. Additionally, carbon intensity
+further declined because of increasing capacity additions of renewable
+energies (changes in the fossil share) and the reduced emission
+intensity of fossil fuels (changes in the fossil intensity, fuel switch)
+\citep{Zheng2020, Peters2017}. Population changes only played a minor
+role but can be considered as a persistent upward driver of emissions.
+
+Comparing China's Kaya identity to the decomposition of the development
+of CO2 emissions of developing and developed countries does not provide
+a clear result on whether China can be considered a developing or
+developed nation. In general, economic growth is the main driver of CO2
+emissions, both in developed and developing nations. However, GDP per
+capita growth is much larger and hence closer to China's figures in
+developing nations as they show a greater growth potential. Overall
+carbon emissions are decreasing in developed nations while they are
+increasing in developing nations and China. This supports the notion of
+China being a developing country relying on emissions driven growth. On
+the other hand, China's energy and carbon intensity are decreasing as it
+is the case for developed countries. The population's development of
+China also more closely resembles the trend of developed countries than
+those of developing countries. To sum up, this classification does not
+clearly indicate whether China is a developing or developed country. As
+mentioned above, comparing China to a more granular classification of
+countries might be worthwhile, as the EDGAR dataset for example
+considers Saudi-Arabia, a country with one of the highest GDP per capita
+as a developing nation.
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-4-1.pdf}
+\caption{Figure 4}
+\end{figure}
+
+Thus, in the next steps, the World Bank's Income Classification Scheme
+will be used for comparison (Figure 5). In high-income countries, GDP
+per capita and population are increasing only at low levels (by roughly
+the factor 0.5 and 0.2 respectively). Carbon intensity and energy
+intensity are decreasing, keeping carbon emissions down. The carbon
+intensity is decreasing because of two factors: the fossil intensity and
+the fossil share. In contrast, in low-income countries, the growth of
+CO2 emissions is exceeding the growth of GDP per capita, both rising by
+a factor of 2.8 and 5 respectively over the observed time span. This is
+driven by a high and increasing carbon intensity. Furthermore,
+population growth plays an important role in this group, and can be
+considered a further driving factor of CO2 emissions. The only
+contrasting factor is the decreasing energy intensity. Comparing both
+groups of countries to China, one can resume that China's development
+does not fit in either of the groups perfectly. Like before China's Kaya
+decomposition shares similar characteristics as both groups: The small
+population growth resembles the trend of high-income countries, the
+dramatically decreasing energy resembles the trend of low-income
+countries. Considering lower-middle income countries, they seem to show
+upwards trends in any of the indicators except for energy intensity. In
+comparison, in upper-middle income countries carbon emissions and GDP
+per capita develop in tandem, while carbon intensity and energy
+intensity only fluctuate around zero in the years from 2000 to 2019.
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-5-1.pdf}
+\caption{Figure 5}
+\end{figure}
+
+To conclude, China seems to be an exception considering the driving
+forces of emissions and thus cannot be assigned uniquely to any of the
+studied group of countries. This is especially due to the exceptionally
+high GDP growth which only recently decoupled from carbon emissions. In
+terms of GDP growth rates and carbon emission growth, China can be
+considered a developing nation as they base their GDP growth on growing
+carbon emissions. However, the carbon and energy intensity that keep CO2
+emissions down, show that China is already getting more efficient in its
+production and that it has the capacity to invest in renewable energy
+source. Considering only those two indicators, China can be better
+compared to developed countries. Thus, it seems that China has a
+responsibility to put forward this trend of efficiency gains in order to
+decouple economic growth and emissions even more. To examine the status
+of China in more depth, China's sectoral trends will be compared to the
+two discussed classification schemes in the following. This can provide
+further information on China's classification, since developing and
+developed nations usually generate wealth in different economic sectors.
+
 \hypertarget{comparison-of-chinas-sector-trends}{%
@@
 
+In this part, sector trends of different groups of countries will be
+considered using the same two categories of country groups as before. We
+take into account five sectors: energy, industry, transport, AFOLU
+(which in the EDGAR database only includes agricultural emissions), and
+buildings. China's relative GHG emissions by sector are presented in a
+stacked bar plot in Figure 6 \& 7. Most of China's emissions in 2019
+came from the energy and industry sector with 44\% and 38\%
+respectively. Only smaller shares are attributable to transport (6\%),
+buildings (5\%) and AFOLU (6\%).
+
+In developed countries (according to the EDGAR classification), energy
+and industry still account for the majority of emissions (58\% in
+total), but transport emissions play a much larger role (21\%) of the
+GHG emissions than in China. This high share of transport emissions can
+be accounted to the high use of private cars in developed economies. For
+instance, the EU road transport accounts for 77\% of GHG emissions in
+the transport sector in 2020 \citep{EEA2022}. AFOLU emissions and
+emissions from buildings each account for roughly 10\% of the total GHG
+emissions.\\
+In contrast, in developing nations, the share of AFOLU emissions is much
+larger (21\%). The high share is typically associated with the expansion
+of agriculture into carbon-dense tropical forests, but also the lack of
+economic development of other sectors. The share of transport, however,
+is much lower than in developed countries as individual transport is not
+that widely spread. The relative emissions in energy and industry are
+comparable to those in developed countries as developing countries are
+rapidly growing to fulfil their own and the developed countries'
+consumption needs. However, absolute emissions levels are much lower.
+
+Again, China's split of emissions does not fit in either of the two
+categories. On the one hand, China's share of emissions coming from the
+AFOLU sector is relatively small resembling developed country
+characteristics. On the other hand, their emissions from transport
+sector are small as well. This is due to the immense share of emissions
+stemming from industry and energy, which reduces the share of emissions
+in the other sectors.
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-6-1.pdf}
+\caption{Figure 6}
+\end{figure}
+
+As before, to get a more granular view on the split of emissions by
+sector, the World Bank's classification will be consulted (Figure 7).
+
+In this classification, differences between high-income and low-income
+countries are very pronounced. While in high-income countries a major
+share of emissions resulted from energy systems (37\%) in 2019, the
+share of emissions from energy only accounts for 9\% of all GHG
+emissions in low-income countries. This highlights an energy system
+largely depending on fossil fuels in high-income countries on the one
+hand, and the lack thereof in low-income countries on the other hand.
+The differences are also immense considering the transport sector. In
+high-income nations, 20\% of the GHG emissions stem from transport,
+while in low-income countries, the share is only 7\%. However, the
+biggest differences are the AFOLU emissions. High-income countries have
+a share of 9\% for AFOLU emissions while in low-income countries this
+sector accounts for 57\% of emissions. The reasons for these differences
+were discussed above.
+
+The emissions by sector for lower-middle and upper-middle income
+countries are more similar, the only difference is that the share of
+AFOLU is larger in lower-middle income countries and the share of
+transport is larger for upper-middle income countries, indicating
+further progress on the typical developing path of the latter country
+group.
+
+Again, China does not really fit into either of the categories due to
+its very high share of emissions stemming from the energy and industry
+sector. China's relative emissions from these two sectors are much
+larger than in any of the other groups studied.
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{Figure 7}
+\end{figure}
+
+As the stacked bar plot can only provide a snapshot in time and relative
+emissions only tell a limited story, we will in a next step compare
+China's per capita emissions by sector over time from 1970 to 2019 to
+those of our four income determined country groups (Figure 8).
+
+Comparing trends is particularly helpful, as emissions from the energy
+and industry sector in China are so large, that it makes any comparison
+of the remaining sectors with the potential peers very difficult.
+
+China's AFOLU emissions per capita are relatively low and decreasing
+over time, similar to the emissions in lower-middle income countries in
+this sector. The AFOLU emissions per capita of high income and
+upper-middle income countries are large because a relatively high
+agricultural output spread over relatively small populations. In the
+building sector, Chinese emissions per capita are relatively low
+compared to high-income countries and rather on the same level as
+upper-middle income countries. The per-capita emissions of the building
+sector are high in richer countries as people require more floor space
+per capita compared to lower-income countries. For transport, China's
+emissions stayed on a low level until 2000 and then increased at high
+speed. Now, they are comparable to per capita emissions of
+upper-middle-income countries.
+
+Considering the three sectors mentioned above, China seems to resemble
+more the emissions per capita characteristics of lower-middle or
+upper-middle income countries, however this is different for the energy
+and industry sectors. In the energy sector, China's emissions per capita
+increased up to roughly 4 tCO2eq in 2019. This is much higher than for
+upper-middle income countries, in which per capita emissions stayed
+relatively constant at 3 tCO2eq in 2019. In high-income countries, the
+per capita emissions from energy are still higher (5 tCO2eq) in 2019
+than in China, however, one can see a downward trend there. Thus, one
+could argue that China can soon be compared to a high-income country
+regarding its per capita energy system emissions. The same holds for the
+industry sector, where this development is even more pronounced.
+Emissions per capita in the industry sector in China increased massively
+in the 2000s and are now at a plateau of 4 tCO2eq annually. The per
+capita emissions of high-income countries in the industry sector in
+contrast have decreased since the 1970s and are now at 3 tCO2eq. In the
+industry China has thus already surpassed per capita emissions levels of
+high-income countries and has the highest value among the five studied
+panels in this sector.
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-8-1.pdf}
+\caption{Figure 8}
+\end{figure}
+
 \hypertarget{discussion}{%
 \subsubsection{Discussion}\label{discussion}}
+
+The prior analysis has shown that clearly classifying China as either a
+developed or a developing from an emissions perspective remains
+difficult.
+
+However, what this analysis has clearly shown, is that the simple
+self-characterization of China as a developing country, that is mirrored
+by Sixth assessment report of the IPCC, does not do justice to the
+drastic economic and emissions development China has witnessed in the
+last decades. As the analysis has shown, China clearly exhibits certain
+emission characteristics of developed countries in some sectors like
+industry and energy systems. When it comes to agricultural per capita
+emissions trends it is comparable to lower-income countries. Maybe most
+importantly, in the industry sector it has the highest per capita
+emissions of any of the candidates that were up for comparison.
+
+What this analysis has undoubtedly confirmed is the realization that
+China is a special case in every respect. China's unique economic
+development, which has led to a five-fold increase in GDP per capita
+over the past two decades, saw the country develop an energy and
+industrial system that together accounts for 82\% of the country's total
+emissions, a share 20\% higher than that of high-income countries.
+
+Nevertheless, one needs to consider that development is not equally
+distributed in China. The rural population has benefited significantly
+less from the economic development than the urban population (East-West
+divide) \citep{Knight2004}. However, the argument that one still has the
+right to predominantly emissions-based development (as in 1992) is no
+longer in line with China's current status as the world's biggest
+emitter. Hence, China's NDC's storyline, which seeks the main
+responsibility for climate change in developed nations, is too
+undercomplex and does not do justice to the evolved realities.
+
+To further investigate this issue, in the next we will predict the
+future development of emissions of China and other countries and further
+consider different equity metrics.
 
@@
 
+The following chapter discusses China's equitable share in climate
+change mitigation. In order to answer the research question, we will
+first discuss the future development of China's emissions, to determine
+when China will become the biggest cumulative emitter. For this, we
+consider multiple development pathways of China in terms of emissions
+and discuss China's cumulative emissions in comparison to other
+countries. Moreover, we will present different rankings of absolute
+emissions, per capita emissions, GDP and GDP per capita, cumulative
+emissions and consumption-based CO2 emissions to discuss China's
+responsibility from different perspectives.
+
 \hypertarget{future-development-of-chinas-emissions}{%
@@
 
+The first equity metric we consider is cumulative emissions, as China
+claims historic developed countries' emissions being the main driver of
+climate change. Looking at cumulative emissions from 1750 until 2019,
+China is on 3 rd position, only behind the U.S. and the EU-27. According
+to this, in 2019 China would already have the 3rd-largest responsibility
+to reduce emissions, since it has historically emitted a total of 12.4\%
+of all greenhouse gases. This is in direct contrast to the country's
+claim to be less responsible for the warming climate.
+
+Importantly, if China continues its emissions pathway, it will become
+the largest cumulative emitter at some point. In order to estimate when
+China will move into first place, we have modeled expected emission
+trends for China as well as for the EU and the U.S. Our modelling is
+based on the following assumptions:
+
+First, for simplicity, we assume that China will reduce not only CO2
+emissions, as communicated internationally, but all GHG emissions to
+zero. As we have seen in section 3, Chinese emissions trends vary
+strongly across sectors. Therefore, we have modelled each sector's
+future emissions pathway following different assumptions. In general, we
+assume a constantly declining growth rate of emissions in each sector
+until a peak year starting with the 2018 to 2019 growth factor. After
+the peak we consider an s-curve emissions reduction for the following
+years until zero emissions are reached, as China might first use the
+simple levers to reduce emissions fast and then needs to work on
+emissions which are difficult to bring down.
+
+As emissions in the AFOLU sector have already been decreasing in China,
+we expect a relative flat emissions level until 2025, followed by a
+decrease until zero emissions are reached in 2060. Buildings are assumed
+to peak emissions in 2030 and are at zero in 2060. The energy systems
+sector is expected to peak the earliest, in 2028, due to the continued
+heavy roll-out of renewable energy sources in China and the experiences
+from other countries decarbonization journeys. Complete decarbonization
+is then assumed to be reached by 2055. We assume the industry sector to
+peak by 2030 and reach complete decarbonization by 2065. As transport is
+the fastest growing sector of Chinese emissions, we assume this trend to
+continue (but slowed down) until 2040, and complete decarbonization in
+2065.
+
+In modeling the development of emissions for the EU-27 and the U.S., we
+are guided by data from the PBL Netherlands Environmental Agency
+\citep{PBL2022}. For simplicity we do not differentiate by sector but
+assume a linear decrease in annual emissions up to the projected
+emissions value for 2030 in both the U.S. and the EU-27. Thereafter, we
+also use an s-shaped reduction curve to achieve zero emissions by 2050.
+
+The resulting sectoral emissions pathways for each country/region are
+depicted in figure xx. The resulting cumulative emissions forecasts for
+the three countries/blocks are shown in figure xx. Accordingly, China
+will pass the EU-27 in cumulative GHG emissions in 2027 and is projected
+to pass the U.S. in 2032 . Afterwards it will be the largest cumulative
+emitter.
+
+These projections hold even when modelling each sector according to the
+Chinese NDC (assuming peak years of 2030 and zero emissions by 2060). In
+the NDC-scenario China will surpass the EU and US respectively in the
+same years as modeled in our main scenarios, but at different emission
+levels -- 452.4 GtCO2eq (main scenario) 451.8 GtCO2eq (NDC-scenario).
+When projecting only CO2 emission developments1 China will surpass the
+EU in 2031 and the US in 2038 according to both scenarios.
+
+This analysis shows that maintaining targets that are ambitious in
+absolute terms but relatively easy to achieve compared to China's size
+and economic power, have already put China at the forefront of global
+responsibility for climate change. From a cumulative emissions
+perspective, China definitely has the same if not larger GHG reduction
+obligations as many developed countries, especially when considering
+that a majority of China's emissions were emitted after the problem of
+climate change has made it on top of the global policy agenda. Moreover,
+the statement of the Chinese NDC that climate change is mainly caused by
+others is not tenable.
+
 \begin{figure}
 \centering
-\includegraphics{Paper_files/figure-latex/unnamed-chunk-1-1.pdf}
-\caption{Label TEst}
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-9-1.pdf}
+\caption{Figure 9}
 \end{figure}
+
+However, cumulative emissions, while easily understood, are not the only
+conceivable equity metric to consider when attempting to assess a
+country's fair share in responding to climate change. Therefore, in the
+following sub-section we investigate other equity metrics.
 
@@
 
-\hypertarget{discussion-1}{%
-\subsubsection{Discussion}\label{discussion-1}}
+This chapter presents different rankings which can shed light on the
+question of China's responsibility to mitigate climate change from
+different angles. The following rankings always display the top 10
+countries (or in case of the EU regions) in the respective category.
+Furthermore, other important countries are added for comparison as well
+as a category named ``Other'' which summarizes the share of all
+remaining countries. The EU-27 is mentioned as a point of reference, but
+emissions of the separate countries are displayed in the ranking or
+summarized in the ``Other'' category. Every graph also provides
+reference points for the rank position where cumulative 50 \% of global
+GDP, population and emissions are surpassed.
 
-\hypertarget{discussion-and-conclusion}{%
-\section{Discussion and Conclusion}\label{discussion-and-conclusion}}
+First, we consider China's responsibility based on absolute emissions in
+the year 2019 (Figure X). In the ranking, China ranks on first place
+with absolute emissions of 14,219.37 Mt CO2 eq. This is more than double
+of the U.S. emissions (6,266.8 Mt CO2 eq) and also close to the
+emissions of all other countries that do not belong to the group of the
+top 10 emitters combined (14,075.12 Mt CO2 eq). Together with the U.S.,
+India and Russia, China makes up for 50\% of global emissions, but these
+four countries do not produce half of the global GDP, nor do they
+represent half of the world's population. This highlights that the
+responsibility of these four countries to drastically reduce emissions
+is high. Considering that China is producing more than double the
+emissions of the U.S., China has by far the highest responsibility to
+mitigate climate change from a current absolute emissions perspective.
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{Figure 10}
+\end{figure}
+
+Next, we consider emissions per capita (Figure x). This is important as
+China is the country with the biggest population worldwide of approx.
+1.4 billion people \citep{WorldBank2022c}. Looking at this ranking, it
+is important to consider that the top emitters according to per capita
+emissions are relatively small countries with low absolute emissions but
+also small populations. Thus, when it comes to reducing absolute
+emissions and fighting climate change, they can only play a minor role.
+China interestingly ranks on place 43 with roughly 10t CO2 eq / capita,
+before EU-27 but behind the U.S. (Ranking: 17). According to this equity
+metric, China's fair share to mitigate climate change from this
+perspective should be located between the share of these two
+countries/groups of countries.
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{Figure 11}
+\end{figure}
+
+Considering GDP and GDP per capita refers to the capacity of acting on
+climate change, following the assumption that richer countries have more
+resources available to fight climate change. As Figure XX shows, China
+had the highest GDP of all countries in 2019, with USD 22.49 trillion.
+Based on this, China would theoretically have to make the greatest
+conribution to reduce emissions. Absolute GDP, however, is limited in
+telling us about a country's actual capacity because it ignores
+population size. Therefore, considering GDP per capita might be more
+worthwhile. Here China only ranks 81st place in the world. Therefore,
+China's responsibility is relatively low from the GDP per capita
+perspective. In comparison, the U.S. rank on place 11. Countries that
+are in the top 10 emitters are often relatively small countries deriving
+their wealth from natural resources. Hence, they have a high
+responsibility to mitigate climate change as they have the ability to
+pay for climate change mitigation measures. However, their absolute
+emissions are relatively small and thus an ambitious reduction might not
+make a huge difference for achieving climate targets. Thus, one should
+consider that these countries should specifically contribute by
+providing financial aid to mitigate emissions elsewhere.
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{Figure 12}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{Figure 13}
+\end{figure}
+
+\hypertarget{discussion-tbd}{%
+\subsubsection{Discussion TBD}\label{discussion-tbd}}
+
+To sum up, China has a very high responsibility to mitigate climate
+change, even the highest responsibility of all countries when
+considering some of the discussed equity metrics. Based on our
+calculations, China is likely surpass the EU well before 2030 and the US
+shortly after in 2032 in terms of cumulative emissions over all GHGs
+from 1850 to 2019 and a modeling of emissions thereafter. The difference
+in emissions from all GHGs to CO2 emissions highlights the importance to
+extend the frame of historic respon
+
+Therefore, China now has a major responsibility to reduce emissions
+which is reinforced when considering that the country's massive
+emissions growth only started after the adoption of the Kyoto Protocol
+in 1997, at a time when the consequences of climate change were already
+being heavily discussed.
+
+However, we also need to consider that China only ranks on 81st. and
+43rd place considering their GDP per capita and their emissions per
+capita, respectively. This diminishes China's responsibility to some
+extent, showing that the global community needs to grant space for
+economic development to be fair. However, this economic development
+should ideally be decoupled from a growth in emissions. If we look at
+the per capita emissions of the countries that rank first, we see that
+these are mostly very small and, from the perspective of absolute
+emissions, less important countries. Although these countries might have
+a high ability to pay from a per capita perspective, their overall
+economic power is not high. The opposite is true for China. China ranks
+first place in absolute emissions and GDP in 2019 with a great distance
+to the following places.
+
+Thus, China has one of the greatest responsibilities to reduce emissions
+from a historic emissions, current emissions and economic capacity
+perspective.
+
+\hypertarget{discussion-and-conclusion-tbd}{%
+\section{Discussion and Conclusion
+TBD}\label{discussion-and-conclusion-tbd}}
+
+In our analysis, we were striving to answer two research questions,
+namely if China can be considered a developing country and what China's
+fair share in climate change mitigation should be.
+
+Regarding out first research question, we find that China cannot be
+easily classified as a developed or developing country. This is due to
+the unique economic growth (China's GDP per capita quintupled in the
+last 20 years), which went hand in hand with very high energy and
+industrial sectors' emissions. Comparing these to other developed
+countries, one can see that China clearly exhibits these countries'
+characteristics in term of sectoral emissions. However, China's
+agricultural per capita emissions trends are more comparable to
+lower-income countries.
+
+Our analysis of different equity metrics for the second research
+question has shown that China not only has a huge responsibility to curb
+emissions, but also the financial capability to do so. The country is
+the world's largest emitter in annual and cumulative terms (based on our
+data) and has the highest GDP of all countries. While it is important to
+acknowledge further room for development, one cannot disregard the fact
+that without significant emission reductions from China, any attempt to
+stay within the temperature limits of the Paris Agreement is sure to
+fail.
+
+Hence, we believe that China's fair share is much higher than what they
+currently plan to do. Together with the EU-27 and the U.S., China should
+bear the highest responsibility for climate change mitigation. Its
+self-classification as a developing country is clearly politically
+motivated, to not give in to the demands of having to do more. At the
+same time, the political leadership in Beijing can present itself as a
+top student in the international community by effortlessly surpassing
+its own goals, as it is expected by different observers \citep{CAT2022}.
+
+In the following, our analysis will be contrasted with two other
+assessments of China's fair share -- the assessment by the Climate
+Action Tracker and by the Climate Equity Monitor.
+
+The CAT evaluates the fair share of a country based on assessments in
+the literature. The results of the literature are categorized using
+seven equity indicators ranging around considerations of responsibility,
+capability, cost-effectiveness and equality, which are weighted equally
+in the analysis. All results of the evaluated studies are then depicted
+on a scale for each category and a 90\% confidence interval is built.
+Based on this, the CAT develops a range of what would be a fair share
+and where to categorize the different countries. The CAT values China's
+share in mitigation efforts as highly insufficient. In comparison, the
+U.S.'s, India's and the EU's planned policies and targets are only
+considered insufficient for achieving a fair share target under the
+Paris Agreement \citep{CAT2022}.
+
+Another equity metric is developed by the Climate Equity Monitor. The
+Climate Equity Monitor is the first initiative from the Global South
+that tracks equity in climate action for Annex 1 and Non-Annex 1
+countries. The initiative calculates the fair share of the carbon budget
+by using the share of cumulative emissions based on the share in the
+global population for a contemporary base year (2019). The cumulative
+annual emissions of a country are calculated for the period from 1850 to
+2019. Based on this, the Climate Equity Monitor calculates if a country
+has a carbon debt or carbon credit. This measure is calculated as the
+difference between cumulative emissions of a country and the country's
+fair share of the global carbon budget already consumed. For China as a
+Non-Annex 1 country, they conclude that the country has a carbon credit
+of 122.4 Gt CO2eq. In comparison, India has a carbon credit of 337.6 Gt
+CO2eq while the US has a carbon debt of 445 Gt CO2eq, and Russia has a
+carbon debt of 125.44 Gt CO2eq \citep{CEM2022}. Accordingly, if China
+kept emitting at its current rate, it would have used up its remaining
+carbon credit until 2031.
+
+It is interesting that the Climate Action Tracker and the Climate Equity
+Monitor come to conclusions that can be interpreted differently. While
+the latter initiative only considers cumulative emissions allowances in
+relation to population size, the former's assessment benchmarks climate
+targets and policies against a larger variety of equity metrics. The
+remaining carbon credit derived from the Climate Equity Monitor might be
+misleading to a certain degree, as it might suggest little urgency to
+act, especially when comparing the credit numbers to the debt numbers of
+other countries. The CAT's assessment, while being methodically more
+sophisticated, better communicates the implications of current emission
+reduction targets and respective policies from an equity perspective.
+
+Our analysis has the following limitations: We only consider cumulative
+emissions from 1850-2019, but the consideration of other time periods
+could also be conceivable. The problem of climate change caused by
+anthropogenic greenhouse gas emissions has only been known since the
+1970s, and since the 1990s there has been a dedicated international
+process to address the problem. Against this background, an additional
+consideration of cumulative emissions in these time periods might be
+worthwhile. For a comprehensive assessment of China's fair share, it
+would have also been interesting to discuss further equity metrics such
+as a ranking of consumption-based emissions. However, this was not
+possible for us, as our data only included consumption-based data for
+approx. 100 countries and crucially missing the US, making a comparison
+less meaningful.
 
@@
 
-  \bibliography{anna.bib,fabian.bib,packages.bib}
+  \bibliography{packages.bib}
 

### 2022-12-12 r-imports/init.R
addedplot 1

@@ -48,7 +48,7 @@ theme_ghg = function(){
   
   theme_minimal() %+replace%    #replace elements we want to change
     
-    theme(
+    #theme(plot.title =element_blank()
       
       # #grid elements
       # panel.grid.major = element_blank(),    #strip major gridlines

### 2022-12-12 r-plots/plot_single_polluters_stacked_rel.R

@@ -1,10 +1,14 @@
 OUT = PDATA$data_rel %>% 
   ggplot(aes(x=year,y=GAS_s_perc,fill=region)) +
   geom_area(color="#636363") +
+  geom_vline(xintercept= 2004, linetype="dotted",color = "red")+
   theme_bw() +
   scale_fill_brewer(palette="Set2") +
   ylab(GAS %.% " Emissions, %") +
   theme_ghg()+
   theme(axis.title.x=element_blank()) +
+  guides(fill = guide_legend("Region") )+
   ggtitle("Relative Emissions of the Top- 5 Polluters " %.% YEAR_L %.% "-" %.% YEAR_U)
 if(DIRECT_PLOTTING) plot(OUT)
+  
+

### 2022-12-12 r-report/Paper.Rmd
Plot 2

@@
 bibliography:
-  - anna.bib
-  - fabian.bib
+#  - anna.bib
+#  - fabian.bib
   - packages.bib
@@
   - \newcommand{\Newrow}{\\}
-  - \AtBeginDocument{\pdfbookmark[section]{Deckblatt}{front}}
+  - \AtBeginDocument{\pdfbookmark[section]{Cover Page}{front}}
 ---
@@
 options(knitr.kable.NA = '',knitr.table.format = "latex")
-knitr::read_chunk('r-report/Paper.R')
+#knitr::read_chunk('r-report/Paper.R')
 library(kableExtra)
@@
 ```{r setup-ex}
+source('r-imports/init.R')
+source('r-analysis/meta.R')
 ```
@@
 \renewcommand{\harvardand}{\&}
+\renewcommand{\harvardurl}{\textbf{URL:} \url}
 \setcitestyle{authoryear,round,aysep={},notesep={: }}
+\nocite{R-rmarkdown,R-tidyverse,R-eurostat,R-WDI,R-plotly,R-imputeTS,R-kableExtra}
 
@@
 
-\nocite{R-rmarkdown,R-tidyverse,R-eurostat,R-WDI,R-plotly,R-imputeTS,R-kableExtra}
-@WorldBank2022a @WorldBank2022b @Worldbank2022c @Giacomo2022
+The development that the People's Republic of China has taken in recent decades is nothing short of remarkable.
+While the country, under the dictatorial leadership of Mao Zedong, was plagued by poverty and famine during the first three decades after its founding in 1949, Deng Xiaoping's policy of reform and opening started the country's economic boom in the late 1970s.
+Millions of Chinese have made the leap out of poverty since, and the country, which at the beginning of the 21st century was still considered the "workbench of the world", has now developed into an economic and technological superpower that is readying itself to overturn the global supremacy of the U.S..
 
-# Data & Assumptions
+During the same period, China's emissions have risen rapidly.
+In 2004, the country surpassed the U.S.
+as the world's largest greenhouse gas emitter and is likely to retain that title for some time.
+In 2019, more than 25% of all global greenhouse gas emissions came from China, more than the U.S.
+and (at the time still) EU-28 combined (see Figure 1).
+As a consequence of this development, China's emissions profile changed dramatically: While the agricultural sector still accounted for a large share of emissions in the early 1970s, its contribution has been only marginal in recent years.
+Figure 2 shows the large-scale industrialization of the country starting in the mid-1990s and the corresponding increase in emissions from the energy sector.
+More recently, transport sector emissions have picked up speed, likely reflecting the wealthy share of China’s citizens spending more money on individual (fossil-fuel based) modes of transport.
 
-## Used Data
+China’s energy mix is still largely dominated by coal.
+In 2020, more than 60% of the country’s total energy supply stemmed from this fossil fuel.
+Renewables on the other hand only contributed 6.2% to total energy supply (excluding biofuel and waste).
+Looking at just the electricity production, the numbers are a bit different: Here the renewable sources’ share was approx.
+28% [@IEA2022].
+However, China remains the country with the world’s largest coal fleet and also the highest planned coal capacity additions.
+In 2021, the country started building 33 GW of additional coal-based power generation and consumed about five times as much coal as India, and nearly six times as much as the U.S.
+[@Green2022].
 
-## General Assumptions
+Chinese carbon emissions growth was predominantly driven by its rapid economic development, which in turn caused the energy sector to grow too.
+Since the year 2000, China's GDP per capita has more than quadrupled, while carbon emissions have more than tripled in the same period (see Figure 3).
+However, the growth of emissions has slowed in recent years, as energy intensity of GDP had started decreasing after the year 2005 and also carbon intensity of energy peaked in 2010 and has been slowly decreasing since.
+While for the first two decades of the 21st century carbon emissions growth rates were closely resembling the growth rates of GDP per capita, since 2010 the two numbers have decoupled.
+China’s immense expansion of renewable energy sources over the last years is likely an underlying driver of this trend, however, as we have seen, Chinese annual emissions remain very high at 14.2 GtCO2e in 2019.
 
-# Analysis
+The question arises, how China plans to curb its emissions.
+At the United Nations General Assembly in 2020, Chinese President Xi Jinping announced the goal of Chinese carbon neutrality before 2060 [@Jinping2020].
+This was the first time China officially committed to a long-term emissions reductions goal [@CAT2022].
+One year later, in November 2021, ahead of COP26, China submitted its updated NDC to the UNFCCC.
+Accordingly, the country plans to peak its carbon emissions before 2030, decrease the carbon intensity of GDP by over 65% (relative to 2005), have around 25% of non-fossil fuels in primary energy consumption by 2030, increase the forest stock volume by six billion cubic meters until 2030 and have 1,200 GW of wind and solar power capacity installed by the same year [@China2022].
+Although some of these objectives are vague to some degree, and the emissions reduction target is only a relative goal, the ambitions China has set for itself are a marked improvement over the targets set out in the previous 2016 NDC.
+Additionally, it is important to note that these goals are unconditional and hence not relying on external climate finance.
+China has adopted numerous policies to support its international targets, such as the “Working Guidance for Carbon Dioxide Peaking and Carbon Neutrality” and the “Action Plan for Carbon Dioxide Peaking Before 2030”.
+The former spells out a set of principles and sectoral goals to achieve carbon dioxide peaking and carbon neutrality, among them the need to exercise nationwide planning and the prioritization of conversing energy (Department of Resource Conservation and Environmental Protection, 2021a).
+The latter defines key tasks for driving the low-carbon energy transition or saving energy, carbon emission mitigation and efficiency improvement [@DRCEP2021b].
+With its “14th Five-Year Plan on Renewable Energy”, the country aims to further accelerate its renewable energy expansion.
+By 2025, 33% of electricity ought to be supplied by renewable sources (18% non-hydro), which could decrease annual carbon emissions by 2.6 gigatons [@Zhou2022].
 
-## China’s Self-Characterization as a Developing Country
-### Categorization of Developed and Developing Countries
-### Comparison of Kaya Identities 
-### Comparison of China’s Sector Trends
-### Discussion
+Nonetheless, China's goals and policies are widely viewed as inadequate by various parties.
+The CAT for example projects that China is likely to comfortably overachieve its NDC targets without substantially increasing its current mitigation efforts.
+Hence, their overall rating of the country’s goals and policies is “insufficient”.
+If all countries were to pursue the same level of ambition as China, global warming would reach approx.
+3°C.
+Therefore, China’s current goals and policies leave significant room for further target-raising ambition.
+The CAT additionally concludes that China’s contributions are also not sufficient to do its “fair-share” in fighting climate change and limiting global warming under the Paris Agreement [@CAT2022].
 
-## China’s Equitable Share in Climate Change Mitigation
-### Future Development of China’s Emissions
+China itself assesses its responsibility for climate change mitigation measures very differently though.
+In its 2021 NDC update, China assigns responsibility for global warming to developed countries.
+It were their emissions that had caused the dramatic increase of GHGs in the atmosphere.
+China, on the other hand, was a developing country, thereby having the right to develop [@China2022].
 
-```{r,fig.cap="Label TEst"}
+This line of argument is as old as the UNFCCC itself.
+In 1992, at the first COP in Rio de Janeiro, where the parties agreed on the UNFCCC, they classified countries into two groups of “Annex-I” and “non-Annex I” countries, consisting of mostly developed and (at the time) developing countries respectively.
+At the same time the principle of common but differentiated responsibilities and respective capabilities (CBRD) was introduced.
+According to this principle, the industrialized nations would need to bear the main responsibility when it comes to emission reductions, while the "non-Annex I" countries would initially have no obligations to avoid emissions.
+This principle was also enshrined in the 1997 Kyoto Protocol.
+The 2015 Paris Agreement reaffirmed the CBRD principle, but, for the first time, brought all signatory countries together to undertake ambitious efforts to tackle climate change and adapt to its impacts [@UNFCCC2015].
+However, it has caused long-standing debates, whether China should continue to be classified as a developing country, given its economic and emissions growth since the UNFCCC was adopted, or whether it has a greater responsibility in addressing climate change.
+
+With these developments in mind and following up on China’s claim to be a developing country, we set out in this paper to discuss equity considerations for China, focusing on two research questions.
+First, we will investigate whether China, from an emissions perspective, can still be characterized as a developing nation.
+For this we compare China’s Kaya identity with other developing and developed nations.
+Furthermore, we consider China’s sectoral emissions trends and contrast them with those of (other) developing and developed nations, controlling for differences in population size and GDP.
+Secondly, we investigate China’s claim of developed countries’ being the driver of climate change, by calculating different measures of (historic) responsibility and assess the level of responsibility China bears in combatting climate change.
+We discuss these findings with regards to a projection of China’s cumulative emissions.
+
+The remainder of this paper is structured as follows: In section 2 we provide an overview of our data and main assumptions, before analyzing China’s self-characterization as a developing country in section 3.
+Section 4 compares different equity metrics for China and other big emitters and discusses China’s role in addressing climate change against different scenarios of future Chinese cumulative emissions.
+In section 5 we discuss our findings in light of other available assessments of China’s role and conclude.
+
+```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
+YEAR_L = 1970
+YEAR_U = 2020
+GAS = "GHG"
+
+source("r-analysis/data_single_polluters.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_single_polluters_stacked_rel.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r,fig.cap="Figure 2: Kaya Identity China - 2000 - 2019"}
+YEAR_L = 2000
+YEAR_U = 2019
+GAS = "GHG"
+
+source("r-analysis/data_kaya_analysis.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_kaya_chn.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r,fig.cap="Figure 3"}
 YEAR_L = 1850
@@
 
-### Equity Metrics
+# Data & Assumptions
+
+Our project is data-driven in nature and relies heavily on the availability of various metrics on both greenhouse gas emissions and measures of (economic) development.
+Furthermore, there are key assumptions connected to our analysis that impact our findings.
+This section provides an overview of the data-sets we use, and makes our underlying assumptions about the data explicit.
+
+## Used Data
+
+In terms of data on GHG emissions we make use of the EDGAR database as the core of our analysis.
+It contains yearly emissions data on the major greenhouse gases by country and sector and makes them commensurable based on global warming potentials on a 100-year scale.
+The database and its development are a joint project of the European Commission Joint Research Center and the Netherlands Environmental Assessment Agency [@EC2022].
+
+We supplemented this data set with data on LULUCF emissions from the national GHG inventory database and add them to the total GHG emissions.
+The data itself was sourced from annual GHG inventories for Annex I countries and gathered from recent communications, biennial update reports, REDD+ submissions and NDCs for Non-annex I countries [@Giacomo2022].
+
+For consumption-based emissions of selected countries since 1990 we make use of an updated dataset from Peters et.
+al [updated from @Peters2011].
+Additionally, we rely on world bank data for GDP, GNI and population [@WorldBank2022d].
+We further hand code variables for countries, specifically their membership to the EU 27 & 28 respectively, as well as their income classification according to the 2019-word-bank-classification for gross national income per capita [@WorldBank2018].
+Lastly two datasets were made available to us a) an inventory of CO2 emissions since 1750 and b) IEA data for energy consumption.
+
+## General Assumptions
+
+Regarding our main assumptions we limit our analysis to years until 2019 as we believe that the pandemic heavily distorted prior trends and hit countries and their economies to varying extents, making any meaningful interpretation and comparison difficult.
+Our main assumption here is that the trends and developments up to 2019 are more meaningful indicators for developments in the years and decades to come, compared to the pandemic years.
+
+To make information accessible and to allow for comparisons across gases we choose to provide all information on multiple GHGs based on 100-year global warming potentials, as provided in our core database EDGAR.
+
+# Analysis
+
+TO BE DONE: Intro statement.
+
+## China’s Self-Characterization as a Developing Country
+
+In the following, China’s self-characterization as a developing country will be critically reviewed from an emissions perspective.
+For this, a definition of developed and developing countries will be developed.
+This is followed by a comparison of China’s emissions development with the emissions development of other developed and developing nations by using a Kaya decomposition.
+As the distribution of emissions by sector is another way to distinguish between developing and developed countries, China’s sectoral emissions are also compared to other countries.
+With this, we strive to find an answer to our first research question.
+
+### Categorization of Developed and Developing Countries
+
+To distinguish between developed and developing countries, different indicators can be considered for instance GDP per capita, the gross national income GNI per capita or the human development index (HDI).
+Furthermore, other indicators such as the level of education or democracy can be taken into account when determining whether a country is developed, developing or underdeveloped [@Kinnunen2019].
+
+Our main data set, the EDGAR dataset, already provides a classification of countries in two groups – developed and developing – which we will use as a starting point.
+According to this, China is categorized as a developing country.
+However, we realized that a more granular categorization of countries might be helpful to answer our first research question.
+Especially since any type of self-categorization might be biased as countries stand to gain from underestimating their development in order to receive more aid and have less responsibilities in the UNFCCC process.
+
+Thus, we decided to use a second country classification scheme for comparison.
+Although a financial indicator might not completely summarize a country’s level of development, we decided to use the GNI cut-offs as our main indicator of development.
+This is mainly because research finds that the GNI correlates with a number of accepted indicators of development outcomes [@Fantom2016].
+Furthermore, the income classification is the standard classification in discussions on development.
+The World Bank, but also other international organizations and aid agencies, use this for analytical and operational purposes.
+The GNI is calculated in the following way:
+
+TO BE DONE FOrmula
+
+Thus, going forward we will also use the World Bank’s Classification of Countries by income, which assigns countries into four different groups: high income, upper-middle income, lower-middle income, low income.
+Income is measured using the GNI per capita of the previous year in U.S.
+dollars using a three-year average exchange rate.
+The classification is updated each year.
+For our analysis, we are using the threshold valid as of July 2019, as our emissions analysis considers this year as the last year.
+The thresholds are as follows:
+
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{|l|l|}
+    \hline
+        \textbf{Group  } & \textbf{Thresholds July 2019 in USD  } \\ \hline
+        Low income   & $< 1,026$ \\ \hline
+        Lower-middle income   & $1,026 - 3,955$ \\ \hline
+        Upper-middle income  & $3,966 - 12,375$ \\ \hline
+        High income  & $> 12,375$ \\ \hline
+    \end{tabular}
+\end{table}
+
+According to the World Bank’s classification, China is classified as an upper-middle income country since 2010 [@WorldBank2022d].
+
+To make use of the more granular look at country groups in relation to our research question, we assume low- and lower-middle income countries to be more likely resembling  developing nations and middle-upper- and high-income countries to be more likely resembling developed nations.
+
+### Comparison of Kaya Identities
+
+With a Kaya identity, one can identify the main driving forces of CO2 emissions in a certain period.
+The Kaya identity expresses CO2 emissions (F) as a function of GDP (G), population (P) and energy (E):
+
+TO BE DONE FOrmula
+
+The term highlights the different components of the identity: G/P is GDP per capita, E/G is the energy intensity of GDP and F/E is the carbon intensity of energy [@Lamb2021].
+By comparing Kaya identities of different regions, we can also discuss regional differences.
+Hence, we use the Kaya identity to discuss if the driving forces of emissions show similarities with developing or developed nations.
+
+Figure 4 displays China’s and developing and developed countries’ Kaya identities according to the IPCC classification in the Sixth Assessment Report from 2000 to 2019.
+In those years, China’s GDP per capita was growing with a factor close to five, thereby being the strongest upward driver of emissions.
+GDP per capita increased almost in tandem with carbon emissions until 2010, in which a decoupling took place.
+Ever since, Chinese emission’s growth rates have been much slower than those of GDP per capita.
+This decoupling is likely due to the decreasing energy intensity of GDP and carbon intensity of energy at the same time.
+The energy intensity is the main counteracting factor on Chinese emissions and decreased constantly since 2005.
+The decreasing trend seemed to have already started in 2000 but had rebounded before 2005, which can be traced back to 2001, when China joined the WTO [@Zheng2020].
+However, since 2010 the decrease has been significant, hence driving the reduction of overall emissions growth rate.
+Furthermore, one can see that carbon intensity of energy decreased since 2010 meaning that the amount of CO2 per unit of energy is decreasing.
+Nevertheless, the relationship remains a positive one.
+The decline of both the energy intensity and carbon intensity is likely due to economic efficiency improvements.
+Additionally, carbon intensity further declined because of increasing capacity additions of renewable energies (changes in the fossil share) and the reduced emission intensity of fossil fuels (changes in the fossil intensity, fuel switch) [@Zheng2020;@Peters2017].
+Population changes only played a minor role but can be considered as a persistent upward driver of emissions.
+
+Comparing China’s Kaya identity to the decomposition of the development of CO2 emissions of developing and developed countries does not provide a clear result on whether China can be considered a developing or developed nation.
+In general, economic growth is the main driver of CO2 emissions, both in developed and developing nations.
+However, GDP per capita growth is much larger and hence closer to China’s figures in developing nations as they show a greater growth potential.
+Overall carbon emissions are decreasing in developed nations while they are increasing in developing nations and China.
+This supports the notion of China being a developing country relying on emissions driven growth.
+On the other hand, China’s energy and carbon intensity are decreasing as it is the case for developed countries.
+The population’s development of China also more closely resembles the trend of developed countries than those of developing countries.
+To sum up, this classification does not clearly indicate whether China is a developing or developed country.
+As mentioned above, comparing China to a more granular classification of countries might be worthwhile, as the EDGAR dataset for example considers Saudi-Arabia, a country with one of the highest GDP per capita as a developing nation.
+
+```{r,fig.cap="Figure 4"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+Thus, in the next steps, the World Bank’s Income Classification Scheme will be used for comparison (Figure 5).
+In high-income countries, GDP per capita and population are increasing only at low levels (by roughly the factor 0.5 and 0.2 respectively).
+Carbon intensity and energy intensity are decreasing, keeping carbon emissions down.
+The carbon intensity is decreasing because of two factors: the fossil intensity and the fossil share.
+In contrast, in low-income countries, the growth of CO2 emissions is exceeding the growth of GDP per capita, both rising by a factor of 2.8 and 5 respectively over the observed time span.
+This is driven by a high and increasing carbon intensity.
+Furthermore, population growth plays an important role in this group, and can be considered a further driving factor of CO2 emissions.
+The only contrasting factor is the decreasing energy intensity.
+Comparing both groups of countries to China, one can resume that China’s development does not fit in either of the groups perfectly.
+Like before China’s Kaya decomposition shares similar characteristics as both groups: The small population growth resembles the trend of high-income countries, the dramatically decreasing energy resembles the trend of low-income countries.
+Considering lower-middle income countries, they seem to show upwards trends in any of the indicators except for energy intensity.
+In comparison, in upper-middle income countries carbon emissions and GDP per capita develop in tandem, while carbon intensity and energy intensity only fluctuate around zero in the years from 2000 to 2019.
+
+```{r,fig.cap="Figure 5"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+To conclude, China seems to be an exception considering the driving forces of emissions and thus cannot be assigned uniquely to any of the studied group of countries.
+This is especially due to the exceptionally high GDP growth which only recently decoupled from carbon emissions.
+In terms of GDP growth rates and carbon emission growth, China can be considered a developing nation as they base their GDP growth on growing carbon emissions.
+However, the carbon and energy intensity that keep CO2 emissions down, show that China is already getting more efficient in its production and that it has the capacity to invest in renewable energy source.
+Considering only those two indicators, China can be better compared to developed countries.
+Thus, it seems that China has a responsibility to put forward this trend of efficiency gains in order to decouple economic growth and emissions even more.
+To examine the status of China in more depth, China’s sectoral trends will be compared to the two discussed classification schemes in the following.
+This can provide further information on China’s classification, since developing and developed nations usually generate wealth in different economic sectors.
+
+### Comparison of China’s Sector Trends
+
+In this part, sector trends of different groups of countries will be considered using the same two categories of country groups as before.
+We take into account five sectors: energy, industry, transport, AFOLU (which in the EDGAR database only includes agricultural emissions), and buildings.
+China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 6 & 7.
+Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively.
+Only smaller shares are attributable to transport (6%), buildings (5%) and AFOLU (6%).
+
+In developed countries (according to the EDGAR classification), energy and industry still account for the majority of emissions (58% in total), but transport emissions play a much larger role (21%) of the GHG emissions than in China.
+This high share of transport emissions can be accounted to the high use of private cars in developed economies.
+For instance, the EU road transport accounts for 77% of GHG emissions in the transport sector in 2020 [@EEA2022].
+AFOLU emissions and emissions from buildings each account for roughly 10% of the total GHG emissions.
+In contrast, in developing nations, the share of AFOLU emissions is much larger (21%).
+The high share is typically associated with the expansion of agriculture into carbon-dense tropical forests, but also the lack of economic development of other sectors.
+The share of transport, however, is much lower than in developed countries as individual transport is not that widely spread.
+The relative emissions in energy and industry are comparable to those in developed countries as developing countries are rapidly growing to fulfil their own and the developed countries’ consumption needs.
+However, absolute emissions levels are much lower.
+
+Again, China’s split of emissions does not fit in either of the two categories.
+On the one hand, China’s share of emissions coming from the AFOLU sector is relatively small resembling developed country characteristics.
+On the other hand, their emissions from transport sector are small as well.
+This is due to the immense share of emissions stemming from industry and energy, which reduces the share of emissions in the other sectors.
+
+```{r,fig.cap="Figure 6"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 7).
+
+In this classification, differences between high-income and low-income countries are very pronounced.
+While in high-income countries a major share of emissions resulted from energy systems (37%) in 2019, the share of emissions from energy only accounts for 9% of all GHG emissions in low-income countries.
+This highlights an energy system largely depending on fossil fuels in high-income countries on the one hand, and the lack thereof in low-income countries on the other hand.
+The differences are also immense considering the transport sector.
+In high-income nations, 20% of the GHG emissions stem from transport, while in low-income countries, the share is only 7%.
+However, the biggest differences are the AFOLU emissions.
+High-income countries have a share of 9% for AFOLU emissions while in low-income countries this sector accounts for 57% of emissions.
+The reasons for these differences were discussed above.
+
+The emissions by sector for lower-middle and upper-middle income countries are more similar, the only difference is that the share of AFOLU is larger in lower-middle income countries and the share of transport is larger for upper-middle income countries, indicating further progress on the typical developing path of the latter country group.
+
+Again, China does not really fit into either of the categories due to its very high share of emissions stemming from the energy and industry sector.
+China's relative emissions from these two sectors are much larger than in any of the other groups studied.
+
+```{r,fig.cap="Figure 7"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 8).
+
+Comparing trends is particularly helpful, as emissions from the energy and industry sector in China are so large, that it makes any comparison of the remaining sectors with the potential peers very difficult.
+
+China’s AFOLU emissions per capita are relatively low and decreasing over time, similar to the emissions in lower-middle income countries in this sector.
+The AFOLU emissions per capita of high income and upper-middle income countries are large because a relatively high agricultural output spread over relatively small populations.
+In the building sector, Chinese emissions per capita are relatively low compared to high-income countries and rather on the same level as upper-middle income countries.
+The per-capita emissions of the building sector are high in richer countries as people require more floor space per capita compared to lower-income countries.
+For transport, China’s emissions stayed on a low level until 2000 and then increased at high speed.
+Now, they are comparable to per capita emissions of upper-middle-income countries.
+
+Considering the three sectors mentioned above, China seems to resemble more the emissions per capita characteristics of lower-middle or upper-middle income countries, however this is different for the energy and industry sectors.
+In the energy sector, China’s emissions per capita increased up to roughly 4 tCO2eq in 2019.
+This is much higher than for upper-middle income countries, in which per capita emissions stayed relatively constant at 3 tCO2eq in 2019.
+In high-income countries, the per capita emissions from energy are still higher (5 tCO2eq) in 2019 than in China, however, one can see a downward trend there.
+Thus, one could argue that China can soon be compared to a high-income country regarding its per capita energy system emissions.
+The same holds for the industry sector, where this development is even more pronounced.
+Emissions per capita in the industry sector in China increased massively in the 2000s and are now at a plateau of 4 tCO2eq annually.
+The per capita emissions of high-income countries in the industry sector in contrast have decreased since the 1970s and are now at 3 tCO2eq.
+In the industry China has thus already surpassed per capita emissions levels of high-income countries and has the highest value among the five studied panels in this sector.
+
+```{r,fig.cap="Figure 8"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
 ### Discussion
 
-# Discussion and Conclusion
+The prior analysis has shown that clearly classifying China as either a developed or a developing from an emissions perspective remains difficult.
+
+However, what this analysis has clearly shown, is that the simple self-characterization of China as a developing country, that is mirrored by Sixth assessment report of the IPCC, does not do justice to the drastic economic and emissions development China has witnessed in the last decades.
+As the analysis has shown, China clearly exhibits certain emission characteristics of developed countries in some sectors like industry and energy systems.
+When it comes to agricultural per capita emissions trends it is comparable to lower-income countries.
+Maybe most importantly, in the industry sector it has the highest per capita emissions of any of the candidates that were up for comparison.
+
+What this analysis has undoubtedly confirmed is the realization that China is a special case in every respect.
+China's unique economic development, which has led to a five-fold increase in GDP per capita over the past two decades, saw the country develop an energy and industrial system that together accounts for 82% of the country’s total emissions, a share 20% higher than that of high-income countries.
+
+Nevertheless, one needs to consider that development is not equally distributed in China.
+The rural population has benefited significantly less from the economic development than the urban population (East-West divide) [@Knight2004].
+However, the argument that one still has the right to predominantly emissions-based development (as in 1992) is no longer in line with China's current status as the world’s biggest emitter.
+Hence, China's NDC’s storyline, which seeks the main responsibility for climate change in developed nations, is too undercomplex and does not do justice to the evolved realities.
+
+To further investigate this issue, in the next we will predict the future development of emissions of China and other countries and further consider different equity metrics.
+
+## China’s Equitable Share in Climate Change Mitigation
+
+The following chapter discusses China’s equitable share in climate change mitigation.
+In order to answer the research question, we will first discuss the future development of China’s emissions, to determine when China will become the biggest cumulative emitter.
+For this, we consider multiple development pathways of China in terms of emissions and discuss China’s cumulative emissions in comparison to other countries.
+Moreover, we will present different rankings of absolute emissions, per capita emissions, GDP and GDP per capita, cumulative emissions and consumption-based CO2 emissions to discuss China’s responsibility from different perspectives.
+
+### Future Development of China’s Emissions
+
+The first equity metric we consider is cumulative emissions, as China claims historic developed countries’ emissions being the main driver of climate change.
+Looking at cumulative emissions from 1750 until 2019, China is on 3 rd position, only behind the U.S.
+and the EU-27.
+According to this, in 2019 China would already have the 3rd-largest responsibility to reduce emissions, since it has historically  emitted a total of 12.4% of all greenhouse gases.
+This is in direct contrast to the country’s claim to be less responsible for the warming climate.
+
+Importantly, if China continues its emissions pathway, it will become the largest cumulative emitter at some point.
+In order to estimate when China will move into first place, we have modeled expected emission trends for China as well as for the EU and the U.S.
+Our modelling is based on the following assumptions:
+
+First, for simplicity, we assume that China will reduce not only CO2 emissions, as communicated internationally, but all GHG emissions to zero.
+As we have seen in section 3, Chinese emissions trends vary strongly across sectors.
+Therefore, we have modelled each sector’s future emissions pathway following different assumptions.
+In general, we assume a constantly declining growth rate of emissions in each sector until a peak year starting with the 2018 to 2019 growth factor.
+After the peak we consider an s-curve emissions reduction for the following years until zero emissions are reached, as China might first use the simple levers to reduce emissions fast and then needs to work on emissions which are difficult to bring down.
+
+As emissions in the AFOLU sector have already been decreasing in China, we expect a relative flat emissions level until 2025, followed by a decrease until zero emissions are reached in 2060.
+Buildings are assumed to peak emissions in 2030 and are at zero in 2060.
+The energy systems sector is expected to peak the earliest, in 2028, due to the continued heavy roll-out of renewable energy sources in China and the experiences from other countries decarbonization journeys.
+Complete decarbonization is then assumed to be reached by 2055.
+We assume the industry sector to peak by 2030 and reach complete decarbonization by 2065.
+As transport is the fastest growing sector of Chinese emissions, we assume this trend to continue (but slowed down) until 2040, and complete decarbonization in 2065.
+
+In modeling the development of emissions for the EU-27 and the U.S., we are guided by data from the PBL Netherlands Environmental Agency [@PBL2022].
+For simplicity we do not differentiate by sector but assume a linear decrease in annual emissions up to the projected emissions value for 2030 in both the U.S.
+and the EU-27.
+Thereafter, we also use an s-shaped reduction curve to achieve zero emissions by 2050.
+
+The resulting sectoral emissions pathways for each country/region are depicted in figure xx.
+The resulting cumulative emissions forecasts for the three countries/blocks are shown in figure xx.
+Accordingly, China will pass the EU-27 in cumulative GHG emissions in 2027 and is projected to pass the U.S.
+in 2032 .
+Afterwards it will be the largest cumulative emitter.
+
+These projections hold even when modelling each sector according to the Chinese NDC (assuming peak years of 2030 and zero emissions by 2060).
+In the NDC-scenario China will surpass the EU and US respectively in the same years as modeled in our main scenarios, but at different emission levels – 452.4 GtCO2eq (main scenario)  451.8 GtCO2eq (NDC-scenario).
+When projecting only  CO2 emission developments1 China will surpass the EU in 2031 and the US in 2038 according to both scenarios.
+
+This analysis shows that maintaining targets that are ambitious in absolute terms but relatively easy to achieve compared to China's size and economic power, have already put China at the forefront of global responsibility for climate change.
+From a cumulative emissions perspective, China definitely has the same if not larger GHG reduction obligations as many developed countries, especially when considering that a majority of China’s emissions were emitted after the problem of climate change has made it on top of the global policy agenda.
+Moreover, the statement of the Chinese NDC that climate change is mainly caused by others is not tenable.
+
+```{r,fig.cap="Figure 9"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+However, cumulative emissions, while easily understood, are not the only conceivable equity metric to consider when attempting to assess a country's fair share in responding to climate change.
+Therefore, in the following sub-section we investigate other equity metrics.
+
+### Equity Metrics
+
+This chapter presents different rankings which can shed light on the question of China’s responsibility to mitigate climate change from different angles.
+The following rankings always display the top 10 countries (or in case of the EU regions) in the respective category.
+Furthermore, other important countries are added for comparison as well as a category named “Other” which summarizes the share of all remaining countries.
+The EU-27 is mentioned as a point of reference, but emissions of the separate countries are displayed in the ranking or summarized in the “Other” category.
+Every graph also provides reference points for the rank position where cumulative 50 % of global GDP, population and emissions are surpassed.
+
+First, we consider China’s responsibility based on absolute emissions in the year 2019 (Figure X).
+In the ranking, China ranks on first place with absolute emissions of 14,219.37 Mt CO2 eq.
+This is more than double of the U.S.
+emissions (6,266.8 Mt CO2 eq) and also close to the emissions of all other countries that do not belong to the group of the top 10 emitters combined (14,075.12 Mt CO2 eq).
+Together with the U.S., India and Russia, China makes up for 50% of global emissions, but these four countries do not produce half of the global GDP, nor do they represent half of the world’s population.
+This highlights that the responsibility of these four countries to drastically reduce emissions is high.
+Considering that China is producing more than double the emissions of the U.S., China has by far the highest responsibility to mitigate climate change from a current absolute emissions perspective.
+
+```{r,fig.cap="Figure 10"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+Next, we consider emissions per capita (Figure x).
+This is important as China is the country with the biggest population worldwide of approx.
+1.4 billion people [@WorldBank2022c].
+Looking at this ranking, it is important to consider that the top emitters according to per capita emissions are relatively small countries with low absolute emissions but also small populations.
+Thus, when it comes to reducing absolute emissions and fighting climate change, they can only play a minor role.
+China interestingly ranks on place 43 with roughly 10t CO2 eq / capita, before EU-27 but behind the U.S.
+(Ranking: 17).
+According to this equity metric, China’s fair share to mitigate climate change from this perspective should be located between the share of these two countries/groups of countries.
+
+```{r,fig.cap="Figure 11"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+Considering GDP and GDP per capita refers to the capacity of acting on climate change, following the assumption that richer countries have more resources available to fight climate change.
+As Figure XX shows, China had the highest GDP of all countries in 2019, with USD 22.49 trillion.
+Based on this, China would theoretically have to make the greatest conribution to reduce emissions.
+Absolute GDP, however, is limited in telling us about a country's actual capacity because it ignores population size.
+Therefore, considering GDP per capita might be more worthwhile.
+Here China only ranks 81st place in the world.
+Therefore, China’s responsibility is relatively low from the GDP per capita perspective.
+In comparison, the U.S.
+rank on place 11.
+Countries that are in the top 10 emitters are often relatively small countries deriving their wealth from natural resources.
+Hence, they have a high responsibility to mitigate climate change as they have the ability to pay for climate change mitigation measures.
+However, their absolute emissions are relatively small and thus an ambitious reduction might not make a huge difference for achieving climate targets.
+Thus, one should consider that these countries should specifically contribute by providing financial aid to mitigate emissions elsewhere.
+
+```{r,fig.cap="Figure 12"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r,fig.cap="Figure 13"}
+YEAR_L = 1850
+YEAR_U = 2060
+GAS = "GHG"
+
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+### Discussion TBD
+
+To sum up, China has a very high responsibility to mitigate climate change, even the highest responsibility of all countries when considering some of the discussed equity metrics.
+Based on our calculations, China is likely surpass the EU well before 2030 and the US shortly after in 2032  in terms of cumulative emissions over all GHGs from 1850 to 2019 and a modeling of emissions thereafter.
+The difference in emissions from all GHGs to CO2 emissions highlights the importance to extend the frame of historic respon
+
+Therefore, China now has a major responsibility to reduce emissions which is reinforced when considering that the country’s massive emissions growth only started after the adoption of the Kyoto Protocol in 1997, at a time when the consequences of climate change were already being heavily discussed.
+
+However, we also need to consider that China only ranks on 81st.
+and 43rd place considering their GDP per capita and their emissions per capita, respectively.
+This diminishes China’s responsibility to some extent, showing that the global community needs to grant space for economic development to be fair.
+However, this economic development should ideally be decoupled from a growth in emissions.
+If we look at the per capita emissions of the countries that rank first, we see that these are mostly very small and, from the perspective of absolute emissions, less important countries.
+Although these countries might have a high ability to pay from a per capita perspective, their overall economic power is not high.
+The opposite is true for China.
+China ranks first place in absolute emissions and GDP in 2019 with a great distance to the following places.
+
+Thus, China has one of the greatest responsibilities to reduce emissions from a historic emissions, current emissions and economic capacity perspective.
+
+# Discussion and Conclusion TBD
+
+In our analysis, we were striving to answer two research questions, namely if China can be considered a developing country and what China’s fair share in climate change mitigation should be.
+
+Regarding out first research question, we find that China cannot be easily classified as a developed or developing country.
+This is due to the unique economic growth (China’s GDP per capita quintupled in the last 20 years), which went hand in hand with very high energy and industrial sectors’ emissions.
+Comparing these to other developed countries, one can see that China clearly exhibits these countries’ characteristics in term of sectoral emissions.
+However, China’s agricultural per capita emissions trends are more comparable to lower-income countries.
+
+Our analysis of different equity metrics for the second research question has shown that China not only has a huge responsibility to curb emissions, but also the financial capability to do so.
+The country is the world’s largest emitter in annual and cumulative terms (based on our data) and has the highest GDP of all countries.
+While it is important to acknowledge further room for development, one cannot disregard the fact that without significant emission reductions from China, any attempt to stay within the temperature limits of the Paris Agreement is sure to fail.
+
+Hence, we believe that China’s fair share is much higher than what they currently plan to do.
+Together with the EU-27 and the U.S., China should bear the highest responsibility for climate change mitigation.
+Its self-classification as a developing country is clearly politically motivated, to not give in to the demands of having to do more.
+At the same time, the political leadership in Beijing can present itself as a top student in the international community by effortlessly surpassing its own goals, as it is expected by different observers [@CAT2022].
+
+In the following, our analysis will be contrasted with two other assessments of China’s fair share – the assessment by the Climate Action Tracker and by the Climate Equity Monitor.
+
+The CAT evaluates the fair share of a country based on assessments in the literature.
+The results of the literature are categorized using seven equity indicators ranging around considerations of responsibility, capability, cost-effectiveness and equality, which are weighted equally in the analysis.
+All results of the evaluated studies are then depicted on a scale for each category and a 90% confidence interval is built.
+Based on this, the CAT develops a range of what would be a fair share and where to categorize the different countries.
+The CAT values China’s share in mitigation efforts as highly insufficient.
+In comparison, the U.S.’s, India’s and the EU’s planned policies and targets are only considered insufficient for achieving a fair share target under the Paris Agreement [@CAT2022].
+
+Another equity metric is developed by the Climate Equity Monitor.
+The Climate Equity Monitor is the first initiative from the Global South that tracks equity in climate action for Annex 1 and Non-Annex 1 countries.
+The initiative calculates the fair share of the carbon budget by using the share of cumulative emissions based on the share in the global population for a contemporary base year (2019).
+The cumulative annual emissions of a country are calculated for the period from 1850 to 2019.
+Based on this, the Climate Equity Monitor calculates if a country has a carbon debt or carbon credit.
+This measure is calculated as the difference between cumulative emissions of a country and the country’s fair share of the global carbon budget already consumed.
+For China as a Non-Annex 1 country, they conclude that the country has a carbon credit of 122.4 Gt CO2eq.
+In comparison, India has a carbon credit of 337.6 Gt CO2eq while the US has a carbon debt of 445 Gt CO2eq, and Russia has a carbon debt of 125.44 Gt CO2eq [@CEM2022].
+Accordingly, if China kept emitting at its current rate, it would have used up its remaining carbon credit until 2031.
+
+It is interesting that the Climate Action Tracker and the Climate Equity Monitor come to conclusions that can be interpreted differently.
+While the latter initiative only considers cumulative emissions allowances in relation to population size, the former’s assessment benchmarks climate targets and policies against a larger variety of equity metrics.
+The remaining carbon credit derived from the Climate Equity Monitor might be misleading to a certain degree, as it might suggest little urgency to act, especially when comparing the credit numbers to the debt numbers of other countries.
+The CAT’s assessment, while being methodically more sophisticated, better communicates the implications of current emission reduction targets and respective policies from an equity perspective.
+
+Our analysis has the following limitations: We only consider cumulative emissions from 1850-2019, but the consideration of other time periods could also be conceivable.
+The problem of climate change caused by anthropogenic greenhouse gas emissions has only been known since the 1970s, and since the 1990s there has been a dedicated international process to address the problem.
+Against this background, an additional consideration of cumulative emissions in these time periods might be worthwhile.
+For a comprehensive assessment of China’s fair share, it would have also been interesting to discuss further equity metrics such as a ranking of consumption-based emissions.
+However, this was not possible for us, as our data only included consumption-based data for approx.
+100 countries and crucially missing the US, making a comparison less meaningful.
 

### 2022-12-12 r-plots/plot_kaya_incomelevels.R

@@ -8,7 +8,7 @@ PDATA$plot_level_kay<-c(COUNTRY,"Low income","Lower middle-income","Upper middle
 
 #plot
 
-PDATA$kaya_incomelevels %>%
+OUT<-PDATA$kaya_incomelevels %>%
   mutate(region = fct_relevel(dev_status_income,PDATA$plot_level_kay)) %>% 
   ggplot(.,aes(x=year,y=value,color=var)) +
   geom_line(size=1) +
@@ -24,3 +24,4 @@ PDATA$kaya_incomelevels %>%
                      guide = guide_legend(reverse = TRUE)) +
   theme(legend.title=element_blank(),
         axis.title.x = element_blank())
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-report/Paper.Rmd
bib fix

@@
 bibliography:
-#  - anna.bib
-#  - fabian.bib
+  - anna.bib
+  - fabian.bib
   - packages.bib
@@
 China has adopted numerous policies to support its international targets, such as the “Working Guidance for Carbon Dioxide Peaking and Carbon Neutrality” and the “Action Plan for Carbon Dioxide Peaking Before 2030”.
-The former spells out a set of principles and sectoral goals to achieve carbon dioxide peaking and carbon neutrality, among them the need to exercise nationwide planning and the prioritization of conversing energy (Department of Resource Conservation and Environmental Protection, 2021a).
+The former spells out a set of principles and sectoral goals to achieve carbon dioxide peaking and carbon neutrality, among them the need to exercise nationwide planning and the prioritization of conversing energy [@DRCEP2021a].
 The latter defines key tasks for driving the low-carbon energy transition or saving energy, carbon emission mitigation and efficiency improvement [@DRCEP2021b].
@@
 It were their emissions that had caused the dramatic increase of GHGs in the atmosphere.
-China, on the other hand, was a developing country, thereby having the right to develop [@China2022].
+China, on the other hand, was a developing country, thereby having the right to develop [@China2021].
 
@@
 
-```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
-YEAR_L = 1970
-YEAR_U = 2020
+```{r,fig.cap="Figure 1"}
+YEAR_L = 1850
+YEAR_U = 2060
 GAS = "GHG"
 
-source("r-analysis/data_single_polluters.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_single_polluters_stacked_rel.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
 
@@
 
-```{r,fig.cap="Figure 2: Kaya Identity China - 2000 - 2019"}
-YEAR_L = 2000
-YEAR_U = 2019
+```{r,fig.cap="Figure 2"}
+YEAR_L = 1850
+YEAR_U = 2060
 GAS = "GHG"
 
-source("r-analysis/data_kaya_analysis.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_kaya_chn.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
 
@@
 Nevertheless, one needs to consider that development is not equally distributed in China.
-The rural population has benefited significantly less from the economic development than the urban population (East-West divide) [@Knight2004].
+The rural population has benefited significantly less from the economic development than the urban population [East-West divide, @Knight2004].
 However, the argument that one still has the right to predominantly emissions-based development (as in 1992) is no longer in line with China's current status as the world’s biggest emitter.

### 2022-12-12 r-report/Paper.Rmd

@@
 
-```{r,fig.cap="Figure 1"}
-YEAR_L = 1850
-YEAR_U = 2060
+```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
+YEAR_L = 1970
+YEAR_U = 2020
 GAS = "GHG"
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_single_polluters.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_single_polluters_stacked_rel.R", local = TRUE, print.eval = TRUE)
 
@@
 
-```{r,fig.cap="Figure 2"}
-YEAR_L = 1850
-YEAR_U = 2060
+```{r,fig.cap="Figure 2: Kaya Identity China - 2000 - 2019"}
+YEAR_L = 2000
+YEAR_U = 2019
 GAS = "GHG"
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_kaya_analysis.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_kaya_chn.R", local = TRUE, print.eval = TRUE)
 

### 2022-12-12 r-report/Paper.Rmd
Added Plot 3

--- 2022-12-12 r-report/Paper.Rmd
@@
 
-```{r,fig.cap="Figure 2: Kaya Identity China - 2000 - 2019"}
+```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
+YEAR_L = 1970
+YEAR_U = 2019
+GAS = "GHG"
+COUNTRY = "China"
+
+source("r-analysis/data_sectors_bycountry.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_sectors_bycountry_stacked_abs.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
 YEAR_L = 2000
@@
 source("r-plots/plot_kaya_chn.R", local = TRUE, print.eval = TRUE)
-
-plot(OUT)
-```
-
-```{r,fig.cap="Figure 3"}
-YEAR_L = 1850
-YEAR_U = 2060
-GAS = "GHG"
-
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
 

### 2022-12-12 r-report/Paper.tex

@@
 among them the need to exercise nationwide planning and the
-prioritization of conversing energy (Department of Resource Conservation
-and Environmental Protection, 2021a). The latter defines key tasks for
-driving the low-carbon energy transition or saving energy, carbon
-emission mitigation and efficiency improvement \citep{DRCEP2021b}. With
-its ``14th Five-Year Plan on Renewable Energy'', the country aims to
-further accelerate its renewable energy expansion. By 2025, 33\% of
-electricity ought to be supplied by renewable sources (18\% non-hydro),
-which could decrease annual carbon emissions by 2.6 gigatons
-\citep{Zhou2022}.
+prioritization of conversing energy \citep{DRCEP2021a}. The latter
+defines key tasks for driving the low-carbon energy transition or saving
+energy, carbon emission mitigation and efficiency improvement
+\citep{DRCEP2021b}. With its ``14th Five-Year Plan on Renewable
+Energy'', the country aims to further accelerate its renewable energy
+expansion. By 2025, 33\% of electricity ought to be supplied by
+renewable sources (18\% non-hydro), which could decrease annual carbon
+emissions by 2.6 gigatons \citep{Zhou2022}.
 
@@
 atmosphere. China, on the other hand, was a developing country, thereby
-having the right to develop \citep{China2022}.
+having the right to develop \citep{China2021}.
 
@@
 distributed in China. The rural population has benefited significantly
-less from the economic development than the urban population (East-West
-divide) \citep{Knight2004}. However, the argument that one still has the
-right to predominantly emissions-based development (as in 1992) is no
-longer in line with China's current status as the world's biggest
-emitter. Hence, China's NDC's storyline, which seeks the main
+less from the economic development than the urban population
+\citep[East-West divide,][]{Knight2004}. However, the argument that one
+still has the right to predominantly emissions-based development (as in
+1992) is no longer in line with China's current status as the world's
+biggest emitter. Hence, China's NDC's storyline, which seeks the main
 responsibility for climate change in developed nations, is too
@@
 
-  \bibliography{packages.bib}
+  \bibliography{anna.bib,fabian.bib,packages.bib}
 

### 2022-12-12 r-report/Paper.Rmd
Text eingefügt und graphen bis 3.2

@@
 
-TO BE DONE: Intro statement.
+The following sections will detail our analysis with regard to the two research questions.
+We first turn to China's self-categorization as developing country and contrast it with different comparisons of development metrics as well as emission trends.
+After an interim discussion we will look at China's responsibility with regard to (projected) cumulative emissions and construct rankings for different equity metrics.
 
@@
 
-```{r,fig.cap="Figure 4"}
-YEAR_L = 1850
-YEAR_U = 2060
+```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
+YEAR_L = 2000
+YEAR_U = 201
+COUNTRY = "China"
 GAS = "GHG"
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_kaya_analysis.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_kaya_country_vs.developed-vs_developing.R", local = TRUE, print.eval = TRUE)
 
@@
 
-```{r,fig.cap="Figure 5"}
-YEAR_L = 1850
-YEAR_U = 2060
+```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
+YEAR_L = 2000
+YEAR_U = 2019
 GAS = "GHG"
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_kaya_analysis.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_kaya_incomelevels.R", local = TRUE, print.eval = TRUE)
 
@@
 
-### Discussion
+### Section Summary
 
@@
 
-```{r,fig.cap="Figure 10"}
+```{r,fig.cap="Figure 10: Absolute GHG Emission - 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
 YEAR_L = 1850
@@
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_ranking_abs.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_rank_abs.R", local = TRUE, print.eval = TRUE)
 
@@
 
-```{r,fig.cap="Figure 11"}
+```{r,fig.cap="Figure 11: Per Capita Emissions- 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
 YEAR_L = 1850
@@
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_ranking_per_cap.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_rank_pc.R", local = TRUE, print.eval = TRUE)
 
@@
 
-```{r,fig.cap="Figure 12"}
+```{r,fig.cap="Figure 12: Absolute GDP p - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
 YEAR_L = 1850
@@
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_rank_gdp.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_rank_gdp.R", local = TRUE, print.eval = TRUE)
 
@@
 
-```{r,fig.cap="Figure 13"}
+```{r,fig.cap="Figure 13: GDP per Capita - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
 YEAR_L = 1850
@@
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_rank_gdp_pc.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_rank_gdp_pc.R", local = TRUE, print.eval = TRUE)
 
@@
 
-### Discussion TBD
+### Section Summary
 
 To sum up, China has a very high responsibility to mitigate climate change, even the highest responsibility of all countries when considering some of the discussed equity metrics.
-Based on our calculations, China is likely surpass the EU well before 2030 and the US shortly after in 2032  in terms of cumulative emissions over all GHGs from 1850 to 2019 and a modeling of emissions thereafter.
-The difference in emissions from all GHGs to CO2 emissions highlights the importance to extend the frame of historic respon
-
+Based on our calculations, China is likely to surpass the EU well before 2030 and the US shortly after in 2032 in terms of cumulative emissions over all GHGs from 1850 to 2019 and a modeling of emissions thereafter.
+The difference in emissions from all GHGs to CO2 emissions highlights the importance to extend the frame of historic responsibility beyond CO2 emissions –  especially in light of growing capabilities, issue salience and data availability that all put greater responsibility recent emissions.
 Therefore, China now has a major responsibility to reduce emissions which is reinforced when considering that the country’s massive emissions growth only started after the adoption of the Kyoto Protocol in 1997, at a time when the consequences of climate change were already being heavily discussed.
-
-However, we also need to consider that China only ranks on 81st.
-and 43rd place considering their GDP per capita and their emissions per capita, respectively.
+However, we also need to consider that China only ranks on 81st and 43rd place considering their GDP per capita and their emissions per capita, respectively.
 This diminishes China’s responsibility to some extent, showing that the global community needs to grant space for economic development to be fair.
@@
 The opposite is true for China.
-China ranks first place in absolute emissions and GDP in 2019 with a great distance to the following places.
-
+China ranks first place in absolute emissions and GDP in 2019 with a great distance to subsequent ranks.
 Thus, China has one of the greatest responsibilities to reduce emissions from a historic emissions, current emissions and economic capacity perspective.
@@
 Our analysis of different equity metrics for the second research question has shown that China not only has a huge responsibility to curb emissions, but also the financial capability to do so.
-The country is the world’s largest emitter in annual and cumulative terms (based on our data) and has the highest GDP of all countries.
-While it is important to acknowledge further room for development, one cannot disregard the fact that without significant emission reductions from China, any attempt to stay within the temperature limits of the Paris Agreement is sure to fail.
+The country is the world’s largest emitter in annual terms , on a pathway to take the first  position in  cumulative terms within a decade and has the highest GDP of all countries.
+While it is important to acknowledge the need for further economic development, one cannot disregard the fact that without significant emission reductions from China, any attempt to stay within the temperature limits of the Paris Agreement is sure to fail.
 
@@
 
-In the following, our analysis will be contrasted with two other assessments of China’s fair share – the assessment by the Climate Action Tracker and by the Climate Equity Monitor.
+In the following, our analysis will be contrasted with two other assessments of China’s responsibility – the assessment by the Climate Action Tracker and by the Climate Equity Monitor.
 
@@
 The cumulative annual emissions of a country are calculated for the period from 1850 to 2019.
-Based on this, the Climate Equity Monitor calculates if a country has a carbon debt or carbon credit.
+Based on this, the Climate Equity Monitor calculates whether a country has a carbon debt or carbon credit.
 This measure is calculated as the difference between cumulative emissions of a country and the country’s fair share of the global carbon budget already consumed.
@@
 
-Our analysis has the following limitations: We only consider cumulative emissions from 1850-2019, but the consideration of other time periods could also be conceivable.
+While aiming to be as comprehensive as possible our analysis has some limitations.
+First, we only consider cumulative emissions from 1850-2019, but the consideration of other time periods could also be conceivable.
 The problem of climate change caused by anthropogenic greenhouse gas emissions has only been known since the 1970s, and since the 1990s there has been a dedicated international process to address the problem.
 Against this background, an additional consideration of cumulative emissions in these time periods might be worthwhile.
-For a comprehensive assessment of China’s fair share, it would have also been interesting to discuss further equity metrics such as a ranking of consumption-based emissions.
+Second, the projection of future emissions rests on major simplification assumptions, it is likely that a more sophisticated approach such as an ARIMA-modelling would result in more robust estimates.
+Third, a comprehensive assessment of China’s responsibility could discuss further equity metrics such as a ranking of consumption-based emissions.
 However, this was not possible for us, as our data only included consumption-based data for approx.
 100 countries and crucially missing the US, making a comparison less meaningful.
+Lastly, reducing capacity to mere GDP and GDP per capita considerations is very much simplifying the issue, as land area, access to renewable resources and intellectual property and many other factors determine a countries mitigation potential, which is very likely to differ by sector.
+With these limitations in mind, we believe none the less that our analysis has shed light on the special case of China and has shown that the under complex self-assessment does not withstand a thorough analysis.
+Keeping these assessments in mind will be worthwhile when assessing the responsibilities of upcoming developing nations.
+The case of China has shown that it is crucial to come to a mutual understanding of what constitutes responsibilities and how they can assessed on an objective basis.
+Especially our analysis of future cumulative emissions indicates that it will be key to frame the issue beyond CO2.
 

### 2022-12-12 r-analysis/data_sectors_bycountry.R

@@ -14,6 +14,7 @@ PDATA$data_abs = data_base %>%
 PDATA$data_rel = data_base %>%
   filter(country == {{COUNTRY}}) %>%
   rename(GAS := {{GAS}}) %>%
+  mutate(GAS = GAS*1e6)
   group_by(year,sector_title) %>%
   summarise(GAS_s=sum(GAS,na.rm=TRUE)) %>%
   na.omit() %>%

### 2022-12-12 r-imports/init.R

@@ -48,8 +48,9 @@ theme_ghg = function(){
   
   theme_minimal() %+replace%    #replace elements we want to change
     
-    #theme(plot.title =element_blank()
-      
+    # theme(plot.title =element_blank(),
+    #     plot.subtitle = element_blank()
+    #   
       # #grid elements
       # panel.grid.major = element_blank(),    #strip major gridlines
       # panel.grid.minor = element_blank(),    #strip minor gridlines

### 2022-12-12 r-plots/plot_kaya_chn.R

@@ -1,0 +1,25 @@
+
+PDATA$plot_level_kay<-c(COUNTRY,"Low income","Lower middle-income","Upper middle-income","High income")
+
+
+OUT<-PDATA$kaya_incomelevels %>%
+  mutate(region = fct_relevel(dev_status_income,PDATA$plot_level_kay)) %>% 
+  filter(dev_status_income== "China") %>% 
+  ggplot(.,aes(x=year,y=value,color=var)) +
+  geom_line(size=1) +
+  geom_hline(aes(yintercept=1)) +
+  facet_wrap(.~region) +
+  theme_bw() +
+  scale_y_log10()+
+  scale_color_brewer(palette="Set2",labels=c("Carbon intensity (CO2/energy)",
+                                             "Carbon emissions",
+                                             "Energy intensity (energy/GDP)",
+                                             "GDP per capita (GDP/pop)",
+                                             "Population"),
+                     guide = guide_legend(reverse = TRUE)) +
+  theme(legend.title=element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank())
+if(DIRECT_PLOTTING) plot(OUT)
+
+OUT

### 2022-12-12 r-plots/plot_kaya_country_vs.developed-vs_developing.R

@@ -23,5 +23,7 @@ OUT<-PDATA$kaya_regions %>%
                      guide = guide_legend(reverse = TRUE)) +
   scale_y_log10()+
   theme(legend.title=element_blank(),
-        axis.title.x = element_blank())
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5))
 if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_kaya_incomelevels.R

@@ -23,5 +23,8 @@ OUT<-PDATA$kaya_incomelevels %>%
                                              "Population"),
                      guide = guide_legend(reverse = TRUE)) +
   theme(legend.title=element_blank(),
-        axis.title.x = element_blank())
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        text= element_text(size =9 ),
+        axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5))
 if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_rank_gdp.R

@@ -2,7 +2,7 @@
 PDATA$data_base_lp_gdp <-PDATA$data_base_lp_gdp %>% 
   mutate(y=round(y/1e12,2))
 # Plot pc
-PDATA$p_gdp <- PDATA$data_base_lp_gdp %>% 
+OUT <- PDATA$data_base_lp_gdp %>% 
   ggplot(., aes(x=x, y=y,label =y)) +
   geom_segment(
     aes(x=x, xend=x, y=0, yend=y), 
@@ -30,10 +30,9 @@ PDATA$p_gdp <- PDATA$data_base_lp_gdp %>%
     legend.position="none"
   ) +
   xlab("") +
-  ylab("GDP, ($ Billion US)") +
-  ggtitle("Responsibility 4: GDP 2019", subtitle = "Highes GDP, China, US, EU-27 & Reference for GDP, Population and Emissions")
-
-PDATA$p_gdp + annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp)==PDATA$ghg_50_gdp$country)), y=PDATA$data_base_lp_gdp$y[3]*0.8, 
+  ylab("GDP, ($ Trillion US)") +
+  ggtitle("Responsibility 4: GDP 2019", subtitle = "Highest GDP, China, US, EU-27 & Reference for GDP, Population and Emissions")+
+  annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp)==PDATA$ghg_50_gdp$country)), y=PDATA$data_base_lp_gdp$y[3]*0.8, 
                       label=" ~50 % of global emissions excl. EU-27", 
                       color="black", size=2.5 , angle=0, fontface="italic", vjust =0.4, hjust=-0.2) +
   annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp)==PDATA$gdp_50_gdp$country)), y=PDATA$data_base_lp_gdp$y[3]*0.8, 
@@ -43,4 +42,5 @@ PDATA$p_gdp + annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp)==PDATA$ghg_5
   annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp)==PDATA$pop_50_gdp$country)), y=PDATA$data_base_lp_gdp$y[3]*0.8, 
            label=" ~50 % of global Population", 
            color="black", size=2.5 , angle=0, fontface="italic", vjust =0.4, hjust=-0.2,) 
+if(DIRECT_PLOTTING) plot(OUT)
 

### 2022-12-12 r-plots/plot_rank_gdp_pc.R

@@ -1,6 +1,6 @@
 
 # Plot pc
-PDATA$p_gdp_pc <- PDATA$data_base_lp_gdp_pc %>% 
+OUT <- PDATA$p_gdp_pc <- PDATA$data_base_lp_gdp_pc %>% 
   #mutate(y=round(y,2))%>% 
   ggplot(., aes(x=x, y=y,label =y)) +
   geom_segment(
@@ -30,9 +30,9 @@ PDATA$p_gdp_pc <- PDATA$data_base_lp_gdp_pc %>%
   ) +
   xlab("") +
   ylab("GDP per Capita, ($ 1000 US)") +
-  ggtitle("Responsibility 5: GDP per Capita  2019", subtitle = "Highest GDP per Capita, China, US, EU-27 & Reference for GDP, Population and Emissions")
 
-PDATA$p_gdp_pc + annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp_pc)==PDATA$ghg_50_gdp_pc$country)), y=PDATA$data_base_lp_gdp_pc$y[3]*0.8, 
+  ggtitle("Responsibility 5: GDP per Capita  2019", subtitle = "Highest GDP per Capita, China, US, EU-27 & Reference for GDP, Population and Emissions")+
+ annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp_pc)==PDATA$ghg_50_gdp_pc$country)), y=PDATA$data_base_lp_gdp_pc$y[3]*0.8, 
                        label=" ~50 % of global emissions", 
                        color="black", size=2.5 , angle=0, fontface="italic", vjust =0.4, hjust=-0.2) +
   annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp_pc)==PDATA$gdp_50_gdp_pc$country)), y=PDATA$data_base_lp_gdp_pc$y[3]*0.8, 
@@ -42,4 +42,5 @@ PDATA$p_gdp_pc + annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp_pc)==PDATA
   annotate("text", x=(which(fct_inorder(PDATA$p_an_gdp_pc)==PDATA$pop_50_gdp_pc$country)), y=PDATA$data_base_lp_gdp_pc$y[3]*0.8, 
            label=" ~50 % of global Population", 
            color="black", size=2.5 , angle=0, fontface="italic", vjust =0.4, hjust=-0.2,) 
-
+ if(DIRECT_PLOTTING) plot(OUT)
+ 

### 2022-12-12 r-report/Paper.Rmd
zwischenstand

@@
 source('r-analysis/meta.R')
+theme_ghg = function(){ 
+  theme_minimal() %+replace%
+     theme(
+       plot.title =element_blank(),
+       plot.subtitle = element_blank()
+    )
+}
+DIRECT_PLOTTING = F
 ```
@@
 One year later, in November 2021, ahead of COP26, China submitted its updated NDC to the UNFCCC.
-Accordingly, the country plans to peak its carbon emissions before 2030, decrease the carbon intensity of GDP by over 65% (relative to 2005), have around 25% of non-fossil fuels in primary energy consumption by 2030, increase the forest stock volume by six billion cubic meters until 2030 and have 1,200 GW of wind and solar power capacity installed by the same year [@China2022].
+Accordingly, the country plans to peak its carbon emissions before 2030, decrease the carbon intensity of GDP by over 65% (relative to 2005), have around 25% of non-fossil fuels in primary energy consumption by 2030, increase the forest stock volume by six billion cubic meters until 2030 and have 1,200 GW of wind and solar power capacity installed by the same year [@China2021].
 Although some of these objectives are vague to some degree, and the emissions reduction target is only a relative goal, the ambitions China has set for itself are a marked improvement over the targets set out in the previous 2016 NDC.
@@
 First, we will investigate whether China, from an emissions perspective, can still be characterized as a developing nation.
-For this we compare China’s Kaya identity with other developing and developed nations.
+For this we compare China’s Kaya Identity with other developing and developed nations.
 Furthermore, we consider China’s sectoral emissions trends and contrast them with those of (other) developing and developed nations, controlling for differences in population size and GDP.
@@
 ```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
 YEAR_L = 1970
@@
 GAS = "GHG"
+COUNTRY = "China"
 
@@
 ```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
 YEAR_L = 1970
@@
 ```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
 YEAR_L = 2000
@@
 
-TO BE DONE FOrmula
+$$\text{GNI} = \text{GDP} + \left (\text{EX}_{FS} - \text{IM}_{FS} \right )$$
+
+whereas $\text{GNI}$ be the gross national income, $\text{GDP}$ be the gross domestic product, $\text{EX}_{FS}$ be the money flowing from, and $\text{IM}_{FS}$ the money flowing to foreign countries.
 
@@
         \textbf{Group  } & \textbf{Thresholds July 2019 in USD  } \\ \hline
-        Low income   & $< 1,026$ \\ \hline
-        Lower-middle income   & $1,026 - 3,955$ \\ \hline
-        Upper-middle income  & $3,966 - 12,375$ \\ \hline
-        High income  & $> 12,375$ \\ \hline
+        Low income   & $< 1026$ \\ \hline
+        Lower-middle income   & $1026 - 3955$ \\ \hline
+        Upper-middle income  & $3966 - 12375$ \\ \hline
+        High income  & $> 12375$ \\ \hline
     \end{tabular}
+    \caption{Classification Thresholds\label{tbl:x}}
 \end{table}
@@
 
-With a Kaya identity, one can identify the main driving forces of CO2 emissions in a certain period.
-The Kaya identity expresses CO2 emissions (F) as a function of GDP (G), population (P) and energy (E):
+With a Kaya Identity, one can identify the main driving forces of CO2 emissions in a certain period.
+The Kaya Identity expresses CO2 emissions $F$ as a function of GDP $G$, population $P$ and energy $E$:
 
-TO BE DONE FOrmula
+$$F = P \: \frac{G}{P} \frac{E}{G} \frac{F}{E}$$
 
-The term highlights the different components of the identity: G/P is GDP per capita, E/G is the energy intensity of GDP and F/E is the carbon intensity of energy [@Lamb2021].
+whereas $\frac{G}{P}$ represents GDP per capita, $\frac{E}{G}$ represents the energy intensity of GDP and $\frac{F}{E}$ represents the carbon intensity of energy [@Lamb2021].
 By comparing Kaya identities of different regions, we can also discuss regional differences.
-Hence, we use the Kaya identity to discuss if the driving forces of emissions show similarities with developing or developed nations.
+Hence, we use the Kaya Identity to discuss if the driving forces of emissions show similarities with developing or developed nations.
 
@@
 
-Comparing China’s Kaya identity to the decomposition of the development of CO2 emissions of developing and developed countries does not provide a clear result on whether China can be considered a developing or developed nation.
+Comparing China’s Kaya Identity to the decomposition of the development of CO2 emissions of developing and developed countries does not provide a clear result on whether China can be considered a developing or developed nation.
 In general, economic growth is the main driver of CO2 emissions, both in developed and developing nations.
@@
 ```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
 YEAR_L = 2000
@@
 ```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
 YEAR_L = 2000
@@
 ```{r,fig.cap="Figure 6"}
-YEAR_L = 1850
-YEAR_U = 2060
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
+YEAR = 1950
 GAS = "GHG"
+COUNTRY = "China"
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_sector_regions_yemission.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_facet_regions_sectors_yemission_stacked_rel.R", local = TRUE, print.eval = TRUE)
 
@@
 ```{r,fig.cap="Figure 7"}
-YEAR_L = 1850
-YEAR_U = 2060
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+
+YEAR = 1950
 GAS = "GHG"
+COUNTRY = "China"
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_sectror_incomelevel_yemissions.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_facet_incomelevels_sectors_yemission_stacked_rel.R", local = TRUE, print.eval = TRUE)
 
@@
 The difference in emissions from all GHGs to CO2 emissions highlights the importance to extend the frame of historic responsibility beyond CO2 emissions –  especially in light of growing capabilities, issue salience and data availability that all put greater responsibility recent emissions.
+
 Therefore, China now has a major responsibility to reduce emissions which is reinforced when considering that the country’s massive emissions growth only started after the adoption of the Kyoto Protocol in 1997, at a time when the consequences of climate change were already being heavily discussed.
+
 However, we also need to consider that China only ranks on 81st and 43rd place considering their GDP per capita and their emissions per capita, respectively.
@@
 China ranks first place in absolute emissions and GDP in 2019 with a great distance to subsequent ranks.
+
 Thus, China has one of the greatest responsibilities to reduce emissions from a historic emissions, current emissions and economic capacity perspective.
 
-# Discussion and Conclusion TBD
+# Discussion and Conclusion
 
@@
 Together with the EU-27 and the U.S., China should bear the highest responsibility for climate change mitigation.
-Its self-classification as a developing country is clearly politically motivated, to not give in to the demands of having to do more.
+Its self-classification as a developing country is clearly politically motivated, to not give-in to the demands of raising its ambition.
 At the same time, the political leadership in Beijing can present itself as a top student in the international community by effortlessly surpassing its own goals, as it is expected by different observers [@CAT2022].
@@
 Lastly, reducing capacity to mere GDP and GDP per capita considerations is very much simplifying the issue, as land area, access to renewable resources and intellectual property and many other factors determine a countries mitigation potential, which is very likely to differ by sector.
+
 With these limitations in mind, we believe none the less that our analysis has shed light on the special case of China and has shown that the under complex self-assessment does not withstand a thorough analysis.

### 2022-12-12 r-report/Paper.tex
zwischenstand

@@
 billion cubic meters until 2030 and have 1,200 GW of wind and solar
-power capacity installed by the same year \citep{China2022}. Although
+power capacity installed by the same year \citep{China2021}. Although
 some of these objectives are vague to some degree, and the emissions
@@
 be characterized as a developing nation. For this we compare China's
-Kaya identity with other developing and developed nations. Furthermore,
+Kaya Identity with other developing and developed nations. Furthermore,
 we consider China's sectoral emissions trends and contrast them with
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-1-1.pdf}
-\caption{Figure 1}
+\caption{Figure 1: Relative Emissions of the Top- 5 Polluters}
 \end{figure}
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-2-1.pdf}
-\caption{Figure 2}
+\caption{Figure 2: Total Emissions, China by Sector - 1970-2019}
 \end{figure}
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{Figure 3}
+\caption{Figure 3: Kaya Identity China - 2000 - 2019}
 \end{figure}
@@
 
-TO BE DONE: Intro statement.
+The following sections will detail our analysis with regard to the two
+research questions. We first turn to China's self-categorization as
+developing country and contrast it with different comparisons of
+development metrics as well as emission trends. After an interim
+discussion we will look at China's responsibility with regard to
+(projected) cumulative emissions and construct rankings for different
+equity metrics.
 
@@
 
-TO BE DONE FOrmula
+\[\text{GNI} = \text{GDP} + \left (\text{EX}_{FS} - \text{IM}_{FS} \right )\]
+
+whereas \(\text{GNI}\) be the gross national income, \(\text{GDP}\) be
+the gross domestic product, \(\text{EX}_{FS}\) be the money flowing
+from, and \(\text{IM}_{FS}\) the money flowing to foreign countries.
 
@@
 
-With a Kaya identity, one can identify the main driving forces of CO2
-emissions in a certain period. The Kaya identity expresses CO2 emissions
-(F) as a function of GDP (G), population (P) and energy (E):
-
-TO BE DONE FOrmula
-
-The term highlights the different components of the identity: G/P is GDP
-per capita, E/G is the energy intensity of GDP and F/E is the carbon
-intensity of energy \citep{Lamb2021}. By comparing Kaya identities of
-different regions, we can also discuss regional differences. Hence, we
-use the Kaya identity to discuss if the driving forces of emissions show
-similarities with developing or developed nations.
+With a Kaya Identity, one can identify the main driving forces of CO2
+emissions in a certain period. The Kaya Identity expresses CO2 emissions
+\(F\) as a function of GDP \(G\), population \(P\) and energy \(E\):
+
+\[F = P \: \frac{G}{P} \frac{E}{G} \frac{F}{E}\]
+
+whereas \(\frac{G}{P}\) represents GDP per capita, \(\frac{E}{G}\)
+represents the energy intensity of GDP and \(\frac{F}{E}\) represents
+the carbon intensity of energy \citep{Lamb2021}. By comparing Kaya
+identities of different regions, we can also discuss regional
+differences. Hence, we use the Kaya Identity to discuss if the driving
+forces of emissions show similarities with developing or developed
+nations.
 
@@
 
-Comparing China's Kaya identity to the decomposition of the development
+Comparing China's Kaya Identity to the decomposition of the development
 of CO2 emissions of developing and developed countries does not provide
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{Figure 4}
+\caption{Figure 4: Kaya Identities - 2000 - 2019\textbar{} China
+vs.~Developed and Developing according to AR\_6 Classification}
 \end{figure}
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{Figure 5}
+\caption{Figure 5:Kaya Identities - 2000 - 2019\textbar{} China
+vs.~Developed and Developing according to AR\_6 Classification}
 \end{figure}
@@
 
-\hypertarget{discussion}{%
-\subsubsection{Discussion}\label{discussion}}
+\hypertarget{section-summary}{%
+\subsubsection{Section Summary}\label{section-summary}}
 
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{Figure 10}
+\caption{Figure 10: Absolute GHG Emission - 2019 \textbar{} Top
+Emittters, China, US, EU-27 and reference for GDP, Emissions and
+Population}
 \end{figure}
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{Figure 11}
+\caption{Figure 11: Per Capita Emissions- 2019 \textbar{} Top Emittters,
+China, US, EU-27 and reference for GDP, Emissions and Population}
 \end{figure}
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{Figure 12}
+\caption{Figure 12: Absolute GDP p - 2019 \textbar{} Highes GDP
+Countries, China, US, EU-27 and reference for GDP, Emissions and
+Population}
 \end{figure}
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{Figure 13}
+\caption{Figure 13: GDP per Capita - 2019 \textbar{} Highes GDP
+Countries, China, US, EU-27 and reference for GDP, Emissions and
+Population}
 \end{figure}
 
-\hypertarget{discussion-tbd}{%
-\subsubsection{Discussion TBD}\label{discussion-tbd}}
+\hypertarget{section-summary-1}{%
+\subsubsection{Section Summary}\label{section-summary-1}}
 
@@
 considering some of the discussed equity metrics. Based on our
-calculations, China is likely surpass the EU well before 2030 and the US
-shortly after in 2032 in terms of cumulative emissions over all GHGs
+calculations, China is likely to surpass the EU well before 2030 and the
+US shortly after in 2032 in terms of cumulative emissions over all GHGs
 from 1850 to 2019 and a modeling of emissions thereafter. The difference
 in emissions from all GHGs to CO2 emissions highlights the importance to
-extend the frame of historic respon
+extend the frame of historic responsibility beyond CO2 emissions --
+especially in light of growing capabilities, issue salience and data
+availability that all put greater responsibility recent emissions.
 
@@
 
-However, we also need to consider that China only ranks on 81st. and
-43rd place considering their GDP per capita and their emissions per
-capita, respectively. This diminishes China's responsibility to some
-extent, showing that the global community needs to grant space for
-economic development to be fair. However, this economic development
-should ideally be decoupled from a growth in emissions. If we look at
-the per capita emissions of the countries that rank first, we see that
-these are mostly very small and, from the perspective of absolute
-emissions, less important countries. Although these countries might have
-a high ability to pay from a per capita perspective, their overall
-economic power is not high. The opposite is true for China. China ranks
-first place in absolute emissions and GDP in 2019 with a great distance
-to the following places.
+However, we also need to consider that China only ranks on 81st and 43rd
+place considering their GDP per capita and their emissions per capita,
+respectively. This diminishes China's responsibility to some extent,
+showing that the global community needs to grant space for economic
+development to be fair. However, this economic development should
+ideally be decoupled from a growth in emissions. If we look at the per
+capita emissions of the countries that rank first, we see that these are
+mostly very small and, from the perspective of absolute emissions, less
+important countries. Although these countries might have a high ability
+to pay from a per capita perspective, their overall economic power is
+not high. The opposite is true for China. China ranks first place in
+absolute emissions and GDP in 2019 with a great distance to subsequent
+ranks.
 
@@
 
-\hypertarget{discussion-and-conclusion-tbd}{%
-\section{Discussion and Conclusion
-TBD}\label{discussion-and-conclusion-tbd}}
+\hypertarget{discussion-and-conclusion}{%
+\section{Discussion and Conclusion}\label{discussion-and-conclusion}}
 
@@
 emissions, but also the financial capability to do so. The country is
-the world's largest emitter in annual and cumulative terms (based on our
-data) and has the highest GDP of all countries. While it is important to
-acknowledge further room for development, one cannot disregard the fact
-that without significant emission reductions from China, any attempt to
-stay within the temperature limits of the Paris Agreement is sure to
-fail.
+the world's largest emitter in annual terms , on a pathway to take the
+first position in cumulative terms within a decade and has the highest
+GDP of all countries. While it is important to acknowledge the need for
+further economic development, one cannot disregard the fact that without
+significant emission reductions from China, any attempt to stay within
+the temperature limits of the Paris Agreement is sure to fail.
 
@@
 self-classification as a developing country is clearly politically
-motivated, to not give in to the demands of having to do more. At the
+motivated, to not give-in to the demands of raising its ambition. At the
 same time, the political leadership in Beijing can present itself as a
@@
 In the following, our analysis will be contrasted with two other
-assessments of China's fair share -- the assessment by the Climate
+assessments of China's responsibility -- the assessment by the Climate
 Action Tracker and by the Climate Equity Monitor.
@@
 annual emissions of a country are calculated for the period from 1850 to
-2019. Based on this, the Climate Equity Monitor calculates if a country
-has a carbon debt or carbon credit. This measure is calculated as the
-difference between cumulative emissions of a country and the country's
-fair share of the global carbon budget already consumed. For China as a
-Non-Annex 1 country, they conclude that the country has a carbon credit
-of 122.4 Gt CO2eq. In comparison, India has a carbon credit of 337.6 Gt
-CO2eq while the US has a carbon debt of 445 Gt CO2eq, and Russia has a
-carbon debt of 125.44 Gt CO2eq \citep{CEM2022}. Accordingly, if China
-kept emitting at its current rate, it would have used up its remaining
-carbon credit until 2031.
+2019. Based on this, the Climate Equity Monitor calculates whether a
+country has a carbon debt or carbon credit. This measure is calculated
+as the difference between cumulative emissions of a country and the
+country's fair share of the global carbon budget already consumed. For
+China as a Non-Annex 1 country, they conclude that the country has a
+carbon credit of 122.4 Gt CO2eq. In comparison, India has a carbon
+credit of 337.6 Gt CO2eq while the US has a carbon debt of 445 Gt CO2eq,
+and Russia has a carbon debt of 125.44 Gt CO2eq \citep{CEM2022}.
+Accordingly, if China kept emitting at its current rate, it would have
+used up its remaining carbon credit until 2031.
 
@@
 
-Our analysis has the following limitations: We only consider cumulative
-emissions from 1850-2019, but the consideration of other time periods
-could also be conceivable. The problem of climate change caused by
-anthropogenic greenhouse gas emissions has only been known since the
-1970s, and since the 1990s there has been a dedicated international
-process to address the problem. Against this background, an additional
-consideration of cumulative emissions in these time periods might be
-worthwhile. For a comprehensive assessment of China's fair share, it
-would have also been interesting to discuss further equity metrics such
-as a ranking of consumption-based emissions. However, this was not
-possible for us, as our data only included consumption-based data for
-approx. 100 countries and crucially missing the US, making a comparison
-less meaningful.
+While aiming to be as comprehensive as possible our analysis has some
+limitations. First, we only consider cumulative emissions from
+1850-2019, but the consideration of other time periods could also be
+conceivable. The problem of climate change caused by anthropogenic
+greenhouse gas emissions has only been known since the 1970s, and since
+the 1990s there has been a dedicated international process to address
+the problem. Against this background, an additional consideration of
+cumulative emissions in these time periods might be worthwhile. Second,
+the projection of future emissions rests on major simplification
+assumptions, it is likely that a more sophisticated approach such as an
+ARIMA-modelling would result in more robust estimates. Third, a
+comprehensive assessment of China's responsibility could discuss further
+equity metrics such as a ranking of consumption-based emissions.
+However, this was not possible for us, as our data only included
+consumption-based data for approx. 100 countries and crucially missing
+the US, making a comparison less meaningful. Lastly, reducing capacity
+to mere GDP and GDP per capita considerations is very much simplifying
+the issue, as land area, access to renewable resources and intellectual
+property and many other factors determine a countries mitigation
+potential, which is very likely to differ by sector.
+
+With these limitations in mind, we believe none the less that our
+analysis has shed light on the special case of China and has shown that
+the under complex self-assessment does not withstand a thorough
+analysis. Keeping these assessments in mind will be worthwhile when
+assessing the responsibilities of upcoming developing nations. The case
+of China has shown that it is crucial to come to a mutual understanding
+of what constitutes responsibilities and how they can assessed on an
+objective basis. Especially our analysis of future cumulative emissions
+indicates that it will be key to frame the issue beyond CO2.
 
@@
     proxy~0.4-27, quadprog~1.5-8, quantmod~0.4.20, R6~2.5.1,
-    Rcpp~1.0.9, RefManageR~1.4.0, regions~0.1.8, reprex~2.0.2,
-    rlang~1.0.5, rmarkdown~2.16, rprojroot~2.0.3, rstudioapi~0.14,
-    rvest~1.0.3, scales~1.2.1, stinepack~1.4, stringi~1.7.8,
-    svglite~2.1.0, systemfonts~1.0.4, tidyselect~1.1.2,
+    RColorBrewer~1.1-3, Rcpp~1.0.9, RefManageR~1.4.0, regions~0.1.8,
+    reprex~2.0.2, rlang~1.0.5, rmarkdown~2.16, rprojroot~2.0.3,
+    rstudioapi~0.14, rvest~1.0.3, scales~1.2.1, stinepack~1.4,
+    stringi~1.7.8, svglite~2.1.0, systemfonts~1.0.4, tidyselect~1.1.2,
     timeDate~4021.104, tools~4.2.1, tseries~0.10-52, TTR~0.24.3,

### 2022-12-12 r-analysis/data_sectors_bycountry.R

@@ -14,7 +14,7 @@ PDATA$data_abs = data_base %>%
 PDATA$data_rel = data_base %>%
   filter(country == {{COUNTRY}}) %>%
   rename(GAS := {{GAS}}) %>%
-  mutate(GAS = GAS*1e6)
+  mutate(GAS = GAS*1e6) %>%
   group_by(year,sector_title) %>%
   summarise(GAS_s=sum(GAS,na.rm=TRUE)) %>%
   na.omit() %>%

### 2022-12-12 r-imports/init.R

@@ -48,8 +48,9 @@ theme_ghg = function(){
   
   theme_minimal() %+replace%    #replace elements we want to change
     
-    # theme(plot.title =element_blank(),
-    #     plot.subtitle = element_blank()
+     theme(
+     #  plot.title =element_blank(),
+    #   plot.subtitle = element_blank()
     #   
       # #grid elements
       # panel.grid.major = element_blank(),    #strip major gridlines

### 2022-12-12 r-plots/Plot_Rank_abs.R

@@ -32,7 +32,7 @@ PDATA$p_abs <- PDATA$data_base_lp_abs %>%
   ylab("GHG Emissions, (Mt. CO2 eq)") +
   ggtitle("Responsibility 1: Absolute Emissions Ranking 2019", subtitle = "Top Emitters, China, US, EU-27 & Reference for GDP, Population and Emissions")
 
-PDATA$p_abs + annotate("text", x=(which(fct_inorder(PDATA$p_an_abs)==PDATA$ghg_50_abs$country)), y=PDATA$data_base_lp_abs$y[2]*0.8, 
+OUT = PDATA$p_abs + annotate("text", x=(which(fct_inorder(PDATA$p_an_abs)==PDATA$ghg_50_abs$country)), y=PDATA$data_base_lp_abs$y[2]*0.8, 
                       label=" ~50 % of global emissions", 
                       color="black", size=2.5 , angle=0, fontface="italic", vjust =0.4, hjust=-0) +
   annotate("text", x=(which(fct_inorder(PDATA$p_an_abs)==PDATA$gdp_50_abs$country)), y=PDATA$data_base_lp_abs$y[2]*0.8, 
@@ -42,7 +42,4 @@ PDATA$p_abs + annotate("text", x=(which(fct_inorder(PDATA$p_an_abs)==PDATA$ghg_5
   annotate("text", x=(which(fct_inorder(PDATA$p_an_abs)==PDATA$pop_50_abs$country)), y=PDATA$data_base_lp_abs$y[2]*0.8, 
            label=" ~50 % of global Population", 
            color="black", size=2.5 , angle=0, fontface="italic", vjust =0.4, hjust=0,) 
-
-PDATA$p_an_abs          
-PDATA$p_abs 
-fct_inorder(PDATA$p_an_abs)
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_cumulative_china_2030.R

@@ -11,3 +11,4 @@ OUT = PDATA$data_cumulative_2030 %>%
   geom_vline(aes(xintercept = PDATA$is_us[meta_gas_alc[GAS]],color="United States"), show.legend = NA, linetype = "dotted",size=.2) +
   geom_vline(aes(xintercept = PDATA$is_eu[meta_gas_alc[GAS]],color="EU-27"), show.legend = NA,linetype = "dotted",size=.2) +
   scale_x_continuous(breaks=c(seq(1750,2050,by=50),PDATA$is_eu[meta_gas_alc[GAS]],PDATA$is_us[meta_gas_alc[GAS]]))
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_cumulative_china_2040.R

@@ -11,3 +11,4 @@ OUT = PDATA$data_cumulative_2040 %>%
   geom_vline(aes(xintercept = PDATA$is_us[meta_gas_alc[GAS]],color="United States"), show.legend = NA, linetype = "dotted",size=.2) +
   geom_vline(aes(xintercept = PDATA$is_eu[meta_gas_alc[GAS]],color="EU-27"), show.legend = NA,linetype = "dotted",size=.2) +
   scale_x_continuous(breaks=c(seq(1750,2050,by=50),PDATA$is_eu[meta_gas_alc[GAS]],PDATA$is_us[meta_gas_alc[GAS]]))
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_facet_incomelevels_sectors_yemission_stacked_rel.R

@@ -1,4 +1,4 @@
-PDATA$data_inc_rel %>%
+OUT = PDATA$data_inc_rel %>%
 #  filter(region==c(COUNTRY, "Developed","Developing")) %>% #line breaks
   ggplot( aes(x = dev_status_income,y=GAS_s_perc, fill=sector_title)) +
   geom_bar(position="stack", stat="identity") +
@@ -12,4 +12,4 @@ PDATA$data_inc_rel %>%
   geom_text(aes(label = round(GAS_s_perc)), position = position_stack(vjust = 0.5), size = 3) +
   guides(fill =guide_legend("Sector"))+
   ggtitle("Relative Emissions " %.% COUNTRY %.% " vs. Income Levels , by Sector, " %.% YEAR)
-
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_facet_regions_sectors_yemission_stacked_rel.R

@@ -1,4 +1,4 @@
-PDATA$data_rel %>%
+OUT = PDATA$data_rel %>%
 #  filter(region==c(COUNTRY, "Developed","Developing")) %>% #line breaks
   ggplot( aes(x = region,y=GAS_s_perc, fill=sector_title)) +
   geom_bar(position="stack", stat="identity") +
@@ -11,3 +11,4 @@ PDATA$data_rel %>%
   geom_text(aes(label = round(GAS_s_perc)), position = position_stack(vjust = 0.5), size = 3) +
   guides(fill =guide_legend("Sector"))+
   ggtitle("Relative Emissions " %.% COUNTRY %.% " vs. Developed/Developing Countries, by Sector, " %.% YEAR)
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_forecast.R

@@ -9,3 +9,4 @@ OUT = PDATA$data_comb %>%
   theme_ghg()+
   theme(axis.title.x = element_blank(),axis.text.y=element_blank(),legend.position = "none") +
   ggtitle("Total Emissions and Forecast, China vs. EU vs. US, by Sector, " %.% YEAR_L %.% "-" %.% FYEAR_U)
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_forecast_delta.R

@@ -9,3 +9,4 @@ OUT = PDATA$data_comb %>%
   theme_ghg()+
   theme(axis.title.x = element_blank(),axis.text.y=element_blank(),legend.position = "none") +
   ggtitle("Change in Total Emissions and Forecast, China vs. EU vs. US, by Sector, " %.% YEAR_L %.% "-" %.% FYEAR_U)
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_kaya_chn.R

@@ -21,5 +21,3 @@ OUT<-PDATA$kaya_incomelevels %>%
         axis.title.x = element_blank(),
         axis.title.y = element_blank())
 if(DIRECT_PLOTTING) plot(OUT)
-
-OUT

### 2022-12-12 r-plots/plot_rank_pc.R

@@ -32,7 +32,7 @@ PDATA$p_pc <- PDATA$data_base_lp_pc %>%
   ylab("Per Capita GHG Emissions, (Mt. CO2 eq)") +
   ggtitle("Responsibility 3: Per Capita Emissions Ranking", subtitle = "Top Emitters, China, US, EU-27 & Reference for GDP, Population and Emissions")
 
-PDATA$p_pc + annotate("text", x=(which(fct_inorder(PDATA$p_an_pc)==PDATA$ghg_50_pc$country)), y=PDATA$data_base_lp_pc$y[9]*0.8, 
+OUT = PDATA$p_pc + annotate("text", x=(which(fct_inorder(PDATA$p_an_pc)==PDATA$ghg_50_pc$country)), y=PDATA$data_base_lp_pc$y[9]*0.8, 
                        label=" ~50 % of global emissions", 
                        color="black", size=2.5 , angle=0, fontface="italic", vjust =0.4, hjust=-0) +
   annotate("text", x=(which(fct_inorder(PDATA$p_an_pc)==PDATA$gdp_50_pc$country)), y=PDATA$data_base_lp_pc$y[3]*0.8, 
@@ -42,9 +42,4 @@ PDATA$p_pc + annotate("text", x=(which(fct_inorder(PDATA$p_an_pc)==PDATA$ghg_50_
   annotate("text", x=(which(fct_inorder(PDATA$p_an_pc)==PDATA$pop_50_pc$country)), y=PDATA$data_base_lp_pc$y[9]*0.8, 
            label=" ~50 % of global Population", 
            color="black", size=2.5 , angle=0, fontface="italic", vjust =0.4, hjust=0,) 
-
-PDATA$p_an_pc          
-PDATA$p_pc 
-fct_inorder(PDATA$p_an_pc)
-
-
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_sectors_bycountry_stacked_abs.R

@@ -1,4 +1,4 @@
-PDATA$data_abs %>% 
+OUT = PDATA$data_abs %>% 
   ggplot(aes(x=year,y=GAS_s,fill=sector_title)) +
   geom_area(color="#636363") +
   theme_bw() +
@@ -8,3 +8,4 @@ PDATA$data_abs %>%
   theme(axis.title.x=element_blank()) +
   guides(fill=guide_legend(title="Sectors"))+
   ggtitle("Total Emissions, " %.% COUNTRY %.% ", by Sector, " %.% YEAR_L %.% "-" %.% YEAR_U)
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_sectors_bycountry_stacked_rel.R

@@ -1,4 +1,4 @@
-PDATA$data_rel %>% 
+OUT = PDATA$data_rel %>% 
   ggplot(aes(x=year,y=GAS_s_perc,fill=sector_title)) +
   geom_area(color="#636363") +
   theme_bw() +
@@ -7,3 +7,4 @@ PDATA$data_rel %>%
   theme_ghg()+
   theme(axis.title.x=element_blank()) +
   ggtitle("Relative Emissions, " %.% COUNTRY %.% ", by Sector, " %.% YEAR_L %.% "-" %.% YEAR_U)
+if(DIRECT_PLOTTING) plot(OUT)

### 2022-12-12 r-plots/plot_single_polluters_stacked_rel.R

@@ -10,5 +10,3 @@ OUT = PDATA$data_rel %>%
   guides(fill = guide_legend("Region") )+
   ggtitle("Relative Emissions of the Top- 5 Polluters " %.% YEAR_L %.% "-" %.% YEAR_U)
 if(DIRECT_PLOTTING) plot(OUT)
-  
-

### 2022-12-12 r-plots/plot_sectors_bycountry_stacked_rel.R
Fixed stacked graphic

@@ -7,4 +7,6 @@ OUT = PDATA$data_rel %>%
   theme_ghg()+
   theme(axis.title.x=element_blank()) +
   ggtitle("Relative Emissions, " %.% COUNTRY %.% ", by Sector, " %.% YEAR_L %.% "-" %.% YEAR_U)
+
 if(DIRECT_PLOTTING) plot(OUT)
+o

### 2022-12-12 r-report/Paper.Rmd
fixes

@@
 options(knitr.kable.NA = '',knitr.table.format = "latex")
-#knitr::read_chunk('r-report/Paper.R')
+knitr::read_chunk('r-report/Paper.R')
 library(kableExtra)
@@
 
-```{r setup-ex}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-theme_ghg = function(){ 
-  theme_minimal() %+replace%
-     theme(
-       plot.title =element_blank(),
-       plot.subtitle = element_blank()
-    )
-}
-DIRECT_PLOTTING = F
+```{r init}
 ```
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
 YEAR_L = 1970
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
 YEAR_L = 1970
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
 YEAR_L = 2000
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
 YEAR_L = 2000
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
 YEAR_L = 2000
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 6"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
-YEAR = 1950
+YEAR = 2019
 GAS = "GHG"
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 7"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
-YEAR = 1950
+YEAR = 2019
 GAS = "GHG"
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 8"}
-YEAR_L = 1850
-YEAR_U = 2060
+YEAR_L = 1970
+YEAR_U = 2019
 GAS = "GHG"
+COUNTRY = "China"
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_sector_incomelevel.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_facet_incomelevels_sectors_emissions.R", local = TRUE, print.eval = TRUE)
 
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 9"}
+YEAR_L = 1970
+YEAR_U = 2019
+FYEAR_L = c(2025,2030,2030,2035,2040)
+FYEAR_U = c(2060,2060,2055,2065,2065)
+FYEAR_US = 2050
+FYEAR_EU = 2050
+GAS = "GHG"
+
+source("r-analysis/forecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_forecast.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r,fig.cap="Figure 10"}
+source("r-plots/plot_forecast_delta.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r init}
+```
+```{r,fig.cap="Figure 11"}
 YEAR_L = 1850
@@
 source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r,fig.cap="Figure 12"}
+source("r-plots/plot_cumulative_china_2040.R", local = TRUE, print.eval = TRUE)
 
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 10: Absolute GHG Emission - 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 11: Per Capita Emissions- 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 12: Absolute GDP p - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
@@
 
+```{r init}
+```
 ```{r,fig.cap="Figure 13: GDP per Capita - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}

### 2022-12-12 r-report/Paper.Rmd
Updated figures

--- 2022-12-12 r-report/Paper.Rmd
@@
 In 2019, more than 25% of all global greenhouse gas emissions came from China, more than the U.S.
-and (at the time still) EU-28 combined (see Figure 1).
+and (at the time still) EU-28 combined (see Figure 1.1).
 As a consequence of this development, China's emissions profile changed dramatically: While the agricultural sector still accounted for a large share of emissions in the early 1970s, its contribution has been only marginal in recent years.
-Figure 2 shows the large-scale industrialization of the country starting in the mid-1990s and the corresponding increase in emissions from the energy sector.
+Figure 1.2 shows the large-scale industrialization of the country starting in the mid-1990s and the corresponding increase in emissions from the energy sector.
 More recently, transport sector emissions have picked up speed, likely reflecting the wealthy share of China’s citizens spending more money on individual (fossil-fuel based) modes of transport.
@@
 Chinese carbon emissions growth was predominantly driven by its rapid economic development, which in turn caused the energy sector to grow too.
-Since the year 2000, China's GDP per capita has more than quadrupled, while carbon emissions have more than tripled in the same period (see Figure 3).
+Since the year 2000, China's GDP per capita has more than quadrupled, while carbon emissions have more than tripled in the same period (see Figure 1.3).
 However, the growth of emissions has slowed in recent years, as energy intensity of GDP had started decreasing after the year 2005 and also carbon intensity of energy peaked in 2010 and has been slowly decreasing since.
@@
 
-```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
+```{r,fig.cap="Relative Emissions of the Top- 5 Polluters"}
 source('r-imports/init.R')
@@
 
-```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
+```{r,fig.cap="Total Emissions, China by Sector - 1970-2019"}
 source('r-imports/init.R')
@@
 
-```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
+```{r,fig.cap="Kaya Identity China - 2000 - 2019"}
 source('r-imports/init.R')
@@
 
-Figure 4 displays China’s and developing and developed countries’ Kaya identities according to the IPCC classification in the Sixth Assessment Report from 2000 to 2019.
+Figure 3.1 displays China’s and developing and developed countries’ Kaya identities according to the IPCC classification in the Sixth Assessment Report from 2000 to 2019.
 In those years, China’s GDP per capita was growing with a factor close to five, thereby being the strongest upward driver of emissions.
@@
 
-```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
+```{r,fig.cap="Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
 source('r-imports/init.R')
@@
 
-Thus, in the next steps, the World Bank’s Income Classification Scheme will be used for comparison (Figure 5).
+Thus, in the next steps, the World Bank’s Income Classification Scheme will be used for comparison (Figure 3.2).
 In high-income countries, GDP per capita and population are increasing only at low levels (by roughly the factor 0.5 and 0.2 respectively).
@@
 
-```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
+```{r,fig.cap="Kaya Identities - 2000 - 2019| China vs. Income Levels"}
 source('r-imports/init.R')
@@
 We take into account five sectors: energy, industry, transport, AFOLU (which in the EDGAR database only includes agricultural emissions), and buildings.
-China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 6 & 7.
-Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively.
+China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 3.3 & 3.4 Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively.
 Only smaller shares are attributable to transport (6%), buildings (5%) and AFOLU (6%).
@@
 
-```{r,fig.cap="Figure 6"}
+```{r,fig.cap="Relative sector Emissions-2019| China vs. Developed vs. Developing"}
 source('r-imports/init.R')
@@
 
-As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 7).
+As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 3.5).
 
@@
 
-```{r,fig.cap="Figure 7"}
+```{r,fig.cap="Relative sector Emissions - 2019| China vs. Income Levels"}
 source('r-imports/init.R')
@@
 
-As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 8).
+As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 3.6).
 
@@
 
-```{r,fig.cap="Figure 8"}
+```{r,fig.cap="1970-2019| China vs. Income Levels"}
 YEAR_L = 1850

### 2022-12-13 r-report/Paper.Rmd
final

@@
 
-```{r,fig.cap="Relative Emissions of the Top- 5 Polluters"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
+```{r init}
+```
+```{r,fig.cap="Relative Emissions of the Top-5 Polluters"}
 YEAR_L = 1970
@@
 
-```{r,fig.cap="Total Emissions, China by Sector - 1970-2019"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
+```{r init}
+```
+```{r,fig.cap="Total Emissions, China, by Sector, 1970-2019"}
 YEAR_L = 1970
@@
 
-```{r,fig.cap="Kaya Identity China - 2000 - 2019"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
+```{r init}
+```
+```{r,fig.cap="Kaya Identity, China, 2000-2019"}
 YEAR_L = 2000
@@
 
-```{r,fig.cap="Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
+```{r init}
+```
+```{r,fig.cap="Kaya Identities, 2000-2019, China vs. Developed/Developing according to AR_6 Classification"}
 YEAR_L = 2000
@@
 
-```{r,fig.cap="Kaya Identities - 2000 - 2019| China vs. Income Levels"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
+```{r init}
+```
+```{r,fig.cap="Kaya Identities, 2000-2019, China vs. Developed and Developing according to AR_6 Classification"}
 YEAR_L = 2000
@@
 We take into account five sectors: energy, industry, transport, AFOLU (which in the EDGAR database only includes agricultural emissions), and buildings.
-China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 3.3 & 3.4 Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively.
+China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 3.3 & 3.4.
+Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively.
 Only smaller shares are attributable to transport (6%), buildings (5%) and AFOLU (6%).
@@
 
-```{r,fig.cap="Relative sector Emissions-2019| China vs. Developed vs. Developing"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
-YEAR = 1950
+```{r init}
+```
+```{r,fig.cap="Relative Sector Emissions, 2019, China vs. Developed/Developing according to AR_6 Classification"}
+YEAR = 2019
 GAS = "GHG"
@@
 
-As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 3.5).
+As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 3.4).
 
@@
 
-```{r,fig.cap="Relative sector Emissions - 2019| China vs. Income Levels"}
-source('r-imports/init.R')
-source('r-analysis/meta.R')
-
-YEAR = 1950
+```{r init}
+```
+```{r,fig.cap="Relative Sector Emissions, 2019, China vs. Countries classified by Income Levels"}
+YEAR = 2019
 GAS = "GHG"
@@
 
-As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 3.6).
+As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 3.5).
 
@@
 
-```{r,fig.cap="1970-2019| China vs. Income Levels"}
-YEAR_L = 1850
-YEAR_U = 2060
+```{r init}
+```
+```{r,fig.cap="Per Capita Emissions, by Sector, 1970-2019, China vs. Countries classified by Income Levels"}
+YEAR_L = 1970
+YEAR_U = 2019
 GAS = "GHG"
+COUNTRY = "China"
 
-source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_sector_incomelevel.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_facet_incomelevels_sectors_emissions.R", local = TRUE, print.eval = TRUE)
 
@@
 
-The resulting sectoral emissions pathways for each country/region are depicted in figure xx.
-The resulting cumulative emissions forecasts for the three countries/blocks are shown in figure xx.
+The resulting sectoral emissions pathways for each country/region are depicted in Figure 3.6, with change rates being displayed in Figure 3.7.
+The resulting cumulative emissions forecasts for the three countries/blocks are shown in Figure 3.8.
 Accordingly, China will pass the EU-27 in cumulative GHG emissions in 2027 and is projected to pass the U.S.
-in 2032 .
+in 2032.
 Afterwards it will be the largest cumulative emitter.
 
-These projections hold even when modelling each sector according to the Chinese NDC (assuming peak years of 2030 and zero emissions by 2060).
+These projections hold even when modelling each sector according to the Chinese NDC (assuming peak years of 2030 and zero emissions by 2060, see Figure 3.9 for comparison).
 In the NDC-scenario China will surpass the EU and US respectively in the same years as modeled in our main scenarios, but at different emission levels – 452.4 GtCO2eq (main scenario)  451.8 GtCO2eq (NDC-scenario).
@@
 
-```{r,fig.cap="Figure 9"}
+```{r init}
+```
+```{r,fig.cap="GHG Emissions Forecast, China vs. EU vs. US"}
+YEAR_L = 1970
+YEAR_U = 2019
+FYEAR_L = c(2025,2030,2030,2035,2040)
+FYEAR_U = c(2060,2060,2055,2065,2065)
+FYEAR_US = 2050
+FYEAR_EU = 2050
+GAS = "GHG"
+
+source("r-analysis/forecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_forecast.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r,fig.cap="GHG Emissions Forecast, China vs. EU vs. US"}
+source("r-plots/plot_forecast_delta.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r init}
+```
+```{r,fig.cap="Projected Cumulative Emissions, China, NDC Scenario"}
 YEAR_L = 1850
@@
 source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2040.R", local = TRUE, print.eval = TRUE)
+
+plot(OUT)
+```
+
+```{r,fig.cap="Projected Cumulative Emissions, China, Main Scenario"}
 source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
@@
 
-First, we consider China’s responsibility based on absolute emissions in the year 2019 (Figure X).
+First, we consider China’s responsibility based on absolute emissions in the year 2019 (Figure 3.10).
 In the ranking, China ranks on first place with absolute emissions of 14,219.37 Mt CO2 eq.
@@
 
-```{r,fig.cap="Figure 10: Absolute GHG Emission - 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
+```{r init}
+```
+```{r,fig.cap="Absolute GHG Emissions, 2019, Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
 YEAR_L = 1850
@@
 
-Next, we consider emissions per capita (Figure x).
+Next, we consider emissions per capita (Figure 3.11).
 This is important as China is the country with the biggest population worldwide of approx.
@@
 
-```{r,fig.cap="Figure 11: Per Capita Emissions- 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
+```{r init}
+```
+```{r,fig.cap="Per Capita GHG Emissions, 2019, Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
 YEAR_L = 1850
@@
 Considering GDP and GDP per capita refers to the capacity of acting on climate change, following the assumption that richer countries have more resources available to fight climate change.
-As Figure XX shows, China had the highest GDP of all countries in 2019, with USD 22.49 trillion.
-Based on this, China would theoretically have to make the greatest conribution to reduce emissions.
+As Figure 3.12 shows, China had the highest GDP of all countries in 2019, with USD 22.49 trillion.
+Based on this, China would theoretically have to make the greatest contribution to reduce emissions.
 Absolute GDP, however, is limited in telling us about a country's actual capacity because it ignores population size.
@@
 
-```{r,fig.cap="Figure 12: Absolute GDP p - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
+```{r init}
+```
+```{r,fig.cap="Absolute GDP 2019, Countries with highest GDP, China, US, EU-27 and reference for GDP, Emissions and Population"}
 YEAR_L = 1850
@@
 
-```{r,fig.cap="Figure 13: GDP per Capita - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
+```{r init}
+```
+```{r,fig.cap="GDP per Capita 2019, Countries with highest GDP, China, US, EU-27 and reference for GDP, Emissions and Population"}
 YEAR_L = 1850

### 2022-12-13 r-report/Paper.tex
final

@@
 than 25\% of all global greenhouse gas emissions came from China, more
-than the U.S. and (at the time still) EU-28 combined (see Figure 1). As
-a consequence of this development, China's emissions profile changed
+than the U.S. and (at the time still) EU-28 combined (see Figure 1.1).
+As a consequence of this development, China's emissions profile changed
 dramatically: While the agricultural sector still accounted for a large
 share of emissions in the early 1970s, its contribution has been only
-marginal in recent years. Figure 2 shows the large-scale
+marginal in recent years. Figure 1.2 shows the large-scale
 industrialization of the country starting in the mid-1990s and the
@@
 quadrupled, while carbon emissions have more than tripled in the same
-period (see Figure 3). However, the growth of emissions has slowed in
+period (see Figure 1.3). However, the growth of emissions has slowed in
 recent years, as energy intensity of GDP had started decreasing after
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-1-1.pdf}
-\caption{Figure 1: Relative Emissions of the Top- 5 Polluters}
+\caption{Relative Emissions of the Top-5 Polluters}
 \end{figure}
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-2-1.pdf}
-\caption{Figure 2: Total Emissions, China by Sector - 1970-2019}
+\caption{Total Emissions, China, by Sector, 1970-2019}
 \end{figure}
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{Figure 3: Kaya Identity China - 2000 - 2019}
+\caption{Kaya Identity, China, 2000-2019}
 \end{figure}
@@
 
-Figure 4 displays China's and developing and developed countries' Kaya
+Figure 3.1 displays China's and developing and developed countries' Kaya
 identities according to the IPCC classification in the Sixth Assessment
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{Figure 4: Kaya Identities - 2000 - 2019\textbar{} China
-vs.~Developed and Developing according to AR\_6 Classification}
+\caption{Kaya Identities, 2000-2019, China vs.~Developed/Developing
+according to AR\_6 Classification}
 \end{figure}
@@
 Thus, in the next steps, the World Bank's Income Classification Scheme
-will be used for comparison (Figure 5). In high-income countries, GDP
+will be used for comparison (Figure 3.2). In high-income countries, GDP
 per capita and population are increasing only at low levels (by roughly
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{Figure 5:Kaya Identities - 2000 - 2019\textbar{} China
-vs.~Developed and Developing according to AR\_6 Classification}
+\caption{Kaya Identities, 2000-2019, China vs.~Developed and Developing
+according to AR\_6 Classification}
 \end{figure}
@@
 buildings. China's relative GHG emissions by sector are presented in a
-stacked bar plot in Figure 6 \& 7. Most of China's emissions in 2019
+stacked bar plot in Figure 3.3 \& 3.4. Most of China's emissions in 2019
 came from the energy and industry sector with 44\% and 38\%
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{Figure 6}
+\caption{Relative Sector Emissions, 2019, China vs.~Developed/Developing
+according to AR\_6 Classification}
 \end{figure}
@@
 As before, to get a more granular view on the split of emissions by
-sector, the World Bank's classification will be consulted (Figure 7).
+sector, the World Bank's classification will be consulted (Figure 3.4).
 
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{Figure 7}
+\caption{Relative Sector Emissions, 2019, China vs.~Countries classified
+by Income Levels}
 \end{figure}
@@
 China's per capita emissions by sector over time from 1970 to 2019 to
-those of our four income determined country groups (Figure 8).
+those of our four income determined country groups (Figure 3.5).
 
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{Figure 8}
+\caption{Per Capita Emissions, by Sector, 1970-2019, China vs.~Countries
+classified by Income Levels}
 \end{figure}
@@
 The resulting sectoral emissions pathways for each country/region are
-depicted in figure xx. The resulting cumulative emissions forecasts for
-the three countries/blocks are shown in figure xx. Accordingly, China
-will pass the EU-27 in cumulative GHG emissions in 2027 and is projected
-to pass the U.S. in 2032 . Afterwards it will be the largest cumulative
-emitter.
+depicted in Figure 3.6, with change rates being displayed in Figure 3.7.
+The resulting cumulative emissions forecasts for the three
+countries/blocks are shown in Figure 3.8. Accordingly, China will pass
+the EU-27 in cumulative GHG emissions in 2027 and is projected to pass
+the U.S. in 2032. Afterwards it will be the largest cumulative emitter.
 
 These projections hold even when modelling each sector according to the
-Chinese NDC (assuming peak years of 2030 and zero emissions by 2060). In
-the NDC-scenario China will surpass the EU and US respectively in the
-same years as modeled in our main scenarios, but at different emission
-levels -- 452.4 GtCO2eq (main scenario) 451.8 GtCO2eq (NDC-scenario).
-When projecting only CO2 emission developments1 China will surpass the
-EU in 2031 and the US in 2038 according to both scenarios.
+Chinese NDC (assuming peak years of 2030 and zero emissions by 2060, see
+Figure 3.9 for comparison). In the NDC-scenario China will surpass the
+EU and US respectively in the same years as modeled in our main
+scenarios, but at different emission levels -- 452.4 GtCO2eq (main
+scenario) 451.8 GtCO2eq (NDC-scenario). When projecting only CO2
+emission developments1 China will surpass the EU in 2031 and the US in
+2038 according to both scenarios.
 
@@
 \includegraphics{Paper_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{Figure 9}
+\caption{GHG Emissions Forecast, China vs.~EU vs.~US}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{GHG Emissions Forecast, China vs.~EU vs.~US}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{Projected Cumulative Emissions, China, NDC Scenario}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{Projected Cumulative Emissions, China, Main Scenario}
 \end{figure}
@@
 First, we consider China's responsibility based on absolute emissions in
-the year 2019 (Figure X). In the ranking, China ranks on first place
+the year 2019 (Figure 3.10). In the ranking, China ranks on first place
 with absolute emissions of 14,219.37 Mt CO2 eq. This is more than double
@@
 \centering
-\includegraphics{Paper_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{Figure 10: Absolute GHG Emission - 2019 \textbar{} Top
-Emittters, China, US, EU-27 and reference for GDP, Emissions and
-Population}
-\end{figure}
-
-Next, we consider emissions per capita (Figure x). This is important as
-China is the country with the biggest population worldwide of approx.
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{Absolute GHG Emissions, 2019, Top Emittters, China, US, EU-27
+and reference for GDP, Emissions and Population}
+\end{figure}
+
+Next, we consider emissions per capita (Figure 3.11). This is important
+as China is the country with the biggest population worldwide of approx.
 1.4 billion people \citep{WorldBank2022c}. Looking at this ranking, it
@@
 \centering
-\includegraphics{Paper_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{Figure 11: Per Capita Emissions- 2019 \textbar{} Top Emittters,
-China, US, EU-27 and reference for GDP, Emissions and Population}
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-14-1.pdf}
+\caption{Per Capita GHG Emissions, 2019, Top Emittters, China, US, EU-27
+and reference for GDP, Emissions and Population}
 \end{figure}
@@
 climate change, following the assumption that richer countries have more
-resources available to fight climate change. As Figure XX shows, China
+resources available to fight climate change. As Figure 3.12 shows, China
 had the highest GDP of all countries in 2019, with USD 22.49 trillion.
 Based on this, China would theoretically have to make the greatest
-conribution to reduce emissions. Absolute GDP, however, is limited in
+contribution to reduce emissions. Absolute GDP, however, is limited in
 telling us about a country's actual capacity because it ignores
@@
 \centering
-\includegraphics{Paper_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{Figure 12: Absolute GDP p - 2019 \textbar{} Highes GDP
-Countries, China, US, EU-27 and reference for GDP, Emissions and
-Population}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Paper_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{Figure 13: GDP per Capita - 2019 \textbar{} Highes GDP
-Countries, China, US, EU-27 and reference for GDP, Emissions and
-Population}
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{Absolute GDP 2019, Countries with highest GDP, China, US, EU-27
+and reference for GDP, Emissions and Population}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Paper_files/figure-latex/unnamed-chunk-16-1.pdf}
+\caption{GDP per Capita 2019, Countries with highest GDP, China, US,
+EU-27 and reference for GDP, Emissions and Population}
 \end{figure}

### 2022-12-13 r-report/Paper.Rmd

@@
 
-```{r init}
+```{r setup-ex}
+source('r-imports/init.R')
+source('r-analysis/meta.R')
+theme_ghg = function(){
+  theme_minimal() %+replace%
+     theme(
+       plot.title =element_blank(),
+       plot.subtitle = element_blank()
+    )
+}
+DIRECT_PLOTTING = F
 ```
@@
 GAS = "GHG"
-COUNTRY = "China"
 
-source("r-analysis/data_sector_incomelevel.R", local = TRUE, print.eval = TRUE)
-source("r-plots/plot_facet_incomelevels_sectors_emissions.R", local = TRUE, print.eval = TRUE)
+source("r-analysis/data_cumulative_mergeforecast.R", local = TRUE, print.eval = TRUE)
+source("r-plots/plot_cumulative_china_2030.R", local = TRUE, print.eval = TRUE)
 
